### 2018-04-25 proceedings/IEEE/proceeding_arxiv.tex
proceedings from CHEF and IEEE 2017

%% A. Irles
%% irles@lal.in2p3.fr
%% Novembre/2017

\documentclass[journal]{IEEEtran}
\usepackage{graphicx}
\usepackage{textcomp}
\newcommand*\vtick{\textsc{\char13}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Latest developments on the highly granular Silicon-Tungsten Electromagnetic Calorimeter technological prototype for the International Large Detector.}

\author{A. Irles\thanks{Laboratoire de l'Acc\'el\'erateur Lin\'eaire, Centre Scientifique d'Orsay, Universit\'e de Paris-Sud XI, CNRS/IN2P3, F-91898 Orsay Cedex, France (e-mail: \texttt{irles{@}lal.in2p3.fr})} on behalf of the CALICE Collaboration.}

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  High precision physics at future colliders requires unprecedented
  highly granular calorimeters for the application of the Particle
  Flow (PF) algorithm. 
  The physical proof of concept was given in the previous campaign
  of beam tests of physic prototypes within the CALICE collaboration.
  We present here the latest beam and laboratory test results and
  R\&D developments for the Silicon-Tungsten Electromagnetic Calorimeter
  technological prototype with fully embedded very front-end (VFE)
  electronics for the International Large Detector at the
  International Linear Collider project. 
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, CALICE, calorimetry, particle flow, electromagnetic calorimeter, high granularity.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

\IEEEPARstart{F}{uture} accelerator based particle physics experiments
require very precise and detailed reconstruction of the final states produced
in the beam collisions. A particular example is the next generation of $e^{+}e^{-}$
linear colliders such the ILC\cite{ilctdr}.
This project will provide collisions of polarized beams with centre-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
These collisions will be studied by two multipurpose detectors:
the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
Another example of an $e^{+}e^{-}$ collider project is the Compact Linear Collider (CLIC)
project\cite{clictdr} which will produce collisions with $c.m.e$ of 380 GeV - 3 TeV
with a detector featuring similar design than the ILD and SiD.
Both projects will study with unprecedented precision the final states with heavy bosons (W, Z  and H) and heavy quarks ($c$, $b$ and $t$).

To meet the required precision levels, these detectors will be based on the Particle Flow (PF) techniques\cite{Brient:2002gh,Morgunov:2004ed}.
These techniques consist of choosing the best information available
to measure the energy of the final state objects (i.e. measuring the charged particles momentum at tracking devices better than in the calorimeters).
Therefore, PF techniques rely on single particle separation.
For this purpose, PF algorithms require highly granular and compact calorimeter systems featuring minimum dead material.
The R\&D of highly granular calorimeters for future linear colliders is conducted within the CALICE collaboration\cite{calice}.
For further about PF and CALICE R\&D we refer the reader to reference \cite{Sefkow:2015hna} and references therein.

Due to the PF requirements, the calorimeters at ILD will be placed inside the magnetic coil
providing magnetic fields of 3.5 T. The baseline design of the ILD ECAL consists in a detector (in the barrel region) of 24 $X_{0}$ of thickness.
The silicon-tungsten electromagnetic calorimeter, SiW-ECAL, design and R\&D conducted by CALICE is oriented at the baseline design of the ILD ECAL.
It has silicon (Si) as active material and tungsten (W) as absorber material.
The combination of Si and W for the construction of the layers allows
for building a very compact calorimeter with compact active layers and small cell size (high granularity) in the transverse and longitudinal planes.
It will consist of an alveolar structure of carbon fibre into which slabs made of tungsten
plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
embedeed in the slabs. The silicon sensors will be segmented
in squared cells of 5x5 mm: a total of $\sim 100$ million channels will constitute the ECAL for ILD.
To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
forseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive within
acquisition windows of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. During the idle time, the bias currents of the electronics will be shut down.
This technique is usually denominated power pulsing.

\section{The CALICE silicon tungsten electromagnetic calorimeter engineering prototype.}

The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
It was successfully tested at DESY, FNAL and CERN running together with another CALICE prototype,
the analogue hadronic calorimeter AHCAL delivering the proof of concept of PF calorimetry.
For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
The active layers were made of a matrix of 3x3 Si wafers. Each of these wafers was segmented in matrices of
6x6 squared pixels of 1x1 $cm^{2}$.
The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
(0.4, 1.6 and 2.4 $X_{0}$) making a total of 24 $X_{0}$ which equivales to $\sim 1~\lambda_{I}$ (interaction length).
Published results proving the good performance of the technology and the PF can be found in references \cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa} and \cite{Bilki:2014uep}

Current prototype, the technological prototype, addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
It will also provide data to deeply study the PF and provide input to tune the Monte Carlo programs.

\subsection{Slabs and Active Signal Units.}

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{shortslab-eps-converted-to.pdf}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visibles. The silicon sensors are glued to the PCB in the other side.}
\label{shortslab}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{fevcob1-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{fevcob2-eps-converted-to.pdf}
  \end{tabular}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Photograph of the FEV11\_COB. The first figure correspond to a picture taken from the top. The second one is a lateral picture.}
\label{fevcob}
\end{figure}

The entity
of sensors, thin PCB (printed circuit boards) and ASICs (application-specific integrated circuits) is called Active Signal Units or ASU.
An individual ASU has a lateral dimension of 18x18 cm$^{2}$ and has glued onto it 4 silicon wafers (currently with a thickness of 320 $\mu$m).
The ASUs are equipped
further with 16 ASIC for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
The readout layers of the SiW-ECAL consist of a chain of ASUs and an interface card
to a data acquisition system (DAQ) at the beginning of the layer.
This interface card also carries services as power connectors,
test output pins, connectors for signal injection, etc. 
Currently, the technological prototype layers are built with version of PCB called FEV11 with 16 SKIROC (see section \ref{sec:DAQ})
 in BGA packages mounted on top of it.
%These PCBs have been tested in different conditions (beam test, pulse injection tests, cosmic muon test)
 %proving a high performance (see section XX for more details) but are
These PCBs still don't meet the requirements
for the ILD in terms of thickness (1.2 mm). The FEV11 thickness is 1.6 alone and 2.7 mm including the ASICs.
Figure \ref{shortslab} shows a picture of a full equipped short slab with FEV11 ASU.
There are ongoing R\&D activities in an alternative PCB design in which the ASICs
will be directly placed on board of the PCB in dedicated cavities. The ASICS will be in semiconductor packaging and wire bonded to the PCB.
A small sample of FEV11\_COB (same connexion pattern with the interface card than FEV11)
with thickness of 1.2 mm is being produced (see figure \ref{fevcob})
and is planned to be added to the prototype and tested in beam tests conditions.

\subsection{Data AcQuisition System.}
\label{sec:DAQ}

SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is the very front end ASIC designed for the readout of the Silicon PIN didoes.
It consists of 64 channels that each comprises a low noise charge preamplifier of variable gain followed by two lines:
a fast line for the trigger decission and a slow line for dual gain charge measurement.
Finally, a Wilkinson type analogue to digital converter fabricates the digitised charge deposition that can be readout. %The output consists in analogue to digital converted charge measurement (ADC).
Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as triggered or not triggered.
The information is stored in 15 cell deep pyshical switched capacitor array (SCA).
This autotrigger capability is mandatory for ILC case since the accelerator will not provide a central global trigger.
A key feature of the SKIROC ASICs is that they can be power pulsed to meet ILC power consumption requirements.

Every ASU of the SiW-ECAL prototype is equipped with 16 SKIROCs version 2. A new version, 2a, has been produced and will be used to equip new layers currently in production.

The design of the subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
Current DAQ consists of three modules which are designed to be generic enough to cope with other applications.
The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs.
All DIFs are connected by single HDMI cables to the concentrator cards: Gigabit Concentrator Card (GDCC).
The HDMI connection is used to transmit both slow control and data readout.
One GDCC controls up to 7 DIFs collecting all data from them and distributing to them the system clock and fast commands.
The most downstream module is the clock and control card (CCC). The CCC provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. spill signals).

The whole system is controled by the Calicoes and the Pyrame DAQ software version 3~\cite{pyrame1,pyrame2}. The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition. Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype.

%%--
\section{SiW-ECAL technological prototype performance on positron beam test.}

This beam test was prepared by a careful and comprehensive commissioning.
The purpose of this phase was to characterize the layers and monitor and control the
noise levels. The commissioning includes the definition of trigger threshold values or noisy channels to be masked.
Studying and control the noise levels in an autotriggered and high-granularity calorimeter
is crucial since noisy cells may saturate the DAQ faster than physical signals.
Two different types of noise were identified:
noise patterns that repeat on all layers 
and noise bursts due to non proper electrical isolation of the layers.
The first source of noise forced us to define a list of channels to be masked in all layers.
The noise bursts issue was circumvented by improving the electrical isolation of single layers.
We have also observed that the noise burst happen only at the end of long acquisitions therefore, in addition to the improved isolation,
we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
However, more studies in the laboratory are needed in order to fully understand these issues.

The prototype tested in beam in June 2017 consisted of 7 layers see figure \ref{prototype}.
In the first layer, $\sim 40\%$ of channels were masked due to a damaged Si wafer. In all the other, only the 6-7\% of channels were masked except in the last one were this number grew up to the 16\% due to a faulty ASIC. The number of masked channels may be drastically reduced by setting individual threshold settings instead of global trigger threshold values for each channel on an ASIC. This possibility will become available with the next version of SKIROC ASIC.

The detector was exposed to a positron beam in the DESY test beam area (line 24).
The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates of te order of the KHz (with maximum of $\sim 3$ KHz). In addition, DESY gives acces to a bore 1 T solenoid, the PCMAG \cite{pcmag}, in the beam area.

The detector was running in power pulsing mode without any extra active cooling system.
By means of an external pulse generator we defined the length of the acquisition window to be
3.7 ms at a frequency of 5 Hz. %% ------------
%5 Hz frequency defined by a pulse generator.
%defined by short spills of 3.7 ms width and 5 Hz frequency defined by a pulse generator.
%The detector was placed on top of a movable table that was directly controlled by Pyrame.

%% PCMAG goes HERE

\begin{figure}[!t]
\centering
\includegraphics[width=3.0in]{proto-eps-converted-to.pdf}
\caption{Technological prototype: 7 single short slabs inside the mechanical aluminum structure.}
\label{prototype}
\end{figure}

The physics program of the beam test can be summarized in the following points:

\begin{itemize}
\item Commissioning and calibration without absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs);
\item magnetic field tests inside the PCMAG magnet with magnetic fields up to 1 T;
\item response to electrons with fully equipped detector, i.e. sensitive parts {\it and} W absorber.
\end{itemize}

\subsection{Calibration runs.}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=2.5in]{mipsummary-eps-converted-to.pdf}  \\
    \includegraphics[width=2.5in]{snsummary-eps-converted-to.pdf}
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated cells.}
\label{mipandSN}
\end{figure}

The main calibration was realized 
by directing the 3 GeV positron beam on 81 positions equally distributed over the surface of the detector.
These data were used for pedestal estimation and energy calibration.
%% initially, first step -------------- built == reconstructed tracks
Calibration and pedestal analysis was done for all single layers not requiring requiring track reconstruction.
We calculated the pedestal position for every channel and SCA by fitting the distribution of non triggered hits with a gaussian function.
Afterwards, we subtracted these values to the distribution of triggered hits and fit the resulting distributions to a Landau function convoluted by a gaussian.
The most-probable-value of the convoluted function is taken as the MIP value.
We have obtained a raw energy calibration spread of the 5\% among all cells with the 98\% of all available cells being fitted. Results are summarized in figure \ref{mipandSN}, upper plot.

The signal-over-noise ratio, defined as the ratio between the most-probable-value of
the Landau-gauss function fit to the data (pedestal subtracted) and the pedestal width
(calculated as the standard deviation of the gaussian distribution fitted to the data), was estimated.
The average value for all channels and slabs is 20.3 ($\sim 3$ times better than in the physics prototype, mainly due to the reduced size of cells and different gain values).
Results are summarized in figure \ref{mipandSN}, lower plot.

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{mip3peaks-eps-converted-to.pdf}
\caption{Single cell energy distribution (for all calibrated cells) for 3 GeV positron tracks acting as MIPs. }
\label{miplog}
\end{figure}

After pedestal subtraction, calibration and track reconstruction we could finalize the MIP calibration by selecting tracks that cross the detector parallel to its normal.
The result is shown in figure \ref{miplog} where single cell the energy distribution for MIPs is shown for all calibrated cells.
The distribution reveals the presence of a second and third peak due to events of multiparticles crossing the detector.

Finally, a calibration run with the beam hitting the slabs under an angle of $\sim 45^{0}$ was done.
The purpose of this run was to proof that the MIP position scales with a factor $\sqrt{2}$
due to the larger path to be crossed by the electrons in the Si wafer.
Preliminary results show a perfect agreement with the expected results.

\subsection{Magnetic field tests.}

For this test, a special PVC structure was
designed and produced to hold the slab vertically, perpendicular to the beam.

The purpose of the test was twofold: first to proof that the DAQ, all electronic devices and the mechanical slab itself were able
to handle strong magnetic fields; second purpose was to proof the stability of performance during these tests.
We took several runs, with 0, 0.5 and 1 T magnetic fields with and without 3 GeV positron beam.
We observed that the pedestals position is independent of the magnetic field (within the 1 per mile). The MIP position was increased, in average,
of the 3\% for 1 T and 1.5\% for 0.5 T with respect with the 0 T case.
This level of increase is expected since the positron traversing the magnetic field hit the slab with a deflecting angle,
increasing then the path of the particle through the wafer. More detailed studies and simulation comparisons are to come.

\subsection{Response to electromagnetic showers.}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=3.0in]{shower1-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{shower2-eps-converted-to.pdf}\\
    \includegraphics[width=3.0in]{shower3-eps-converted-to.pdf}
  \end{tabular}
\caption{Raw electromagnetic shower profiles for three different tungsten configurations. In the x-axis, we show the layer number. In the y-axis, the averaged fraction of {\it energy} (sum of ADC in all triggered cells in a event, considering only events where all layers had at least a hit) measured in every layer. }
\label{showers}
\end{figure}

The purpose of the beam test was to study the interaction of electrons with the absorber material resulting in
electromagnetic showers.
We inserted W plates of different thicknesses between the sensitive layers and we performed
a scan of energies of the positron beam: 1, 2, 3, 4, 5 and 5.8 GeV.
We tested the response of the detector with three different configurations of the W repartition.
The first one adding up a total of 6.16 $X_{0}$, the second 7.84 $X_{0}$ and the third of 9.52 $X_{0}$.
Preliminary results of the raw electromagnetic shower profiles are shown in figure \ref{showers}
for the three different configurations and for all energies. This first approach to the data looks promising but further studies and comparisons with simulations are needed.

\section{Outlook.}

The ILD ECAL will host long layers of up to $\sim$2.5m.
Current research efforts are focused in the construction and test of such long layers made of chains of ASUs (up to $\sim$15 ASU).
A long layer of $\sim$2.m  is now being produced and tested in the laboratory (figure \ref{longslab}).
A long layer constitutes a technological challenge in both aspects, the mechanical
(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
and the electrical (i.e. transmission of signals and high currents).
For example, interconnections between ASUs and between ASU and interface card are one of the most involved parts of the assembly
and require close collaboration between mechanical and electronic engineers.
Currently, this interconnection is made with flat kapton connectors manually soldiered onto the layers by heating procedure.
This is, so far, carried manually and found to be time consuming. Other alternatives are currently being  investigated.

%%--
\begin{figure}[!t]
\centering
\includegraphics[width=2.0in]{longslab-eps-converted-to.pdf}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\caption{Design of a long layer being currently produced.}
\label{longslab}
\end{figure}

\appendices
% use section* for acknowledgment
\section*{Acknowledgment}

This project has received funding from the European Union’s Horizon 2020 Research and Innovation programme under Grant Agreement no. 654168.

This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).

The research leading to these results has received funding from the People Programme (Marie
Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
programme coordinated by Campus France.

The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\begin{thebibliography}{1}

\bibitem{ilctdr}
  \emph{http://www.linearcollider.org/ILC/Publications/Technical-Design-Report}

\bibitem{Behnke:2013lya} 
  T.~Behnke {\it et al.},
  ``The International Linear Collider Technical Design Report - Volume 4: Detectors,''
  arXiv:1306.6329 [physics.ins-det].
  %%CITATION = ARXIV:1306.6329;%%
  %284 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{clictdr}
  \emph{http://clic-study.web.cern.ch/}

\bibitem{Brient:2002gh} 
  J.~C.~Brient and H.~Videau,
  %``The Calorimetry at the future e+ e- linear collider,''
  eConf C {\bf 010630}, E3047 (2001)
  [hep-ex/0202004].
  %%CITATION = HEP-EX/0202004;%%
  %90 citations counted in INSPIRE as of 08 Nov 2017

\bibitem{Morgunov:2004ed} 
  V.~Morgunov and A.~Raspereza,
  ``Novel 3-D clustering algorithm and two particle separation with tile HCAL,''
  physics/0412108.
  %%CITATION = PHYSICS/0412108;%%
  %6 citations counted in INSPIRE as of 08 Nov 2017

\bibitem{calice} 
  \emph{https://twiki.cern.ch/twiki/bin/view/CALICE/CaliceCollaboration}

\bibitem{Sefkow:2015hna} 
  F.~Sefkow, A.~White, K.~Kawagoe, R.~Pöschl and J.~Repond,
  ``Experimental Tests of Particle Flow Calorimetry,''
  Rev.\ Mod.\ Phys.\  {\bf 88}, 015003 (2016)
  doi:10.1103/RevModPhys.88.015003
  [arXiv:1507.05893 [physics.ins-det]].
  %%CITATION = doi:10.1103/RevModPhys.88.015003;%%
  %5 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2011ha} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Tests of a particle flow algorithm with CALICE test beam data,''
  JINST {\bf 6}, P07005 (2011)
  doi:10.1088/1748-0221/6/07/P07005
  [arXiv:1105.3417 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/6/07/P07005;%%
  %32 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Anduze:2008hq} 
  J.~Repond {\it et al.} [CALICE Collaboration],
  ``Design and Electronics Commissioning of the Physics Prototype of a Si-W Electromagnetic Calorimeter for the International Linear Collider,''
  JINST {\bf 3}, P08001 (2008)
  doi:10.1088/1748-0221/3/08/P08001
  [arXiv:0805.4833 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/3/08/P08001;%%
  %78 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2008aa} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Response of the CALICE Si-W electromagnetic calorimeter physics prototype to electrons,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 608}, 372 (2009)
  doi:10.1016/j.nima.2009.07.026
  [arXiv:0811.2354 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2009.07.026;%%
  %56 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2010xj} 
  C.~Adloff {\it et al.},
  ``Study of the interactions of pions in the CALICE silicon-tungsten calorimeter prototype,''
  JINST {\bf 5}, P05007 (2010)
  doi:10.1088/1748-0221/5/05/P05007
  [arXiv:1004.4996 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/5/05/P05007;%%
  %19 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{CALICE:2011aa} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Effects of high-energy particle showers on the embedded front-end electronics of an electromagnetic calorimeter for a future lepton collider,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 654}, 97 (2011)
  doi:10.1016/j.nima.2011.06.056
  [arXiv:1102.3454 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2011.06.056;%%
  %9 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Bilki:2014uep} 
  B.~Bilki {\it et al.} [CALICE Collaboration],
  %``Testing hadronic interaction models using a highly granular silicon–tungsten calorimeter,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 794}, 240 (2015)
  doi:10.1016/j.nima.2015.05.009
  [arXiv:1411.7215 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2015.05.009;%%
  %5 citations counted in INSPIRE as of 07 Nov 2017

 \bibitem{Callier:2011zz} 
  S.~Callier, F.~Dulucq, C.~de La Taille, G.~Martin-Chassard and N.~Seguin-Moreau,
  ``SKIROC2, front end chip designed to readout the Electromagnetic CALorimeter at the ILC,''
  JINST {\bf 6}, C12040 (2011).
  doi:10.1088/1748-0221/6/12/C12040
  %%CITATION = doi:10.1088/1748-0221/6/12/C12040;%%
  %21 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Gastaldi:2014vaa} 
  F.~Gastaldi, R.~Cornat, F.~Magniette and V.~Boudry,
  ``A scalable gigabit data acquisition system for calorimeters for linear collider,''
  PoS TIPP {\bf 2014}, 193 (2014).
  %%CITATION = POSCI,TIPP2014,193;%%
  %1 citations counted in INSPIRE as of 08 Nov 2017

\bibitem{pyrame1}
  F. Magniette, M. Rubio-Roy, and F. Thiant,
  ``Pyrame, a rapid-prototyping framework for online systems,''
  Journal of Physics, Conference Series, Vol 664, 2015.

\bibitem{pyrame2}
  M. Rubio-Roy, F. Thiant, and F. Magniette,
  ``Flexible online monitoring for high-energy physics with Pyrame,''
  Journal of Physics, Conference Series, 2016.

%\bibitem{Shpak:2016anm} 
%  K.~Shpak [CALICE ILD SiW ECAL Group],
%  ``The ILD/CALICE Silicon-Tungsten Electromagnetic Calorimeter: status and potential,''
%  PoS ICHEP {\bf 2016}, 1085 (2016).
%  %%CITATION = POSCI,ICHEP2016,1085;%%

\bibitem{pcmag} 
  R.~Dienner,
  ``PCMAG Solenoid Upgrade at DESY Testbeam Area T24/1,''
  \emph{http://bib-pubdb1.desy.de/record/192513}

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

%\begin{IEEEbiography}{Adrián Irles}
%Biography text here.
%\end{IEEEbiography}

% if you will not have a photo at all:
%\begin{IEEEbiographynophoto}{John Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

%\begin{IEEEbiographynophoto}{Jane Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2018-04-25 paper-draft/draft.tex
Paper first commit. Not ready for circulation

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jinstpub} % for details on the use of the package, please
                     % see the JINST-author-manual

\usepackage[utf8]{inputenc}

\usepackage{lineno}
\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{{#1}}}

\linenumbers

\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}

% e-mail addresses: only for the forresponding author
\emailAdd{irles@lal.in2p3.fr}
%\collaboration[]{on behalf of the CALICE collaboration}

\abstract{
  High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
  of the energy of final state particles.
  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require highly granular and hermetic calorimeters systems.
  The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
  design and R\&D is tailored to the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
  In this document we present the latest news on R\&D of such prototype with fully embedded very front-end (VFE) electronics.
  Special emphasis is given to the presentation and discussion of the commissioning of the prototype
  for beam test and to the performance of the device in such beam test carried at DESY in June 2017.
}

\keywords{Calorimeter methods, calorimeters, Si and pad detectors}

\begin{document}
\maketitle
\flushbottom

\section{Introduction}

Future accelerator based particle physics experiments
require very precise and detailed reconstruction of the final states produced
in the beam collisions. A particular example is the next generation of $e^{+}e^{-}$
linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
This project will provide collisions of polarized beams with centre-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
These collisions will be studied by two multipurpose detectors:
the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
Another example of an $e^{+}e^{-}$ collider project is the Compact Linear Collider (CLIC)
project\cite{Aicheler:2012bya,Linssen:2012hp,Lebrun:2012hj}
which will produce collisions with $c.m.e$ of 380 GeV - 3 TeV
with a detector featuring similar design than the ILD and SiD.
Both projects will explore with unprecedented precision the origin of the electroweak symmetry breaking and new physics beyond the standard model by exploring final states with heavy bosons (W, Z  and H) and fermions ({\it i.e.} heavy quarks as $c$, $b$ and $t$).

To meet the required precision levels, these detectors will be based on the Particle Flow (PF) techniques\cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}.
These techniques rely on single particle separation to make possible the choice of the best information available
in the full detector to measure the energy of the final state objects: {\it i.e.} the charged particles momentum is better measured by the tracking system
the photons energy by the electromagnetic calorimeter and the neutral hadrons energy by the full calorimeter system.
In that way the poor resolution of the calorimeter systems (compared with trackers) will  only have a reduced impact in the overall reconstruction.
For this purpose, detectors optimized for PF algorithms have some requirements, summarized here:

\begin{itemize}
\item a highly efficient and "transparent" tracking system between the interaction point and the calorimetry systems;
\item highly granular ({\it imaging calorimetry}) and compact calorimeter systems featuring minimum dead material;
\item and high power of particle separation\footnote{
For that reason the calorimeter systems at ILD will be placed inside the magnetic coil
providing magnetic fields of 3.5 T}.
\end{itemize}

The R\&D of highly granular calorimeters for future linear colliders is conducted within the CALICE collaboration and, for now on, we refer the reader to \cite{Sefkow:2015hna} for further information about PF and the CALICE R\&D.

In this document we will focus in the description of the silicon-tungsten electromagnetic calorimeter,
SiW-ECAL, its commissioning and its performance in beam test.
The SiW-ECAL is the baseline choice for the ILD ECAL. It consists in a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
It has silicon (Si) as active material and tungsten (W) as absorber material.
The combination of Si and W choices  makes possible the design and construction
of a very compact calorimeter with highly granular and compact active layers.
It will consist of an alveolar structure of carbon fiber into which modules called SLABs made of tungsten
plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
embedded in the SLABs. The silicon sensors will be segmented
in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million channels will constitute the ECAL for ILD.
The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs.
To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive within
acquisition windows of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. During the idle time, the bias currents of the electronics will be shut down.
This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels, the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.

The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
It was successfully tested at DESY, FNAL and CERN running together with another prototype from the CALICE
collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of PF calorimetry.
For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
The active layers were made of a matrix of 3x3 Si wafers. Each of these wafers was segmented in matrices of
6x6 squared pixels of 1x1 $cm^{2}$.
The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
(0.4, 1.6 and 2.4 $X_{0}$) making a total of 24 $X_{0}$.
Published results proving the good performance of the technology and the PF can be found in references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.

\section{The SiW-ECAL engineering prototype}

The new generation prototype is called the SiW-ECAL technological prototype and it addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
It will also provide data to deeply study the PF and provide input to tune the Monte Carlo programs.

\subsection{Silicon sensors}
\label{sec:wafers}

The sensors consist on float zone silicon wafers 320$\mu$m thick with high resistivity (larger than 5000 $\Omega\cdot$cm). The size of the wafer is $9\times9$ cm$^{2}$ featuring an array of 256 PIN diodes of $5\times5$ mm$^{2}$. A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC if the particle traverses the 320$\mu$m perpendicularly to its larger surface.

The original design of the silicon wafers included an edge termination made of floating guard-rings.
It was observed in beam test\cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
and the pixels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
This coupling lead to fake events in which, at least,
the channels in the four edges of the wafer are triggered at the same time. 
This is why these events are so often called squared events. 
An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-rings design 
as well as the internal crosstalk. As outcome of this R\&D program, the technological prototype 
is equipped with silicon wafers with:

\begin{itemize}
\item \todo{N wafers type-X with guard-rings of XXX characteristics (continuous, segmented, segmented smaller??)}
\item \todo{N wafers type-Y without guard rings and the width of the peripheral dead areas lower than 500 $\mu$m thanks to the use of stealth dicing technique.}
\end{itemize}

For the wafers \todo{type-Y}, the amount of squared events is expected to be reduced by, at least, a \todo{factor XXX}. In both cases, 
for interaction with low energy particles as the delivered at the DESY beam test facility (see Section \ref{sec:beamtest}) the
amount of squared events is expected to be negligible, therefore we will not do any differentiation 
of our results depending on the wafer type mounted in the detector.

\todo{ Is this needed? If so, what are the right plots to show?} Before the assembly of the sensors in the detector, these are characterized one-by-one by measuring the leakage current (of the order of 1 nA per single diode) 
as a function of the bias voltage (I-V curve), the full depletion voltage (of 40 V) extracted from C-V curve and
the stability in time (leakage current versus time at a nominal bias).
%The single diodes have capacitances of 8 $pF$.

\begin{figure}[!t]
\centering
\begin{tabular}{l}
  \includegraphics[width=3.0in]{figs/test.jpg} \\
  \includegraphics[width=3.0in]{figs/test.jpg} \\
  \includegraphics[width=3.0in]{figs/test.jpg}
\end{tabular}
\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: La Esperanza del Condenado, J. Miró}}
\label{shortslab}
\end{figure}

\subsection{SKIROC: Silicon pin Kalorimeter Integrated ReadOut Chip}
\label{sec:skiroc}

SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is the very front end ASIC designed for the readout of the Silicon PIN didoes.
It consists of 64 channels in AMS 0.35 $\mu$m SiGe technology. Each channel comprises a low noise charge preamplifier of variable gain followed by two lines:
a fast shaper for the trigger decision and a set of dual gain slow shaper for charge measurement. 
The gain can be controlled by modifying the feedback capacitance during the configuration of the detector.
With the slowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs 
(a slightly less than the desired final value for the ILC). 
Finally, a Wilkinson type analogue to digital converter fabricates the digitized charge deposition that can be readout. 
Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as
triggered or not triggered and the information is stored in 15 cell deep physical switched capacitor array (SCA).
The trigger threshold can be controlled both globally and locally (channel by channel) although the
dynamical range for the channel by channel option is too small in the SKIROC version 2 due to a mistake in the development. The trigger holds the voltage of the two slow shapers with a tunable delay and also
holds the voltage swept with the slow clock trigger to obtain timing information.

The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
the bias currents of the ASIC can be switched off during the idle time between bunch trains.
With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
meeting the ILC requirements. All the results shown in this paper are obtained using the power pulsing feature.

Every ASU of the SiW-ECAL prototype is equipped with 16 SKIROCs version 2. A new version, 2a, has been produced and will be used to equip new layers currently in production.
In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.

\begin{figure}[!t]
  \centering
    \includegraphics[width=4in]{figs/skiroc2_block.eps}
\caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
\label{SKIROC2}
\end{figure}

\subsection{Active Sensor Units}
\label{sec:ASU}

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=4in]{figs/ASU_geometry1.eps}  \\
    \includegraphics[width=4in]{figs/ASU_geometry2.eps}  \\
  \end{tabular}
  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back. The channels are separated (in x and y) by 5.5 mm.
    The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.}
\label{ASU}
\end{figure}

The entity
of sensors, thin PCB (printed circuit boards) and ASICs (application-specific integrated circuits) is called Active Signal Units or ASU.
An individual ASU has a lateral dimension of 18x18 cm$^{2}$ and has glued onto it 4 silicon wafers (currently with a thickness of 320 $\mu$m). The high voltage is delivered to the wafers using a HV-kapton sheet that covers the full extension of the wafers.
The ASUs are equipped
further with 16 ASIC for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm. The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU_geometry}

The readout layers of the SiW-ECAL consist of a chain of ASUs and an adapter board
to a data acquisition system (DAQ) at the beginning of the layer.
This adapter board is called SMBv4
and it also serves as a place to sit the power connectors (low voltage to power the analog and digital
parts of the ASIC and high voltage to bias the PIN diodes) and the super capacitances used for the power pulsing. 
These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance. 
The purpose of these capacitances is to provide local storage 
of the necessary charge to avoid the transport of current pulses over long cables, 
ensuring in this way the stability of the ASICs during the acquisition.

Currently, the technological prototype layers are built with version of PCB called FEV11 with 16 SKIROC (see Section \ref{sec:DAQ}).
The FEV11 thickness is 1.6 alone and 2.7 mm including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
Figure \ref{shortslab} (left) shows a picture of a full equipped short slab with FEV11 ASU.
There are ongoing R\&D activities in an alternative PCB design in which the ASICs
are directly placed on board of the PCB in dedicated cavities.
The ASICS will be in semiconductor packaging and wire bonded to the PCB. This is the so-called COB (chip-on-board) version of the ASU.
A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
with a total thickness of 1.2 mm has been produced and tested in the laboratory
showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{shortslab} (right).

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{figs/test.jpg} & \includegraphics[width=2.8in]{figs/fev11_cob.png} 
  \end{tabular}
  \caption{Left \todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visibles. The silicon sensors are glued to the PCB in the other side.
  Right: two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
\label{ASU}
\end{figure}

\subsection{Data AcQuisition system}
\label{sec:DAQ}

The design of the subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
Current DAQ consists of three modules which are designed to be generic enough to cope with other applications.
The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs.
All DIFs are connected by single HDMI cables to the concentrator cards: Gigabit Concentrator Card (GDCC).
The HDMI connection is used to transmit both slow control and data readout.
One GDCC controls up to 7 DIFs collecting all data from them and distributing to them the system clock and fast commands.
The most downstream module is the clock and control card (CCC).
The CCC provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. spill signals).

The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition.
Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype. 
This new version of the DAQ software implements a new mechanism to allow any module to treat and publish data in real time. 
Those data are made available to any requesting module, in particular to a new online monitor module developed
for this beam test, allowing for quick online checks of the data quality and integrity.

\subsection{Setup}
\label{sec:setup}

The prototype tested in beam is composed of 7 layers consisting in one short SLAB each.
A short SLAB is made of: one single ASU FEV11 equipped with 16 SKIROC2 and 4 wafers glued on the other side (1024 channels);
an interface card SMBv4; and a DIF. All these elements sit on a "U" shape carbon structure to protect the wafers.
The full system is then covered by two aluminum plates to provide electromagnetic shielding and mechanical stability.
The 7 layers are supported by a PVC and aluminum structure that in which can be inserted to 10 layers.
The distance between two layer slots is 15 mm and this space is used to place tungsten plates of different thicknesses.
For the beam test described in Section \ref{sec:beamtest}, the layers were placed in positions 1-6 and 10.
During the commissioning, the slabs have been tested both inside and outside of the structure.
A photograph showing the prototype can be seen in Figure \ref{proto}. The ASICs and channels
are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
%The mapping from this numbering scheme to real positions in the ASUs is shown in the right plot of Figure \ref{proto}.

\begin{figure}[!t]
\centering
\begin{tabular}{l}
\includegraphics[width=4.0in]{figs/proto.png} 
\end{tabular}
\caption{Prototype with 7 layers inside the aluminum stack.}
\label{proto}
\end{figure}

\section{Commissioning of the detector}
\label{sec:commissioning}

This beam test was prepared by a careful and comprehensive commissioning comprising:
the debug of the
single SLABSs with special emphasis in the control of the noise and the study of the
prototype performance in cosmic rays tests.

The SKIROC2 has been already commissioned for previous experiences (see for example the 
references \cite{Amjad:2014tha,Suehara:2018mqk}). 
Therefore, all the settings used for the SKIROC2 to obtain 
the results described in this paper are motivated by previous experiences. 
For example, the value of 1.2pF for the preamplifier. 
With this gain, the SKIROC2 ensures a linearity better than 90\% 
for 0.5-200 MIPs, which is optimal for 
electromagnetic showers created by few GeV 
electrons or positrons. The delay of the trigger signal is the same than in 
reference \cite{Amjad:2014tha,Suehara:2018mqk}: 130 DAC for all ASICS. 
This value was chosen by selecting the delay in which an injected signal
of few MIPs of value get the maximum value of ADC. %Finally, the value of the
%compensation capacitance at the output of the preamplifier has been set to 6pF instead of 
%4pF to prevent overshots and ripples of the signal used as input to the trigger
%decision and ADC lines.

\subsection{Optimization of noise levels}
\label{sec:comm_noise}

The purpose of this phase was to monitor and control the
noise levels of the prototype. The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
Studying and control the noise levels in an self-triggered and high-granularity calorimeter
is crucial since noisy channels may saturate the DAQ faster than physical signals.
Two different types of noise were identified:
randomly distributed (in time) noisy channels 
and noise bursts affecting to all layers at the same time.

The first type of noise source (randomly distributed in time)
forced us to define a list of channels to be masked in all 
layers. Again, two different type of noisy channels have been identified. 
The first group is compose by randomly distributed (in space) channels which 
slightly larger number of triggers than the others. The second group is made of
a fixed list of channels, all in the same positions for all SLABs, that were giving
underflowed ADC triggers at high rates.

The channels associated to "underflowed-noise" events were identified by means of the online monitoring
tools. Some preliminary inspections of the FEV11 layout hint that
the cause of this "underflowed-noise" events may be in an improvable routing of the
lines from the PIN pad to the SKIROC. 
For this reason, if a given channel appeared to be associated 
to "underflowed-noise" events in one of the SLABs, 
it was masked in all of them, taking in this way the most conservative solution.
For example, all channels number 37 were masked in all ASICs.
More studies in this respect are to come.

The list of the noisy channels randomly distributed in time and space was
defined by means of dedicated data taking runs. 
These runs were characterized by: their short acquisition windows (of 2.5 ms, only 1.1 ms 
of effectively data taking time), their low
spill frequency (5 Hz) to minimize the chances of having real events due to cosmic rays 
hitting the detector during the
data taking; and the relatively high trigger threshold values between 250 and 400 DAC 
(which is equivalent to $\sim$0.5-2 MIP, see Section \ref{sec:comm_trigger} for more 
information). The full process was an iterative process starting with several repetitions
of runs at a high threshold value and then some iterations at lower threshold each up to 250 DAC. 
In every of there iterations, the channels identified as noisy were masked.
A full run involved 3-5 threshold values and at least two repetitions per value.
Again, we decided to follow a conservative approach for list the noisy channels to be masked:
if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers it was added to the list.

In addition to the different noisy channel types described above, we also have
masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
listed as noisy) or if a Si-wafer was misworking (high leakage currents). In these cases 
and in all mentioned above, the masking involved two steps: disabling of the trigger and 
the disabling of the power of the preamplifier of that channel. A summary of the results of the masking procedure is shown in Figure \ref{noisycells}.

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
  \includegraphics[width=4in]{figs/commissioning/masked_layer.eps} \\
  \includegraphics[width=4in]{figs/commissioning/masked_chip.eps}
  \end{tabular}
\caption{Ratio of channels that are marked as noisy in all slabs. 
Top: inventory of the different type of noisy channels per slab. 
Bottom: break up of the noisy channels per ASIC. We see two spikes in the number of channels masked due to routing issues in the ASICs 1 and 9. 
These two ASICs are located near the SMB where the density of lines (data and power transmission) is higher, complicating in this way the
routing. The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
in the second plot since they are fully masked.}
\label{noisycells}
\end{figure}

We observed that the noise bursts happening coherently at the same time in all SLABS
was associated to cases when the electrical isolation between SLABs was broken.
This is a hint of a system effect as grounding loops or noise in the power supplies.
The issue was circumvented by improving the electrical isolation of single layers.
We have also observed that the noise burst happen only at the end of long acquisitions therefore, in addition to the improved isolation,
we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
However, more studies in the laboratory are needed in order to fully understand these issues.

\subsection{Threshold determination}
\label{sec:comm_trigger}

Once that the SKIROC main settings have been fixed and the masking of the noisy channels at a relatively high threshold value
has been done, the final step is the selection of the optimal trigger threshold values.
For that, we perform dedicated runs in which we scan a reasonable range of trigger threshold values (in DAC units)
with all channels enabled (excepted the marked as noisy). For each of the DAC points
we took data during $\sim$ 1 minute per DAC in order to speed up the commissioning.
Plotting the total number of hits normalized to the maximum vs the DAC
for each channel gives the so-called S-curves. In the absence of external signals (cosmic rays, injected signals, etc) 
these noise S-curves show the convolution of the envelope of the 
electronic noise at the output of the fast shaper (the trigger decision line).
Indeed, the size of this enveloppe is related to slow clock frequency
(larger periods, larger possibility to find a noise variation over the threshold).

To reduce to the minimum the
presence of cosmic rays signals, we perform runs with short open acquisition windows (1.1 ms). 
In Figure \ref{scurve_channels} 
two S-curves of two different channels from the second layer of the setup are shown.

The S-curves are fitted to a complementary error function
\begin{equation}
S(DAC)=p_{0} \times erfc(\frac{DAC-p_{1}}{p_{2}}) = 
\newline
\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} \exp^{-t^{2}} dt,
\label{eq_S-curve}
\end{equation}
where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
the 50\% of its maximum and $p_{2}$ give us the width of the S-curve.

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
  \includegraphics[width=2.8in]{figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{figs/commissioning/scurve_chn2_asic0_layer2.eps}
  \end{tabular}
\caption{Two S-curves obtained during noise runs.}
\label{scurve_channels}
\end{figure}

The function from equation \ref{eq_S-curve} was fitted to all
channels data and all the values of $p_{1}$ and $p_{2}$ were saved.
To decide the final trigger threshold value for the full ASIC, we took the maximum between:

\begin{equation}
DAC_{optimal}^{ASIC-j} = <p_{1}^{ASIC-j}> + 5 \times <p_{2}^{ASIC-j}>
\end{equation}
and 230 if more than the 30\% of the 64 channels S-curves in the ASIC could be fitted. 
If not, we took a most conservative value of 250 DAC. The election of these two values was 
sustained by previous experiences, see for example \cite{Amjad:2014tha}.

The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.

\subsection{S/N ratio in the trigger line}
\label{sec:comm_trigger_sn}

Similar kind of measurements can be done but using external signals. 
This will allow to calculate the signal over noise (S/N) ratio to trigger 1 MIP signals.
To calculate the S/N of the trigger we need to compare the 1 MIP S-curve and 2 MIP S-curve. The S/N 
will be defined as the ratio between the distance of both S-curves at its 50\% and the width of the 
S-curve.

In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP S-curves obtained for a one channel
in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
"fake" signals are directly injected in the preamplifier (via a 3 pF capacitor in the injection line). 
From this plot we can extract a S/N ratio of $\sim$12. 
We don expect large differences with the results that we would obtain with 
full equipped SLABs 
although this board is thought for commissioning and test of the SKIROC ASICS in an
"ideal" environment in contrast with the FEV
ASUS that are optimized to meet detector constraints and to hold several ASICs at the same time.
For example: only power pulsing of the analog power is done in this testboard,
there is a set of external capacitors on the board connected to some ASIC pins and
usually only one channel is tested. This allows us to commission the SKIROC2 itself

\begin{figure}[!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=4in]{figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
	\end{tabular}
\caption{S-curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
\label{scurves_injection}
\end{figure}

We have obtained similar results using real signals, in this case cosmic rays signals. This is shown 
in Figure \ref{scurves_cosmics}  where 
we show the result of the fit to the noise S-curves for all channels (in red) in one of the ASICs of 
the second layer together with the results of the S-curve with cosmic rays (black points and blue 
line). For the cosmic S-curve we took 30 min of data per point using very long spills (150 ms) in 
frequencies of 5Hz and we add up the triggers from all channels together. In addition, using the 
knowledge of the MIP value (see next section), we performed a simple cut in the ADC
to keep only signals corresponding to a MIP 
(pedestal subtracted) $\pm30$ ADC counts. With this cut we try reduce the contribution of muons 
traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
since we were using simple setups with only single slabs during in the run. For all these reasons, we expect
a broader distribution of the cosmic S-curve. This is one of the reasons why, if we calculate the S/N 
using this plot, the value would be unrealistic (much lower, indeed). 
In addition to this, we should remember that the noise S-curve do correspond to the real noise 
distribution but only to the envelope of the noise in the fast shaper, therefore the
distance between the two S-curves is smaller than the real distance between noise and signal.

\begin{figure}[!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=4in]{figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
	\end{tabular}
\caption{S-curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
\label{scurves_cosmics}
\end{figure}

In conclusion, both ways of estimating the S/N ratio of the trigger have their own limitations but in 
both cases, the 50\% of the S-curve of 1 MIP are compatible within $\pm10$ ADC. This allow us
to, at least, estimate the relative distance between our final trigger threshold for every ASIC and 
the 1 MIP position. This is shown in Figure \ref{trigger_thresholds}. Two ASICS ($\sim2\%$) have a
trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.

\begin{figure}[!t]
  \centering
  \includegraphics[width=4in]{figs/commissioning/threshold_chip.eps}
  \caption{Summary of trigger threshold settings for all ASICs in the setup. The values are given in DAC and in estimated MIP units, using the distance between two MIPs from Figure \ref{scurves_injection}. The uncertainty quoted in the right axis is estimated from difference between the 50\% position of the S-curve for one MIP extracted from this figure and Figure \ref{scurves_cosmics}.}
\label{trigger_thresholds}
\end{figure}

\subsection{Prospects}
\label{sec:comm_prospects}

All the commissioning procedure described above relies in very conservative decisions
due to the presence of unknown noise sources during most of the commissioning phase. These sources are
now well know and isolated and therefore a new ``noise'' commissioning procedure can proposed
for the next beam test. It will consist in an iterative algorithm that first
will identify and mask the "underflowed-noisy" channels and afterwards run a set of acquisitions
in which the number of triggers per channel will be compared with the number of expected triggers
assuming only cosmics rays as signal. This will allow us to have an
unambiguous definition of the noise levels channel per channel instead of 
defining that levels relatively to the total number
of recorded triggers. Finally, once that the noisy channels
are identified, the optimization of the threshold levels
will be performed and the last run for identification of noisy channels will be taken using this optimal
level will be taken. In this run, we can decide to mask the noisy channels or
to increase its own trigger threshold level if we are using Skiroc2a.

Using this new procedure we manage to reduce the number of masked channels by a factor 2 without any loss of performance,
at least in the laboratory and using 3 of the 7 SLABs. This new procedure will be tested in the next beam test.
Also, in order to
optimize the commissioning of the detector,
we will propose a new set of measurements in the next beam test consisting in:
a scan of optimal delay of the hold values of the trigger using MIP like particles;
and a threshold scan for the determination of the S/N in the trigger line using
1 MIP and $\sqrt{2}$ MIP (tilting the detector by 45 degrees) signals.

\section{Performance on positron beam test at DESY}
\label{sec:beamtest}

The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates from few hundreds of Hz to few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
These positrons are produced in the following way: first, the electron/positron synchrotron DORIS II 
is used to produced a photon beam via bremsstralhung when interacting with a carbon fiber target;
secondly, these photons are then converted to electron/positron pairs; 
and, finally, the beam energy is selected with dipole magnets and collimators. 
In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.

The prototype tested in beam in June 2017 consisted of 7 layers as explained in Section \ref{sec:setup}.
The detector was exposed to a positron beam in the DESY test beam area (line 24).
By means of an external pulse generator we defined the length of the acquisition window to be
3.7 ms at a frequency of 5 Hz, emulating in this way similar conditions than the ILC will have.
The detector was running in power pulsing mode without any extra active cooling system.

The physics program of the beam test can be summarized in the following points:

\begin{itemize}
\item Commissioning and calibration without tungsten absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs);
\item magnetic field tests up to 1 T in the PCMag;
\item response to electrons with fully equipped detector, i.e. sensitive parts {\it and} W absorber.
\end{itemize}

For the first two points from above, we used the SiW-ECAL in the tracker mode, {\it i.e.} without 
intercalated tungsten plates. Due to the low material budget of our setup when the tungsten is not 
included, a beam of positrons of few GeV of energies provides satisfactory data for calibration since 
the positrons deposit the minimum amount of energy by ionization.
The calibration of the detector was realized 
by directing the 3 GeV positron beam on 81 positions equally distributed over the surface of the 
detector.
These data were used for pedestal estimation and energy calibration.
Calibration and pedestal analysis was done for all single layers not requiring track reconstruction.
The study of these data is discussed in Section \ref{sec:pedestal} for the pedestal and noise studies and Section \ref{sec:mip} for the results of the calibration.

For the tests inside the magnetic field, a special PVC structure was
designed and produced to support one single SLAB.
The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
mechanical slab itself were able
to handle strong magnetic fields; second to prove the stability of the performance during these tests.
We took several runs, with 0, 0.5 and 1 T magnetic fields with and without 3 GeV positron beam and 
we observed that the pedestal and noise values are independent of the magnetic field (see Section 
\ref{sec:magnetic}). The study of the MIP calibration stability will be discussed in future 
publications, where full studies of the data including comparison with simulations should be included.

To fulfill the last point of the list we inserted W plates of different thicknesses between the 
sensitive layers. Then we performed
a scan of energies of the positron beam: 1-5.8 GeV.
We tested the response of the detector with three different configurations of the W repartition.
The accumulated amount of tungsten, in radiation length units, $X_{0}$, in front of each of the 
SLABs is:
\begin{itemize}
\item W-configuration 1: $0.6,1.2,1.8,2.4,3.6,4.8$ and $6.6~X_{0}$
\item W-configuration 2: $1.2,1.8,2.4,3.6,4.8,6.6$ and $8.4~X_{0}$
\item W-configuration 3: $1.8,2.4,3.6,4.8,6.6,8.4$ and $10.2~X_{0}$
\end{itemize}

Preliminary results of the raw electromagnetic shower profiles look promising but will not be 
discussed in this article since deeper analysis and comparison with montecarlo simulations
will be needed to extract conclusive results from the data. This will be the topic of a future 
article, possibly combining data with future beam tests that are currently in preparation. What it
is included in this article, in Section \ref{sec:showers} is the study of the pedestals in this events.

\subsection{Pedestal and noise studies with the SiW-ECAL in tracker mode}
\label{sec:pedestal}

Due to the way that the SKIROC2 ASICs work, it is possible to extract the pedestals
simultaneously to the recording of signals from particle interactions. Indeed, when a channel
is triggered, the rest are read out at the end of the slow clock period (usually called BCID - for bunch crossing ID  and marked as
non triggered channels. This allows us to reconstruct the pedestal distribution
for all channels and for all SCAs. These distributions are fitted with a Gaussian
and the pedestal value are associated with the mean of the result of the fit.
These values will be, afterwards, subtracted to the ADC recorded by the SKIROC2 for all channels and SCAs.
The noise of the channel and SCA corresponds to the width of the pedestal distribution.
The calibration runs have been used to calculate the pedestal distribution reference values of the detector.
In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
subtracting the pedestal mean position.

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=4in]{figs/mip_pedestal_example.eps}
  \end{tabular}
  \caption{Pedestal (blue dashed line) and signal (black continuous line) distribution for one channel in the third layer. The results of the MIP calibration fit are included (red). The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range. The signal distribution is integrated over all SCAs.}
\label{signal_pedestal}
\end{figure}

In Figure \ref{pedestal_channel} (left) we observe that both the pedestal position for each SCA in the same channel can be
different in few \%s. In the case of the pedestal mean position, these differences are even larger between different ASICs in the same
layer (Figure \ref{pedestal_layer}, left plot) or between layers (Figure \ref{pedestal_all}, left). This is the reason of
performing the pedestal correction layer-, chip-, channel- and SCA-wisely.
For the noise, the dispersion is smaller ($\sim 5 \%$) and only dependent on the SCA. This is shown in the right plots of Figures \ref{pedestal_channel}, \ref{pedestal_layer} and \ref{pedestal_all}.

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{figs/pedestal/ped_width_layer2_chip4_cell10.eps}
  \end{tabular}
  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
\label{pedestal_channel}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{figs/pedestal/width_mean_layer2.eps}
  \end{tabular}
  \caption{Pedestal mean position (upper plot) and width (lower plot) for all channels in one layer. The data is grouped on bunches in which the value in the x-axis
    corresponds to the value of the channel number plus the value of the ASIC number multiplied by 100. The black points show the value for the first SCA
    and the red points show the average value for all the others SCAs (with the standard deviation of the sample as error bar).}
\label{pedestal_layer}
\end{figure}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{figs/pedestal/h_ped_mean.eps} & \includegraphics[width=2.8in]{figs/pedestal/h_ped_width.eps}
  \end{tabular}
  \caption{Pedestal mean position (left) and width (right) for all channels and all SCAs in the setup.}
\label{pedestal_all}
\end{figure}

\subsubsection{Pedestal and noise in large magnetic fields}
\label{sec:magnetic}

For the tests inside the magnetic field we used the SLAB of the first layer
in the special PVC struture mentioned at the begining of this section. We should also mention that
the PCMag is in a different area (downstream) on the same beam line,
therefore, due to the presence of additional collimators the beam rates are lower.

We divided the
data taking in 3 stages in this order:
a long run (13h) with a magnetic field of 1 T, a second and shorter run of 3 hours with 0.5 T and a final run with the magnet off.
In the cases were we had beam, we used the 3 GeV positron beam settings impacting in the ASIC number 12.

The comparison of the pedestal values and noise levels between the reference run in the stack
and the different runs in the magnetic field are shown in Figure \ref{pedestal_magnetic}.
We see that in both cases, the agreement is perfect within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few SCAs.

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.8in]{figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{figs/pedestal/1T/summary_noise_chip12.eps}
  \end{tabular}
  \caption{Average deviation of the pedestal mean position (left) and width (right) for all channels in the ASIC 12. The values are given in MIP units obtained from calibration (see Section \ref{sec:mip}).}
\label{pedestal_magnetic}
\end{figure}

\subsection{MIP response and tracking efficiency with the SiW-ECAL in tracker mode}
\label{sec:mip}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
      \includegraphics[width=2.8in]{figs/MIP/MIPsummary_title.eps} & \includegraphics[width=2.8in]{figs/MIP/SNsummary_title.eps}  
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated channels.}
\label{mipandSN}
\end{figure}

After the calculation of the pedestals for each channels and SCA, these are subtracted and the same data (without track
recognision) are used for the calibration.
A Landau function convoluted by a Gaussian is fit to the resulting hit distribution
in ADC units.
The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
conversion from ADC to energy.
We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.

We checked the MIP 
calibration by selecting tracks that cross the detector parallel to its normal
and filling a histogram with the energy measured by each channel with a hit.
We did this for all calibration runs together.
The results are shown in figure \ref{mip3peaks} where the single channel energy 
distribution for MIPs is shown for all calibrated channels in the same distribution. 
The distribution nicely fits in the 1 MIP spectrum, showing in that way the good
performance of our default calibration that, for simplicity, was done without requiring
tracking reconstruction.
The distribution also reveals the presence of a second and third peak due to events involving multiple 
particles crossing the detector.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=4in]{figs/MIP/MIP3peaks.eps} 
    \end{tabular}
    \caption{The single channel energy distribution (for all calibrated channels) for 3 GeV positron tracks acting as MIPs.}
\label{mip3peaks}
\end{figure}

To evaluate 
the single hit detection efficiency we define a high purity sample of
events of positrons traversing the detector perpendicularly by selecting
tracks with at least 5 layers (of 7 possible) with a hit in exactly the same channel. Afterwards we 
check if the other layers have or not a hit in the same channel (expanding the search
to the neighbor channels) with energy larger or equal than 0.3 MIP.
Finally, we repeat this for all layers 
and channels. The results are shown in Figure \ref{efficiency}. Except few exceptions, the efficiency is 
compatible with $100\%$.
Lower efficiencies in the first layer are related to the presence of
noisy channels not well identified in the commissioning phase that boosted the filling
of the the 15 SCAs of three ASICs. In the last layer (separated from the
other layers by four slots of 1.5 cm instead of only one) we also observe few small deviations
from the $\sim100\%$ which are indeed
associated to a slight misalignment of the tracks visible only in the outliers channels. 
If we remove these channels i nthe outliers from the analysis
the full efficiency is recovered.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
    \end{tabular}
    \caption{Left: MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles. Right: same figures with a zoom in the y-axis. In both cases, the average efficiency of the 64 channels in each ASIC is shown.}
\label{efficiency}
\end{figure}

\subsubsection{S/N ratio in the ADC}
\label{sec:mip}

The signal-over-noise ratio in the ADC (corresponding to the slow shaper of the SKIROC2) is defined 
as the ratio between the most-probable-value of
the Landau-gauss function fit to the data (pedestal subtracted) and the noise (the pedestal width). This quantity 
has been calculated for all channels and all slabs and, in average, it corresponds to 20.4.
Results are summarized in Figure \ref{mipandSN}, rightmost plot.

\subsection{Pedestal stability in electromagnetic shower events}
\label{sec:showers}

The pedestal stability in events with large amount of charge deposited by the ASICs, as are the 
electromagnetic shower events, has been also calculated. All the results shown in this section correspond to data taken during the tungsten program, 
using the W-configuration number 2 when shooting the beam in the ASIC 12 (and partially in the 13). Only the ASIC 12 is used in the analysis. For other configurations and 
positions of the beam we get comparable results. We used also a calibrated data sample were the pedestal values have been 
subtracted and the MIP calibration has been applied. 
Therefore, all energy measurements are given in MIP units and the pedestal
values are expected to be equal to zero.
In order to select a high purity of
electromagnetic shower like the events, 
we used a simple criteria: select only events with at least 6 of the layers with at least a hit with E > 0.5 MIP.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{figs/pedestal/pedestal_vs_nhits_shower.eps} \\
    \end{tabular}
    \caption{Left: mean position of the projection of the pedestal distribution of all channels of ASIC 12 in the Layer 3 calculated when different energies are collected in the ASIC (in bins of 10 MIPs). Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA. The points for SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
\label{pedestal_shower_1}
\end{figure}

Two main observations have been extracted from the recalculation of the pedestals and its comparison
with the values obtained previously during the calibration runs. The first observation
consists in a relatively small 
drift of the pedestal values
towards lower values when the collected energy is high (or when the number of triggered channels is large).
For events with 80 MIPs collected in the ASIC, we have an average drift of the pedestal of $\sim$ 0.05 MIP. 
This can be seen in Figure \ref{pedestal_shower_1} for several SCAs where the
average of the projection of the pedestal distribution for all channels non triggered in ASIC 12 of layer 3 
is plot as a function of the total energy measured by the ASIC (or the total number of hits).
We see that in all cases, the slopes of the curves 
for each SCA are very similar.
This is feature is known and it is due to the architecture of the SKIROC2 (and 2a) ASICs 
where high inrush of currents can slightly shift the baseline of the analogue power supply. 
This feature is foreseen to be removed from the SKIROC3 ASICs.

The second observation extracted from this analysis can be also seen in Figure \ref{pedestal_shower_1}: in addition
to the small drift of the pedestal value an SCA-alternate global shift
is observed. This feature is still not fully understood although the fact that the effect is observed in
alternate SCAs but no time dependence has been observed hints to some issue affecting the digital part of the ASIC 
(where the SCAs enter in play). 
In Figure \ref{pedestal_shower_2} we can see the effect, SCA per SCA, for different energies of the beam
and for different layers. We see that the effect is enhanced when large amounts of charge
are deposited in the ASIC ({\it i.e.} at larger beam energies or for the layers in the maximum of the shower
profile).
Dedicated tests in the laboratory and in the beam are needed in order to clarify this issue.

\begin{figure}[!t]
  \centering 
    \begin{tabular}{ll}
      \includegraphics[width=2.8in]{figs/pedestal/pedestal_deviation_layer3.eps} & \includegraphics[width=2.8in]{figs/pedestal/pedestal_deviation_4GeV.eps} \\
    \end{tabular}
    \caption{Left: average value on each SCA of the calculated pedestals for all channels of ASIC 12 in the Layer 3 for different energies of the beam. Right: same but fixing the energy of the beam and comparing several layers.}
\label{pedestal_shower_2}
\end{figure}

\subsection{Fake triggers filtering}
\label{sec:retriggers}

Several types of fake signals have been observed in the technollogical prototype since its construction and test. A detailed description of them
can be found in previous articles, as for example, in Ref. \cite{Amjad:2014tha}. All these fake signals are easily identified
and tagged during the data acquisition and removed afterwards from the analysis
not introducing any loss of performance as can be seen, for example, in the tracking efficiency plots.
In the following, we briefly describe the status of the monitoring, debugging and filtering
of such kind of events.

\subsubsection*{Empty triggers}

Empty trigger events are a well known feature of SKIROC2. The issue appears when during
the acquisition the rising edge of the slow clock falls during the OR64 signal used
to signalize the lecture of a signal over threshold to validate the change to a new SCA.
When this happens at the end of the clock period, the change to a new SCA is validated twice.
This effect creates around 10-15\% of empty events which are easily filter and removed from the
analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to $\sim3\%$ by reducing
the length of the OR64 by a factor X.}

\subsubsection*{Plane events and retriggers}

Another well know issue is related to the appearance of bunches of consecutive fake triggers that
quickly fill several SCA in consecutive slow clock periods. These events are also
characterized by triggering many channels (some times even all channels of an ASIC) at the same time.
Although the ultimate reason of the appearance of these events remains unknown we have done
a lot of advances in this topic. We know that the SKIROC2 and 2a preamplifiers are referenced to the analog power supply level,
therefore, any voltage dip can ve seen as signal by the preamplifiers. The presence of a high inrush of current
due to many channels triggered at the same time can create these voltage dips.
In previous studies ({\it i.e.} reference \cite{Amjad:2014tha}), the ratio of retriggers and plane events
was reduced by improving the power supply stabilization capacitances. It is important to remark that
all layers and all ASICs analog and digital levels are powered using the same power supply.
Moreover, the high voltage power supply for the polarization of the PIN diode it is also common for all layers.
Therefore any noise in
these power supplies or any overload of an ASIC may lead participate in the creation of fake signals
in different ASICs and layers.

Studying the MIP calibration data of this beam test we have noticed that most of the retriggers and plane events are originated 
in
ASICs far from the beam spot. Even more, hot spots tend appear near the channels 37 and the channels tagged as ``underflowed'' 
during
the commissioning phase. The amount these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 KHz) and at higher rates even larger than $40\%$ in other 
ASICs far from the beam spot.
Moreover, it has been noticed a correlation between the time that an ASIC was full and the time of the appearance of some 
retriggers in other areas of the PCB. 
This correlation corresponds to $\sim8$ BCIDs (1.6 $\mu$s) which hints
of a distortion on the analogue power supply when
the signal that informs the DIF that one ASIC memory has been filled is transmitted from the ASICs to
the DIF through the PCB.

All this information and dedicated studies in the laboratory will be used for the
improvement of the power delivery, the PCB design and for further SKIROC developments 
with the possible approval the ILC in the scope.

\section{Summary and prospects}
\label{sec:prospects}

The R\&D program of the highly granular SiW-ECAL detector is in an exciting phase. 
After the proof of principle of the imaging calorimetry concept using the physics prototype, the 
technological prototype is being constructed and tested. In this document we describe the commissioning and
beam test performance of a prototype built in with the first fully assembled
detector elements (still only 7 over the total of $\sim$10000 to be in the ILD).

A very comprehensive and detailed commissioning procedure has been established and optimized
allowing us to identify and isolate the different noise sources that could spoil the data taking.
The beam test has provided a lot of useful data, allowing first for the study of 
the performance of the detector and secondly 
for its channel by channel calibration. 
A full analysis including the comparison with simulations of the 
second part of the data taking program (the electromagnetic showers) is to come.
During both phases, the commissioning and the beam test,
we have collected a good amount of data and results
that will serve as input for future improvements on
the design of the ASUs, the SKIROC and the upstream DAQ.

\todo{Do we want to discuss these things?}
In parallel to the work described here, several R\&D efforts are being carried.
For example, we know that the ILD ECAL will host long layers of up to $\sim$2.5m.
A long layer constitutes a technological challenge in both aspects, the mechanical
(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
and the electrical (i.e. transmission of signals and high currents).
For example, interconnections between ASUs and between ASU and interface card are one of
the most involved parts of the assembly
and require close collaboration between mechanical and electronic engineers.
Therefore, many efforts are focused in the construction and test of such long 
layers made of chains of ASUs (up to $\sim$15 ASU) 
as well as in the standardization of the interconnections. 
In addition, many efforts in the compactification of
the DAQ and the ASUs ({\it i.e.} the chip on board versions of the 
ASUs described in Section \ref{sec:ASU}) are being
conducted by the SiW-ECAL collaboration.

\acknowledgments

This project has received funding from the European Union{\textquotesingle}s Horizon 2020 Research and Innovation program under Grant Agreement no. 654168.
This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).
The research leading to these results has received funding from the People Programme (Marie
Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
programme coordinated by Campus France.
The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).

% We suggest to always provide author, title and journal data:
% in short all the informations that clearly identify a document.

\bibliographystyle{JHEP}
\bibliography{references}

\end{document}

### 2018-05-11 performance-paper-draft/draft.tex
First draft ready to iterate
Small text and figures improvement

--- 2018-04-25 paper-draft/draft.tex
@@
   of the energy of final state particles.
-  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require highly granular and hermetic calorimeters systems.
+  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
   The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
@@
 
-To meet the required precision levels, these detectors will be based on the Particle Flow (PF) techniques\cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}.
-These techniques rely on single particle separation to make possible the choice of the best information available
-in the full detector to measure the energy of the final state objects: {\it i.e.} the charged particles momentum is better measured by the tracking system
-the photons energy by the electromagnetic calorimeter and the neutral hadrons energy by the full calorimeter system.
-In that way the poor resolution of the calorimeter systems (compared with trackers) will  only have a reduced impact in the overall reconstruction.
-For this purpose, detectors optimized for PF algorithms have some requirements, summarized here:
+It is known that in a {\it classical} typical multipurpose detector
+of a collider experiment the charged particles momentum is better measured by the tracking system
+the photons energy are only observed in the calorimeter system (mainly in the electromagnetic) if they are not converted
+and the measurement of the neutral hadrons energy can only be done by involving the full calorimeter systems.
+To meet the required precision levels by the ILC or CLIC physics goals,
+new techniques relying on single particle separation to make possible the choice of the best information available
+in the full detector to measure the energy of the final state objects have been developed.
+These techniques are called Particle Flow (PF) techniques \cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}
+and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
+For this purpose, detectors optimized for PF algorithms have some requirements. Some of them are summarized here:
 
@@
 The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
-It was successfully tested at DESY, FNAL and CERN running together with another prototype from the CALICE
+It was successfully tested at DESY, FNAL and CERN running in front of another prototype from the CALICE
 collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of PF calorimetry.
@@
 
-\section{The SiW-ECAL engineering prototype}
+\section{The SiW-ECAL technological prototype}
 
@@
 The original design of the silicon wafers included an edge termination made of floating guard-rings.
-It was observed in beam test\cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
+It was observed in beam tests \cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
 and the pixels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
@@
 \centering
-\begin{tabular}{l}
-  \includegraphics[width=3.0in]{figs/test.jpg} \\
-  \includegraphics[width=3.0in]{figs/test.jpg} \\
-  \includegraphics[width=3.0in]{figs/test.jpg}
+\begin{tabular}{lll}
+  \includegraphics[width=1.8in]{figs/test.jpg} &
+  \includegraphics[width=1.8in]{figs/test2.jpg} &
+  \includegraphics[width=1.8in]{figs/test3.jpg}
 \end{tabular}
-\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: La Esperanza del Condenado, J. Miró}}
+\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: Triptic La Esperanza del Condenado, J. Miró}}
 \label{shortslab}
@@
 
-SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is the very front end ASIC designed for the readout of the Silicon PIN didoes.
-It consists of 64 channels in AMS 0.35 $\mu$m SiGe technology. Each channel comprises a low noise charge preamplifier of variable gain followed by two lines:
+SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is the very front end ASIC (application-specific integrated circuits)
+designed for the readout of the Silicon PIN didoes.
+In its version SKIROC2 (and 2a) it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
+Each channel comprises a low noise charge preamplifier of variable gain followed by two lines:
 a fast shaper for the trigger decision and a set of dual gain slow shaper for charge measurement. 
@@
 The trigger threshold can be controlled both globally and locally (channel by channel) although the
-dynamical range for the channel by channel option is too small in the SKIROC version 2 due to a mistake in the development.
-The trigger holds the voltage of the two slow shapers with a tunable delay and also
+dynamical range for the channel by channel option is too small in the SKIROC version 2 due to a mistake in the development. This issue has
+been solved in the SKIROC2a. The trigger holds the voltage of the two slow shapers with a tunable delay and also
 holds the voltage swept with the slow clock trigger to obtain timing information.
@@
 
-Every ASU of the SiW-ECAL prototype is equipped with 16 SKIROCs version 2. A new version, 2a, has been produced and will be used to equip new layers currently in production.
+Every ASU of the SiW-ECAL prototype is equipped with 16 SKIROCs version 2. A newer version, 2a, with some incremental improvements
+and bug fixing has been produced and will be used to equip new layers currently in production.
 In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
@@
   \end{tabular}
-  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back. The channels are separated (in x and y) by 5.5 mm.
-    The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.}
+  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back.
+    The channels are separated (in x and y) by 5.5 mm.
+    The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.
+    The ASICs and channels
+    are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
+  }
 \label{ASU}
@@
 The entity
-of sensors, thin PCB (printed circuit boards) and ASICs (application-specific integrated circuits) is called Active Signal Units or ASU.
+of sensors, thin PCB (printed circuit boards) and ASICs is called Active Signal Units or ASU.
 An individual ASU has a lateral dimension of 18x18 cm$^{2}$ and has glued onto it 4 silicon wafers (currently with a thickness of 320 $\mu$m).
@@
 The ASUs are equipped
-further with 16 ASIC for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm. The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU_geometry}
+further with 16 ASIC for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
+The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}
 
@@
 The HDMI connection is used to transmit both slow control and data readout.
-One GDCC controls up to 7 DIFs collecting all data from them and distributing to them the system clock and fast commands.
+One GDCC controls up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
 The most downstream module is the clock and control card (CCC).
@@
 During the commissioning, the slabs have been tested both inside and outside of the structure.
-A photograph showing the prototype can be seen in Figure \ref{proto}. The ASICs and channels
-are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
+A photograph showing the prototype can be seen in Figure \ref{proto}. 
 %The mapping from this numbering scheme to real positions in the ASUs is shown in the right plot of Figure \ref{proto}.
@@
 Therefore, all the settings used for the SKIROC2 to obtain 
-the results described in this paper are motivated by previous experiences. 
+the results described in this paper are motivated by these previous experiences. 
 For example, the value of 1.2pF for the preamplifier. 
 With this gain, the SKIROC2 ensures a linearity better than 90\% 
-for 0.5-200 MIPs, which is optimal for 
+for 0.5-200 MIPs\footnote{\todo{Is this a fact?}}, which is enough for 
 electromagnetic showers created by few GeV 
@@
 noise levels of the prototype. The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
-Studying and control the noise levels in an self-triggered and high-granularity calorimeter
+Studying and control the noise levels
 is crucial since noisy channels may saturate the DAQ faster than physical signals.
 Two different types of noise were identified:
-randomly distributed (in time) noisy channels 
+randomly distributed in time noisy channels 
 and noise bursts affecting to all layers at the same time.
@@
 layers. Again, two different type of noisy channels have been identified. 
-The first group is compose by randomly distributed (in space) channels which 
-slightly larger number of triggers than the others. The second group is made of
+The first group is compose by randomly distributed in space channels.
+The second group is made of
 a fixed list of channels, all in the same positions for all SLABs, that were giving
 underflowed ADC triggers at high rates. 
-
 The channels associated to "underflowed-noise" events were identified by means of the online monitoring
@@
 Again, we decided to follow a conservative approach for list the noisy channels to be masked:
-if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers it was added to the list.
+if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC
+it was added to the list.
 
@@
 was associated to cases when the electrical isolation between SLABs was broken.
-This is a hint of a system effect as grounding loops or noise in the power supplies.
+This is a hint of a system effect as can be the appearence of
+grounding loops or noise in the power supplies.
 The issue was circumvented by improving the electrical isolation of single layers.
-We have also observed that the noise burst happen only at the end of long acquisitions therefore, in addition to the improved isolation,
+We have also observed that the noise bursts happened only at the end of long acquisitions therefore, in addition to the improved isolation,
 we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
@@
 with all channels enabled (excepted the marked as noisy). For each of the DAC points
-we took data during $\sim$ 1 minute per DAC in order to speed up the commissioning.
+we took data only during $\sim$ 1 minute per DAC in order to speed up the commissioning.
 Plotting the total number of hits normalized to the maximum vs the DAC
@@
 electronic noise at the output of the fast shaper (the trigger decision line).
-Indeed, the size of this enveloppe is related to slow clock frequency
-(larger periods, larger possibility to find a noise variation over the threshold).
+Indeed, the size of this enveloppe is related to the slow clock frequency
+(larger periods increase the possibility to find a noise variation over the threshold).
 
 To reduce to the minimum the
-presence of cosmic rays signals, we perform runs with short open acquisition windows (1.1 ms). 
+presence of cosmic rays signals, we perform runs with short open acquisition windows (1.1 ms)\footnote{The acquisition window is defined by means
+  of a external pulse generator that emulates similar spill conditions than at the ILC. For DAQ needs, the actual data recording starts 1.4 ms after
+rising edge of the spill signal arrives. In this paper we will always refer to the effectively open acquisition window not including the mentioned 1.4 ms.}. 
 In Figure \ref{scurve_channels} 
@@
 \end{equation}
-and 230 if more than the 30\% of the 64 channels S-curves in the ASIC could be fitted. 
-If not, we took a most conservative value of 250 DAC. The election of these two values was 
+and 230 if at least the the 30\% of the 64 channels S-curves in the ASIC could be fitted. 
+If less than the 30\% of the channels were fit
+we took a most conservative value of 250 DAC for the threshold of the ASIC.
+The election of these two values was 
 sustained by previous experiences, see for example \cite{Amjad:2014tha}.
@@
 
-In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP S-curves obtained for a one channel
+In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP S-curves obtained for one channel
 in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
-"fake" signals are directly injected in the preamplifier (via a 3 pF capacitor in the injection line). 
+"fake" signals are directly injected in the preamplifier (via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
 From this plot we can extract a S/N ratio of $\sim$12. 
@@
 there is a set of external capacitors on the board connected to some ASIC pins and
-usually only one channel is tested. This allows us to commission the SKIROC2 itself
+usually only one channel is tested. This board allows us to commission and debug the SKIROC itself
+but not the full system.
 
@@
 traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
-since we were using simple setups with only single slabs during in the run. For all these reasons, we expect
+since we were using simple setups with only single slabs. For all these reasons, we expect
 a broader distribution of the cosmic S-curve. This is one of the reasons why, if we calculate the S/N 
@@
 to, at least, estimate the relative distance between our final trigger threshold for every ASIC and 
-the 1 MIP position. This is shown in Figure \ref{trigger_thresholds}. Two ASICS ($\sim2\%$) have a
+the 1 MIP position by combining the information extracted from Figs \ref{scurves_injection} and \ref{scurves_cosmics}.
+This is shown in Figure \ref{trigger_thresholds}. Two ASICS ($\sim2\%$) have a
 trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.
@@
 The values are given in DAC and in estimated MIP units, using the distance between two MIPs from Figure \ref{scurves_injection}.
-The uncertainty quoted in the right axis is estimated from difference between the 50\% position of the S-curve for one MIP extracted from this figure and Figure \ref{scurves_cosmics}.}
+The uncertainty quoted in the right axis is estimated from difference between the 50\% position of the S-curve for one MIP extracted from Figured \ref{scurves_injection} and \ref{scurves_cosmics}.}
 \label{trigger_thresholds}
@@
 due to the presence of unknown noise sources during most of the commissioning phase. These sources are
-now well know and isolated and therefore a new ``noise'' commissioning procedure can proposed
-for the next beam test. It will consist in an iterative algorithm that first
+now well know and isolated and therefore a new ``noise'' commissioning procedure has been studied.
+It will consist in an iterative algorithm that first
 will identify and mask the "underflowed-noisy" channels and afterwards run a set of acquisitions
@@
 unambiguous definition of the noise levels channel per channel instead of 
-defining that levels relatively to the total number
-of recorded triggers. Finally, once that the noisy channels
+defining such levels relatively to the total number
+of recorded triggers per ASIC. Finally, once that the noisy channels
 are identified, the optimization of the threshold levels
-will be performed and the last run for identification of noisy channels will be taken using this optimal
-level will be taken. In this run, we can decide to mask the noisy channels or
+will be performed and a last run for identification of noisy channels will be taken using this optimal
+threshold. In this run, we can decide to mask the noisy channels or
 to increase its own trigger threshold level if we are using Skiroc2a.
@@
 optimize the commissioning of the detector,
-we will propose a new set of measurements in the next beam test consisting in:
-a scan of optimal delay of the hold values of the trigger using MIP like particles;
-and a threshold scan for the determination of the S/N in the trigger line using
-1 MIP and $\sqrt{2}$ MIP (tilting the detector by 45 degrees) signals.
+we propose a new set of measurements in the next beam test such as
+a scan of optimal delay of the hold values of the trigger using MIP like particles
+and a threshold scan for the determination of the S/N in the trigger line. This later
+can be done comparing 1 MIP and $\sqrt{2}$ MIP (tilting the detector by 45 degrees) signals.
 
@@
 \ref{sec:magnetic}). The study of the MIP calibration stability will be discussed in future 
-publications, where full studies of the data including comparison with simulations should be included.
+publications where full studies of the data including comparison with simulations should be included.
 
@@
 The accumulated amount of tungsten, in radiation length units, $X_{0}$, in front of each of the 
-SLABs is:
+SLABs was:
 \begin{itemize}
@@
 simultaneously to the recording of signals from particle interactions. Indeed, when a channel
-is triggered, the rest are read out at the end of the slow clock period (usually called BCID - for bunch crossing ID  and marked as
+is triggered, the rest are read out at the end of the slow clock period (usually called BCID - for bunch crossing identity)  and marked as
 non triggered channels. This allows us to reconstruct the pedestal distribution
@@
 These values will be, afterwards, subtracted to the ADC recorded by the SKIROC2 for all channels and SCAs.
-The noise of the channel and SCA corresponds to the width of the pedestal distribution.
+The noise is associated to the widht of the pedestal distribution.
 The calibration runs have been used to calculate the pedestal distribution reference values of the detector.
@@
 performing the pedestal correction layer-, chip-, channel- and SCA-wisely.
-For the noise, the dispersion is smaller ($\sim 5 \%$) and only dependent on the SCA. This is shown in the right plots of Figures \ref{pedestal_channel}, \ref{pedestal_layer} and \ref{pedestal_all}.
+For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_channel}, \ref{pedestal_layer} and \ref{pedestal_all}.
 
@@
 events of positrons traversing the detector perpendicularly by selecting
-tracks with at least 5 layers (of 7 possible) with a hit in exactly the same channel. Afterwards we 
+tracks with at least 4 layers (of 7 possible) with a hit in exactly the same channel. Afterwards we 
 check if the other layers have or not a hit in the same channel (expanding the search
-to the neighbor channels) with energy larger or equal than 0.3 MIP.
+to the closest neighbouring channels) with energy larger or equal than 0.3 MIP.
 Finally, we repeat this for all layers 
@@
 associated to a slight misalignment of the tracks visible only in the outliers channels. 
-If we remove these channels i nthe outliers from the analysis
+If we remove these channels from the analysis
 the full efficiency is recovered.
@@
 \subsubsection{S/N ratio in the ADC}
-\label{sec:mip}
+\label{sec:sn}
 
@@
 In both cases, the results are shown for few SCA.
-The points for SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
+The points for the curves with SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
 \label{pedestal_shower_1}
@@
 towards lower values when the collected energy is high (or when the number of triggered channels is large).
-For events with 80 MIPs collected in the ASIC, we have an average drift of the pedestal of $\sim$ 0.05 MIP. 
-This can be seen in Figure \ref{pedestal_shower_1} for several SCAs where the
+%For events with 80 MIPs collected in the ASIC, we have an average drift of the pedestal of $\sim$ 0.05 MIP. 
+This is shown in Figure \ref{pedestal_shower_1} for several SCAs where the
 average of the projection of the pedestal distribution for all channels non triggered in ASIC 12 of layer 3 
@@
 
-The second observation extracted from this analysis can be also seen in Figure \ref{pedestal_shower_1}: in addition
+The second observation extracted from this analysis can be also seen in Figure \ref{pedestal_shower_1} but
+more clearly in Figure \ref{pedestal_shower_2}: in addition
 to the small drift of the pedestal value an SCA-alternate global shift
-is observed. This feature is still not fully understood although the fact that the effect is observed in
-alternate SCAs but no time dependence has been observed hints to some issue affecting the digital part of the ASIC 
+is observed. We see that the effect is enhanced when large amounts of charge
+are deposited in the ASIC ({\it i.e.} at larger beam energies or for the layers in the maximum of the shower
+profile). We also observed that this alternation is only SCA dependent and not BCID dependent.
+This is not yet fully understood although the fact that the effect is observed in
+alternate SCAs hints to some issue affecting the digital part of the ASIC 
 (where the SCAs enter in play).
-In Figure \ref{pedestal_shower_2} we can see the effect, SCA per SCA, for different energies of the beam
-and for different layers. We see that the effect is enhanced when large amounts of charge
-are deposited in the ASIC ({\it i.e.} at larger beam energies or for the layers in the maximum of the shower
-profile).
+
 Dedicated tests in the laboratory and in the beam are needed in order to clarify this issue.
@@
 and tagged during the data acquisition and removed afterwards from the analysis
-not introducing any loss of performance as can be seen, for example, in the tracking efficiency plots.
+not introducing any significance loss of performance as can be seen, for example, in the hit detection efficiency plots (see Section \ref{sec:mip}).
 In the following, we briefly describe the status of the monitoring, debugging and filtering
@@
 
-Empty trigger events are a well known feature of SKIROC2. The issue appears when during
-the acquisition the rising edge of the slow clock falls during the OR64 signal used
-to signalize the lecture of a signal over threshold to validate the change to a new SCA.
-When this happens at the end of the clock period, the change to a new SCA is validated twice.
+Empty trigger events are a well known feature of SKIROC2. The SKIROC2 uses
+an OR64 signal to mark the the change to a new SCA when a signal over threshold is
+detected. The empty triggers appear when during
+the acquisition the rising edge of the slow clock falls during the OR64 signal
+and therefore the change to a new SCA is validated twice.
 This effect creates around 10-15\% of empty events which are easily filter and removed from the
-analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to $\sim3\%$ by reducing
-the length of the OR64 by a factor X.}
+analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to $\sim3\%$
+  due to a decrease of the OR64 by a factor X.}
 
@@
 characterized by triggering many channels (some times even all channels of an ASIC) at the same time.
-Although the ultimate reason of the appearance of these events remains unknown we have done
-a lot of advances in this topic. We know that the SKIROC2 and 2a preamplifiers are referenced to the analog power supply level,
+Although the ultimate reason of the appearance of these events remains unknown we
+think that they may be related to some distortion of the
+power supply baselines. We know that the SKIROC2 and 2a preamplifiers are referenced to the analog power supply level,
 therefore, any voltage dip can ve seen as signal by the preamplifiers. The presence of a high inrush of current
@@
 Therefore any noise in
-these power supplies or any overload of an ASIC may lead participate in the creation of fake signals
+these power supplies or any overload of an ASIC may participate in the creation of fake signals
 in different ASICs and layers.
@@
 in
-ASICs far from the beam spot. Even more, hot spots tend appear near the channels 37 and the channels tagged as ``underflowed'' 
+ASICs far from the beam spot. Even more, hot spots tend to appear near the channels 37 and the channels tagged as ``underflowed'' 
 during
@@
 of a distortion on the analogue power supply when
-the signal that informs the DIF that one ASIC memory has been filled is transmitted from the ASICs to
-the DIF through the PCB.
+the signal that informs the DIF that one ASIC memory has been filled is transmitted through the PCB.
 
@@
 
-\todo{Do we want to discuss these things?}
 In parallel to the work described here, several R\&D efforts are being carried.

### 2018-06-11 performance-paper-draft/draft.tex
Correction to the draft long version from Roman and myself. The intro and abstract need to be revisited

@@
   High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
-  of the energy of final state particles.
+  of the final state of the particles produced in the collissions
   The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
@@
   design and R\&D is tailored to the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
-  In this document we present the latest news on R\&D of such prototype with fully embedded very front-end (VFE) electronics.
-  Special emphasis is given to the presentation and discussion of the commissioning of the prototype
-  for beam test and to the performance of the device in such beam test carried at DESY in June 2017.
+  In this document we present and discuss the commissioning of the prototype
+  and the performance of the device in a beam test carried at DESY in June 2017.
 }
@@
 It was successfully tested at DESY, FNAL and CERN running in front of another prototype from the CALICE
-collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of PF calorimetry.
+collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of the technollogy
+and the PF calorimetry.
 For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
 It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
-The active layers were made of a matrix of 3x3 Si wafers. Each of these wafers was segmented in matrices of
-6x6 squared pixels of 1x1 $cm^{2}$.
+The active layers were made of a matrix of 3x3 Si wafers of 500 $\mu$m thickness. Each of these wafers was segmented in matrices of
+6x6 squared channels of 1x1 $cm^{2}$, allowing for density of 1500 channels/dm$^{3}$
 The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
 (0.4, 1.6 and 2.4 $X_{0}$) making a total of 24 $X_{0}$.
-Published results proving the good performance of the technology and the PF can be found in references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
+That very first prototype offered a signal over noise on the measured charge of 7.5 for MIP like 
+particles. More results proving the good performance of the technology and the PF can be found in
+references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
 
@@
 
-The new generation prototype is called the SiW-ECAL technological prototype and it addresses the main technological challenges: compactness,
+The new generation prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
 power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
-It will also provide data to deeply study the PF and provide input to tune the Monte Carlo programs.
+It will also provide data to deeply study the PF and provide input to tune simulation programs as for example
+GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
+in particle physics to simulate the passage of particles through matter.
 
@@
 
-The sensors consist on float zone silicon wafers 320$\mu$m thick with high resistivity (larger than 5000 $\Omega\cdot$cm).
-The size of the wafer is $9\times9$ cm$^{2}$ featuring an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
-A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC if the particle traverses the 320$\mu$m perpendicularly to its larger surface.
+The sensors consist on floating zone silicon wafers 320$\mu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
+The size of the wafer is $9\times9$ cm$^{2}$ and it is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
+A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
+for particles incident perpendicularly to its surface.
 
@@
 It was observed in beam tests \cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
-and the pixels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
+and the channels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
 This coupling lead to fake events in which, at least,
 the channels in the four edges of the wafer are triggered at the same time. 
-This is why these events are so often called squared events. 
+This is why these events are called squared events. 
 An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-rings design 
-as well as the internal crosstalk. As outcome of this R\&D program, the technological prototype 
-is equipped with silicon wafers with:
+as well as the internal crosstalk.
+%As outcome of this R\&D program, the technological prototype 
+%is equipped with silicon wafers with:
+It was concluded that using wafers without guard rings and with a width of the peripheral areas lower than 
+500 $\mu$m thanks to the use of stealth dicing technique, the amount of these squared events 
+can be reduced to be almost negligible. This need to be confirmed in beam test.
+Unfortunately, for the interaction with low energy particles as the delivered at the
+DESY beam test facility (see Section \ref{sec:beamtest}) the
+amount of squared events is expected to be negligible, therefore we will not discuss this issue in the following.
+% do any differentiation 
+%of our results depending on the wafer type mounted in the detector.
 
-\begin{itemize}
-\item \todo{N wafers type-X with guard-rings of XXX characteristics (continuous, segmented, segmented smaller??)}
-\item \todo{N wafers type-Y without guard rings and the width of the peripheral dead areas lower than 500 $\mu$m thanks to the use of stealth dicing technique.}
-\end{itemize}
+%\begin{itemize}
+%\item \todo{N wafers type-X with guard-rings of XXX characteristics (continuous, segmented, segmented smaller??)}
+%\item \todo{N wafers type-Y without guard rings and the width of the peripheral dead areas lower than 500 $\mu$m thanks to the use of stealth dicing technique.}
+%\end{itemize}
 
-For the wafers \todo{type-Y}, the amount of squared events is expected to be reduced by, at least, a \todo{factor XXX}. In both cases, 
-for interaction with low energy particles as the delivered at the DESY beam test facility (see Section \ref{sec:beamtest}) the
-amount of squared events is expected to be negligible, therefore we will not do any differentiation 
-of our results depending on the wafer type mounted in the detector.
+%For the wafers \todo{type-Y}, the amount of squared events is expected to be reduced by, at least, a \todo{factor XXX}. In both cases, 
+%for interaction with low energy particles as the delivered at the DESY beam test facility (see Section \ref{sec:beamtest}) the
+%amount of squared events is expected to be negligible, therefore we will not do any differentiation 
+%of our results depending on the wafer type mounted in the detector.
 
-\todo{ Is this needed?
-If so, what are the right plots to show?} Before the assembly of the sensors in the detector, these are characterized one-by-one by measuring the leakage current (of the order of 1 nA per single diode)
-as a function of the bias voltage (I-V curve), the full depletion voltage (of 40 V) extracted from C-V curve and
-the stability in time (leakage current versus time at a nominal bias).
+%\todo{ Is this needed?
+If so, what are the right plots to show?} Before the assembly of the sensors in the detector, these are characterized one-by-one by measuring the leakage current (of %the order of 1 nA per single diode)
+%as a function of the bias voltage (I-V curve), the full depletion voltage (of 40 V) extracted from C-V curve and
+%the stability in time (leakage current versus time at a nominal bias).
 %The single diodes have capacitances of 8 $pF$.
 
-\begin{figure}[!t]
-\centering
-\begin{tabular}{lll}
-  \includegraphics[width=1.8in]{figs/test.jpg} &
-  \includegraphics[width=1.8in]{figs/test2.jpg} &
-  \includegraphics[width=1.8in]{figs/test3.jpg}
-\end{tabular}
-\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: Triptic La Esperanza del Condenado, J. Miró}}
-\label{shortslab}
-\end{figure}
+%\begin{figure}[!t]
+%\centering
+%\begin{tabular}{lll}
+%  \includegraphics[width=1.8in]{figs/test.jpg} &
+%  \includegraphics[width=1.8in]{figs/test2.jpg} &
+%  \includegraphics[width=1.8in]{figs/test3.jpg}
+%\end{tabular}
+%\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: Triptic La Esperanza del Condenado, J. Miró}}
+%\label{shortslab}
+%\end{figure}
 
@@
 
-SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is the very front end ASIC (application-specific integrated circuits)
+The SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is a
+very front end ASIC (application-specific integrated circuits)
 designed for the readout of the Silicon PIN didoes.
-In its version SKIROC2 (and 2a) it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
-Each channel comprises a low noise charge preamplifier of variable gain followed by two lines:
+In its version SKIROC2 it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
+Each channel comprises a low noise charge preamplifier of variable gain followed by two branches:
 a fast shaper for the trigger decision and a set of dual gain slow shaper for charge measurement. 
@@
 triggered or not triggered and the information is stored in 15 cell deep physical switched capacitor array (SCA).
-The trigger threshold can be controlled both globally and locally (channel by channel) although the
-dynamical range for the channel by channel option is too small in the SKIROC version 2 due to a mistake in the development. This issue has
-been solved in the SKIROC2a. The trigger holds the voltage of the two slow shapers with a tunable delay and also
-holds the voltage swept with the slow clock trigger to obtain timing information.
 
@@
 With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
-meeting the ILC requirements. All the results shown in this paper are obtained using the power pulsing feature.
-
-Every ASU of the SiW-ECAL prototype is equipped with 16 SKIROCs version 2. A newer version, 2a, with some incremental improvements
-and bug fixing has been produced and will be used to equip new layers currently in production.
-In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
-In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
+meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.
 
@@
     The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.
-    The ASICs and channels
+    The areas covered by the different ASICs and channels
     are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
@@
 of sensors, thin PCB (printed circuit boards) and ASICs is called Active Signal Units or ASU.
-An individual ASU has a lateral dimension of 18x18 cm$^{2}$ and has glued onto it 4 silicon wafers (currently with a thickness of 320 $\mu$m).
+An individual ASU has a lateral dimension of 18x18 cm$^{2}$.
+The ASUs are currently equipped
+further with 16 SKIROC2 ASICs for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
+The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}. Each ASU is equipped with 4 silicon wafers as the described in Section \ref{sec:wafers}.
 The high voltage is delivered to the wafers using a HV-kapton sheet that covers the full extension of the wafers.
-The ASUs are equipped
-further with 16 ASIC for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
-The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}
+
+\subsection{Data AcQuisition system}
+\label{sec:DAQ}
+
+The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
+It consists on three modules.
+The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs;
+All DIFs are connected by single HDMI cables to the concentrator cards that make
+the second module: the Gigabit Concentrator Cards (GDCCs).
+%The HDMI connection is used to transmit both slow control and data readout.
+This cards are used to control up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
+The last module, the most downstream, is the clock and control card (CCC) which
+provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
+generated external pulse generator to simulate the ILC spill conditions).
+The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
+%The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition.
+%Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype. 
+%This new version of the DAQ software implements a new mechanism to allow any module to treat and publish data in real time. 
+%Those data are made available to any requesting module, in particular to a new online monitor module developed
+%for this beam test, allowing for quick online checks of the data quality and integrity.
+
+\subsection{Readout layers and SLABs}
+\label{sec:setup}
+
+\begin{figure}[!t]
+  \centering
+    \includegraphics[width=2.8in]{figs/test.jpg} 
+  \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
+\label{ASU2}
+\end{figure}
 
@@
 This adapter board is called SMBv4
-and it also serves as a place to sit the power connectors (low voltage to power the analog and digital
-parts of the ASIC and high voltage to bias the PIN diodes) and the super capacitances used for the power pulsing. 
+and it also serves as to hold other services as power connectors or the super capacitances used for the power pulsing. 
 These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance. 
@@
 
-Currently, the technological prototype layers are built with version of PCB called FEV11 with 16 SKIROC (see Section \ref{sec:DAQ}).
-The FEV11 thickness is 1.6 alone and 2.7 mm including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
-Figure \ref{shortslab} (left) shows a picture of a full equipped short slab with FEV11 ASU.
-There are ongoing R\&D activities in an alternative PCB design in which the ASICs
-are directly placed on board of the PCB in dedicated cavities.
-The ASICS will be in semiconductor packaging and wire bonded to the PCB. This is the so-called COB (chip-on-board) version of the ASU.
-A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
-with a total thickness of 1.2 mm has been produced and tested in the laboratory
-showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{shortslab} (right).
+The readout layers are embedded on a "U" shape carbon structure to protect the wafers.
+The full system is then covered by two aluminum plates
+to provide electromagnetic shielding and mechanical stability.
+This ensemble is denominated SLAB
+(``short'' for 1 ASU ensembles or ``long'' for several ASUs enchained) and it can be seen in
+Figure \ref{ASU2}.
+With current SLABs, a potential density of
+4000 channels/dm$^{3}$ is achievable. This number should be compared with
+the density achieved for previous beam tests: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.
+
+\begin{figure}[!t]
+\centering
+\begin{tabular}{l}
+\includegraphics[width=6.0in]{figs/assembly.png} 
+\end{tabular}
+\caption{Process flow for the assembly of the SiW-ECAL SLABs.}
+\label{assembly}
+\end{figure}
+
+The SiW-ECAL detector designed for the ILD requires of the order
+of $10^{5}$ highly integrated detection like the ones described in this text.
+For the production of the small sample of SLABs studied in this document,
+a scalable working procedure has been established among several groups \cite{Boudry:2318814}
+profiting from the funding of projects like AIDA2020 or the HIGHTEC emblematic project
+of the P2IO. A schematic view of this assembly procedure chain can be seen in
+Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
+
+\section{Commissioning}
+\label{sec:commissioning}
+
+This beam test was prepared by a careful and comprehensive commissioning comprising
+the debug of the
+short SLABSs with special emphasis in the control of the noise and the study of the
+prototype performance in cosmic rays tests.
+
+Earlier experiences with the SKIROC2 ASIC are reported in Refs. \cite{Amjad:2014tha,Suehara:2018mqk}). 
+Internal SKIROC2 parameters found in these references are adopted in the following
+except if the opposite is stated.
+For example, the gain value of 1.2pF for the preamplifier is used. 
+With this gain, the SKIROC2 ensures a linearity better than 90\% 
+for 0.5-200 MIPs, which is enough for 
+electromagnetic showers created by few GeV 
+electrons or positrons.
+% The delay of the trigger signal is the same than in 
+%reference \cite{Amjad:2014tha,Suehara:2018mqk}: 130 DAC for all ASICS. 
+%This value was chosen by selecting the delay in which an injected signal
+%of few MIPs of value get the maximum value of ADC. %Finally, the value of the
+%compensation capacitance at the output of the preamplifier has been set to 6pF instead of 
+%4pF to prevent overshots and ripples of the signal used as input to the trigger
+%decision and ADC lines.
+
+\subsection{Optimization of noise levels}
+\label{sec:comm_noise}
+
+%The purpose of this phase was to monitor and control the
+%noise levels of the prototype.
+%The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
+Studying and control the noise levels
+is crucial since noisy channels may saturate the DAQ faster than physical signals.
+Two different types of noise sources were identified:
+a set of noisy channels randomly distributed in time 
+and noise bursts affecting to all layers at the same time.
+The outcome of this commissioning is summarized in Figure \ref{noisycells}.
+
+The first type of noise source, noise events randomly distributed in time,
+forced us to define a list of channels to be masked in all 
+layers. Again, two different type of noisy channels have been identified. 
+The first group is compose by randomly distributed in space channels.
+The second group is made of
+a fixed list of channels, all in the same positions for all SLABs,
+and all associated to a higher rate of events with underflowed value
+of the read ADC.
+%The latter set of channels were identified by means of the online monitoring
+%tools.
+%As channels are located in the same place for all SLABs,
+%we took the conservative assumption
+%that all modules would have problems in the same set of channels.
+%For example, all channels number 37.
+A large amount of these channels are located
+in areas of the PCB where the density of lines 
+(data and power transmission) is higher than in others.
+This hints for an issue on the routing of the PCB.
+Therefore, these channels are tagged in Figure \ref{noisycells} with the "routing issues" label
+although more tests and deeper inspections of the PCB layout are needed to clarify this issue.
+
+The list of the noisy channels randomly distributed in time and space was
+defined by means of dedicated data taking runs. 
+These runs were characterized by: their short acquisition windows (open to data recording for 
+only 1.1 ms) at low repetition frequencies (5 Hz) to minimize the chances of having real events due to cosmic rays 
+hitting the detector during the
+data taking; and the relatively high trigger threshold values between 250 and 400 DAC 
+(which are equivalent to $\sim$0.5-2 MIP, see Section \ref{sec:comm_trigger} for more 
+information). The full process was an iterative process starting with several repetitions
+of runs at a high threshold value and then some iterations at lower threshold but always 
+higher than 0.5 MIP. 
+In each of the iterations, the channels identified as noisy were masked.
+A full run involved 3-5 threshold values and at least two repetitions per value.
+Again, we decided to follow a conservative approach for list the noisy channels to be masked:
+if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC
+it was added to the list. These channels are labeled as "other" in the first plot in  Figure \ref{noisycells}.
+
+In addition to the different noisy channel types described above, we also have
+masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
+listed as noisy) or if a Si-wafer was misworking (high leakage currents). In these cases 
+and in all mentioned above, the masking involved two steps: disabling of the trigger and 
+the disabling of the power of the preamplifier of that channel.
+
+\begin{figure}[!t]
+  \centering
+  \begin{tabular}{l}
+  \includegraphics[width=4in]{figs/commissioning/masked_layer.eps} \\
+  \includegraphics[width=4in]{figs/commissioning/masked_chip.eps}
+  \end{tabular}
+\caption{Ratio of channels that are marked as noisy in all slabs. 
+Top: inventory of the different type of noisy channels per slab. 
+Bottom: break down of the total number of noisy channels per ASIC. 
+The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
+in the second plot since they are fully masked.}
+\label{noisycells}
+\end{figure}
+
+The other source of noise mentioned at the beginining of this section
+consist on noise bursts happening coherently at the same time in all SLABS
+and it was correlated to occasions when the electrical isolation between SLABs was broken.
+This is a hint of a system effect as can be the appearance of
+grounding loops or disturbances in the power supplies.
+The issue was circumvented by improving the electrical isolation of single layers.
+We have also observed that the noise bursts happens only at the end of long acquisitions. Therefore, in addition to the improved isolation,
+we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
+Ddedicated studies in the laboratory are currently pngoingin order to fully understand this issue.
+
+The list of channels mentioned above is discarded from the data taking from now on.
+
+\subsection{Threshold determination}
+\label{sec:comm_trigger}
+
+In order to select the optimal trigger threshold values for the detector operation
+we perform dedicated scans of trigger threshold values
+with all channels enabled (excepted the marked as noisy). 
+The threshold values are given in internal DAC units which are translated to
+meaningful physical quantities in Section \ref{sec:comm_trigger_sn}. 
+The threshold scan curves made of the total number of hits normalized to 1 vs the threshold
+for each channel are modeled by a complementary error function called ThS curves from now on:
+
+\begin{equation}
+ThS(DAC)=p_{0} \times erfc(\frac{DAC-p_{1}}{p_{2}}) = 
+\newline
+\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} e^{-t^{2}} dt,
+\label{eq_S-curve}
+\end{equation}
+where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
+the 50\% of its maximum and $p_{2}$ give us the width of the ThS curve.
+
+In the absence of external signals (cosmic rays, injected signals, etc) 
+these noise ThS curves show the convolution of the envelope of the 
+electronic noise at the output of the fast shaper (the trigger decision branch on the SKIROC).
+Indeed, the size of this envelope is related to the slow clock frequency.
+
+To reduce to the minimum the presence of cosmic rays signals, 
+we perform runs with short open acquisition windows
+as described in the previous section.
+In Figure \ref{scurve_channels} 
+two result of two threshold scans and the fit by
+a ThS curves for two different channels from the second layer of the setup are shown.
 
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/test.jpg} & \includegraphics[width=2.8in]{figs/fev11_cob.png} 
+  \includegraphics[width=2.8in]{figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{figs/commissioning/scurve_chn2_asic0_layer2.eps}
   \end{tabular}
-  \caption{Left \todo{Temporary picture: La Esperanza del Condenado, J.
-Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visibles.
-The silicon sensors are glued to the PCB in the other side.
-  Right: two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
-\label{ASU}
+\caption{Two threshold scan curves and their associated ThS curves.}
+\label{scurve_channels}
 \end{figure}
 
-\subsection{Data AcQuisition system}
-\label{sec:DAQ}
+The function from equation \ref{eq_S-curve} was fitted to all
+channels data and all the values of $p_{1}$ and $p_{2}$ were saved.
+The final threshold value of every ASIC, in DAC units, was chosen 
+by taking the
 
-The design of the subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
-Current DAQ consists of three modules which are designed to be generic enough to cope with other applications.
-The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs.
-All DIFs are connected by single HDMI cables to the concentrator cards: Gigabit Concentrator Card (GDCC).
-The HDMI connection is used to transmit both slow control and data readout.
-One GDCC controls up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
-The most downstream module is the clock and control card (CCC).
-The CCC provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. spill signals).
+\begin{equation}
+maximum(DAC_{optimal}^{ASIC-j} = <p_{1}^{ASIC-j}> + 5 \times <p_{2}^{ASIC-j}>,230)
+\end{equation}
 
-The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
-The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition.
-Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype. 
-This new version of the DAQ software implements a new mechanism to allow any module to treat and publish data in real time. 
-Those data are made available to any requesting module, in particular to a new online monitor module developed
-for this beam test, allowing for quick online checks of the data quality and integrity.
+if at least the the 30\% of the 64 channels ThS curves in the ASIC could be fitted.
+If only less  than the 30\% of curves of the 64 channels were
+succesfully fit, a global DAC value of 250 was set.
+The $<>$ denotes the average over all the channels on the ASIC.
+The choice of these two values was 
+sustained by previous experiences, see for example \cite{Amjad:2014tha}.
 
-\subsection{Setup}
-\label{sec:setup}
+The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
 
-The prototype tested in beam is composed of 7 layers consisting in one short SLAB each.
-A short SLAB is made of: one single ASU FEV11 equipped with 16 SKIROC2 and 4 wafers glued on the other side (1024 channels);
-an interface card SMBv4; and a DIF. All these elements sit on a "U" shape carbon structure to protect the wafers.
-The full system is then covered by two aluminum plates to provide electromagnetic shielding and mechanical stability.
-The 7 layers are supported by a PVC and aluminum structure that in which can be inserted to 10 layers.
-The distance between two layer slots is 15 mm and this space is used to place tungsten plates of different thicknesses.
-For the beam test described in Section \ref{sec:beamtest}, the layers were placed in positions 1-6 and 10.
-During the commissioning, the slabs have been tested both inside and outside of the structure.
-A photograph showing the prototype can be seen in Figure \ref{proto}. 
-%The mapping from this numbering scheme to real positions in the ASUs is shown in the right plot of Figure \ref{proto}.
+\subsection{S/N ratio in the trigger line}
+\label{sec:comm_trigger_sn}
+
+Similar kind of measurements can be done but using external signals. 
+This will allow to calculate the signal over noise (S/N) ratio to trigger 1 MIP signals.
+To calculate the S/N of the trigger we need to compare the 1 MIP ThS curve and 2 MIP ThS curve. The S/N 
+will be defined as the ratio between the distance of both ThS curves at its 50\% and the width of the 
+ThS curve.
+
+In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP ThS curves obtained for several channel
+in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
+ signals are directly injected in the preamplifier 
+(via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
+From this plot we can extract a S/N ratio of $\sim$12.8. 
+We do not expect large differences with the results that we would obtain with 
+a full equipped SLABs 
+although this board is thought for commissioning and test of the SKIROC ASICS in an
+"ideal" environment in contrast with the FEV
+ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
+%For example: only power pulsing of the analog power is done in this testboard,
+%there is a set of external capacitors on the board connected to some ASIC pins and
+%usually only one channel is tested. This board allows us to commission and debug the SKIROC itself
+%but not the full system.
+
+\begin{figure}[!t]
+    \centering
+  \begin{tabular}{l}
+	\includegraphics[width=4in]{figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
+	\end{tabular}
+\caption{ThS curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
+\label{scurves_injection}
+\end{figure}
+
+We have obtained similar results using real signals, in this case cosmic rays signals by using very long
+acquisition windows of 150 ms at 5 Hz. This is shown 
+in Figure \ref{scurves_cosmics}  where 
+we show the result of the fit to the noise ThS curves for all channels individually (in red) in one of the ASICs of 
+the second layer together with the results of the ThS curve obtained with cosmic rays integrated for all channels
+(black points and blue line).
+%For the cosmic ThS curve we took 30 min of data per point using very long spills (150 ms) in 
+%frequencies of 5Hz and we add up the triggers from all channels together. In addition, using the 
+%knowledge of the MIP value (see next section), we performed a simple cut in the ADC
+%to keep only signals corresponding to a MIP 
+%(pedestal subtracted) $\pm30$ ADC counts. With this cut we try reduce the contribution of muons 
+%traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
+%since we were using simple setups with only single slabs. 
+We expect
+a broader distribution of the cosmic ThS curve since muons can traverse
+the detector at different incidence angles.  
+In addition to this, we should remember that the noise ThS curve do correspond to the real noise 
+distribution but only to the envelope of the noise in the fast shaper, therefore the
+distance between the two ThS curves is smaller than the real distance between noise and signal.
+Therefore, if we calculate the S/N 
+using this plot, the value would be unrealistic but at least provides 
+the comparison between the ThS curve for 1 MIP real and injected signals.
+
+\begin{figure}[!t]
+    \centering
+  \begin{tabular}{l}
+	\includegraphics[width=4in]{figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
+	\end{tabular}
+\caption{ThS curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
+\label{scurves_cosmics}
+\end{figure}
+
+Both ways of estimating the S/N ratio of the trigger have their own limitations
+and dedicted studies in beam test are needed in order to
+precisely determine it.
+In the meanwhile, combining the information contained in the Figs \ref{scurves_injection} and \ref{scurves_cosmics},
+we can estimate the value in energy at wich we have set our trigger threshold.
+This is shown in Figure \ref{trigger_thresholds}.% Two ASICS have a
+%trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=4in]{figs/commissioning/threshold_chip.eps}
+  \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
+\label{trigger_thresholds}
+\end{figure}
+
+\subsection{Prospects}
+\label{sec:comm_prospects}
+
+All the commissioning procedure described above relies in very conservative decisions
+due to the presence of unknown noise sources during most of the commissioning phase. These sources are
+now well know and isolated and therefore a new ``noise commissioning procedure'' has been studied.
+It will consist in an iterative algorithm that first
+will identify and mask the channels giving underflowed signals and afterwards run a set of acquisitions
+in which the number of triggers per channel will be compared with the number of expected triggers
+assuming only cosmic rays as signal. This will allow us to have an
+unambiguous definition of the noise levels channel per channel instead of 
+defining such levels relatively to the total number
+of recorded triggers per ASIC. Finally, once that the noisy channels
+are identified, the optimization of the threshold levels
+will be performed and a last run for identification of noisy channels will be taken using this optimal
+threshold.
+%In this run, we can decide to mask the noisy channels or
+%to increase its own trigger threshold level if we are using Skiroc2a.
+
+Using this new procedure we manage to reduce the number of masked channels by a factor 2 without any loss of performance,
+at least in the laboratory and using 3 of the 7 SLABs. This new procedure will be tested in the next beam test.
+Also, in order to
+optimize the commissioning of the detector,
+we propose a new set of measurements in the next beam test such as
+a scan of optimal delay of the hold values of the trigger using MIP like particles
+and a threshold scan for the determination of the S/N in the trigger line. This later
+can be done by the comparison of ThS curves taken with 1 MIP and $\sqrt{2}$ MIP signals (tilting the detector by 45 degrees).
+
+\section{Performance on positron beam test at DESY}
+\label{sec:beamtest}
+
+The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
+rates from few hundreds of Hz to few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
+The particles beam ies produced as follows: first, the electron/positron synchrotron DORIS II 
+is used to produced a photon beam via bremsstralhung when interacting with a carbon fiber target;
+secondly, these photons are then converted to electron/positron pairs; 
+and, finally, the beam energy is selected with dipole magnets and collimators. 
+In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.
 
@@
 
-\section{Commissioning of the detector}
-\label{sec:commissioning}
-
-This beam test was prepared by a careful and comprehensive commissioning comprising:
-the debug of the
-single SLABSs with special emphasis in the control of the noise and the study of the
-prototype performance in cosmic rays tests.
-
-The SKIROC2 has been already commissioned for previous experiences (see for example the 
-references \cite{Amjad:2014tha,Suehara:2018mqk}). 
-Therefore, all the settings used for the SKIROC2 to obtain 
-the results described in this paper are motivated by these previous experiences. 
-For example, the value of 1.2pF for the preamplifier. 
-With this gain, the SKIROC2 ensures a linearity better than 90\% 
-for 0.5-200 MIPs\footnote{\todo{Is this a fact?}}, which is enough for 
-electromagnetic showers created by few GeV 
-electrons or positrons. The delay of the trigger signal is the same than in 
-reference \cite{Amjad:2014tha,Suehara:2018mqk}: 130 DAC for all ASICS. 
-This value was chosen by selecting the delay in which an injected signal
-of few MIPs of value get the maximum value of ADC. %Finally, the value of the
-%compensation capacitance at the output of the preamplifier has been set to 6pF instead of 
-%4pF to prevent overshots and ripples of the signal used as input to the trigger
-%decision and ADC lines.
-
-\subsection{Optimization of noise levels}
-\label{sec:comm_noise}
-
-The purpose of this phase was to monitor and control the
-noise levels of the prototype. The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
-Studying and control the noise levels
-is crucial since noisy channels may saturate the DAQ faster than physical signals.
-Two different types of noise were identified:
-randomly distributed in time noisy channels 
-and noise bursts affecting to all layers at the same time.
-
-The first type of noise source (randomly distributed in time)
-forced us to define a list of channels to be masked in all 
-layers. Again, two different type of noisy channels have been identified. 
-The first group is compose by randomly distributed in space channels.
-The second group is made of
-a fixed list of channels, all in the same positions for all SLABs, that were giving
-underflowed ADC triggers at high rates. 
-The channels associated to "underflowed-noise" events were identified by means of the online monitoring
-tools. Some preliminary inspections of the FEV11 layout hint that
-the cause of this "underflowed-noise" events may be in an improvable routing of the
-lines from the PIN pad to the SKIROC. 
-For this reason, if a given channel appeared to be associated 
-to "underflowed-noise" events in one of the SLABs, 
-it was masked in all of them, taking in this way the most conservative solution.
-For example, all channels number 37 were masked in all ASICs.
-More studies in this respect are to come.
-
-The list of the noisy channels randomly distributed in time and space was
-defined by means of dedicated data taking runs. 
-These runs were characterized by: their short acquisition windows (of 2.5 ms, only 1.1 ms 
-of effectively data taking time), their low
-spill frequency (5 Hz) to minimize the chances of having real events due to cosmic rays 
-hitting the detector during the
-data taking; and the relatively high trigger threshold values between 250 and 400 DAC 
-(which is equivalent to $\sim$0.5-2 MIP, see Section \ref{sec:comm_trigger} for more 
-information). The full process was an iterative process starting with several repetitions
-of runs at a high threshold value and then some iterations at lower threshold each up to 250 DAC. 
-In every of there iterations, the channels identified as noisy were masked.
-A full run involved 3-5 threshold values and at least two repetitions per value.
-Again, we decided to follow a conservative approach for list the noisy channels to be masked:
-if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC
-it was added to the list.
-
-In addition to the different noisy channel types described above, we also have
-masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
-listed as noisy) or if a Si-wafer was misworking (high leakage currents). In these cases 
-and in all mentioned above, the masking involved two steps: disabling of the trigger and 
-the disabling of the power of the preamplifier of that channel. A summary of the results of the masking procedure is shown in Figure \ref{noisycells}.
-
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{l}
-  \includegraphics[width=4in]{figs/commissioning/masked_layer.eps} \\
-  \includegraphics[width=4in]{figs/commissioning/masked_chip.eps}
-  \end{tabular}
-\caption{Ratio of channels that are marked as noisy in all slabs. 
-Top: inventory of the different type of noisy channels per slab. 
-Bottom: break up of the noisy channels per ASIC. We see two spikes in the number of channels masked due to routing issues in the ASICs 1 and 9. 
-These two ASICs are located near the SMB where the density of lines (data and power transmission) is higher, complicating in this way the
-routing. The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
-in the second plot since they are fully masked.}
-\label{noisycells}
-\end{figure}
-
-We observed that the noise bursts happening coherently at the same time in all SLABS
-was associated to cases when the electrical isolation between SLABs was broken.
-This is a hint of a system effect as can be the appearence of
-grounding loops or noise in the power supplies.
-The issue was circumvented by improving the electrical isolation of single layers.
-We have also observed that the noise bursts happened only at the end of long acquisitions therefore, in addition to the improved isolation,
-we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
-However, more studies in the laboratory are needed in order to fully understand these issues.
-
-\subsection{Threshold determination}
-\label{sec:comm_trigger}
-
-Once that the SKIROC main settings have been fixed and the masking of the noisy channels at a relatively high threshold value
-has been done, the final step is the selection of the optimal trigger threshold values.
-For that, we perform dedicated runs in which we scan a reasonable range of trigger threshold values (in DAC units)
-with all channels enabled (excepted the marked as noisy). For each of the DAC points
-we took data only during $\sim$ 1 minute per DAC in order to speed up the commissioning.
-Plotting the total number of hits normalized to the maximum vs the DAC
-for each channel gives the so-called S-curves. In the absence of external signals (cosmic rays, injected signals, etc) 
-these noise S-curves show the convolution of the envelope of the 
-electronic noise at the output of the fast shaper (the trigger decision line).
-Indeed, the size of this enveloppe is related to the slow clock frequency
-(larger periods increase the possibility to find a noise variation over the threshold).
-
-To reduce to the minimum the
-presence of cosmic rays signals, we perform runs with short open acquisition windows (1.1 ms)\footnote{The acquisition window is defined by means
-  of a external pulse generator that emulates similar spill conditions than at the ILC. For DAQ needs, the actual data recording starts 1.4 ms after
-rising edge of the spill signal arrives. In this paper we will always refer to the effectively open acquisition window not including the mentioned 1.4 ms.}. 
-In Figure \ref{scurve_channels} 
-two S-curves of two different channels from the second layer of the setup are shown.
-
-The S-curves are fitted to a complementary error function
-\begin{equation}
-S(DAC)=p_{0} \times erfc(\frac{DAC-p_{1}}{p_{2}}) = 
-\newline
-\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} \exp^{-t^{2}} dt,
-\label{eq_S-curve}
-\end{equation}
-where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
-the 50\% of its maximum and $p_{2}$ give us the width of the S-curve.
-
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{ll}
-  \includegraphics[width=2.8in]{figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{figs/commissioning/scurve_chn2_asic0_layer2.eps}
-  \end{tabular}
-\caption{Two S-curves obtained during noise runs.}
-\label{scurve_channels}
-\end{figure}
-
-The function from equation \ref{eq_S-curve} was fitted to all
-channels data and all the values of $p_{1}$ and $p_{2}$ were saved.
-To decide the final trigger threshold value for the full ASIC, we took the maximum between:
-
-\begin{equation}
-DAC_{optimal}^{ASIC-j} = <p_{1}^{ASIC-j}> + 5 \times <p_{2}^{ASIC-j}>
-\end{equation}
-and 230 if at least the the 30\% of the 64 channels S-curves in the ASIC could be fitted. 
-If less than the 30\% of the channels were fit
-we took a most conservative value of 250 DAC for the threshold of the ASIC.
-The election of these two values was 
-sustained by previous experiences, see for example \cite{Amjad:2014tha}.
-
-The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
-
-\subsection{S/N ratio in the trigger line}
-\label{sec:comm_trigger_sn}
-
-Similar kind of measurements can be done but using external signals. 
-This will allow to calculate the signal over noise (S/N) ratio to trigger 1 MIP signals.
-To calculate the S/N of the trigger we need to compare the 1 MIP S-curve and 2 MIP S-curve. The S/N 
-will be defined as the ratio between the distance of both S-curves at its 50\% and the width of the 
-S-curve.
-
-In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP S-curves obtained for one channel
-in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
-"fake" signals are directly injected in the preamplifier (via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
-From this plot we can extract a S/N ratio of $\sim$12. 
-We don expect large differences with the results that we would obtain with 
-full equipped SLABs 
-although this board is thought for commissioning and test of the SKIROC ASICS in an
-"ideal" environment in contrast with the FEV
-ASUS that are optimized to meet detector constraints and to hold several ASICs at the same time.
-For example: only power pulsing of the analog power is done in this testboard,
-there is a set of external capacitors on the board connected to some ASIC pins and
-usually only one channel is tested. This board allows us to commission and debug the SKIROC itself
-but not the full system.
-
-\begin{figure}[!t]
-    \centering
-  \begin{tabular}{l}
-	\includegraphics[width=4in]{figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
-	\end{tabular}
-\caption{S-curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
-\label{scurves_injection}
-\end{figure}
-
-We have obtained similar results using real signals, in this case cosmic rays signals. This is shown 
-in Figure \ref{scurves_cosmics}  where 
-we show the result of the fit to the noise S-curves for all channels (in red) in one of the ASICs of 
-the second layer together with the results of the S-curve with cosmic rays (black points and blue 
-line). For the cosmic S-curve we took 30 min of data per point using very long spills (150 ms) in 
-frequencies of 5Hz and we add up the triggers from all channels together. In addition, using the 
-knowledge of the MIP value (see next section), we performed a simple cut in the ADC
-to keep only signals corresponding to a MIP 
-(pedestal subtracted) $\pm30$ ADC counts. With this cut we try reduce the contribution of muons 
-traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
-since we were using simple setups with only single slabs. For all these reasons, we expect
-a broader distribution of the cosmic S-curve. This is one of the reasons why, if we calculate the S/N 
-using this plot, the value would be unrealistic (much lower, indeed). 
-In addition to this, we should remember that the noise S-curve do correspond to the real noise 
-distribution but only to the envelope of the noise in the fast shaper, therefore the
-distance between the two S-curves is smaller than the real distance between noise and signal.
-
-\begin{figure}[!t]
-    \centering
-  \begin{tabular}{l}
-	\includegraphics[width=4in]{figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
-	\end{tabular}
-\caption{S-curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
-\label{scurves_cosmics}
-\end{figure}
-
-In conclusion, both ways of estimating the S/N ratio of the trigger have their own limitations but in 
-both cases, the 50\% of the S-curve of 1 MIP are compatible within $\pm10$ ADC. This allow us
-to, at least, estimate the relative distance between our final trigger threshold for every ASIC and 
-the 1 MIP position by combining the information extracted from Figs \ref{scurves_injection} and \ref{scurves_cosmics}.
-This is shown in Figure \ref{trigger_thresholds}. Two ASICS ($\sim2\%$) have a
-trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=4in]{figs/commissioning/threshold_chip.eps}
-  \caption{Summary of trigger threshold settings for all ASICs in the setup.
-The values are given in DAC and in estimated MIP units, using the distance between two MIPs from Figure \ref{scurves_injection}.
-The uncertainty quoted in the right axis is estimated from difference between the 50\% position of the S-curve for one MIP extracted from Figured \ref{scurves_injection} and \ref{scurves_cosmics}.}
-\label{trigger_thresholds}
-\end{figure}
-
-\subsection{Prospects}
-\label{sec:comm_prospects}
-
-All the commissioning procedure described above relies in very conservative decisions
-due to the presence of unknown noise sources during most of the commissioning phase. These sources are
-now well know and isolated and therefore a new ``noise'' commissioning procedure has been studied.
-It will consist in an iterative algorithm that first
-will identify and mask the "underflowed-noisy" channels and afterwards run a set of acquisitions
-in which the number of triggers per channel will be compared with the number of expected triggers
-assuming only cosmics rays as signal. This will allow us to have an
-unambiguous definition of the noise levels channel per channel instead of 
-defining such levels relatively to the total number
-of recorded triggers per ASIC. Finally, once that the noisy channels
-are identified, the optimization of the threshold levels
-will be performed and a last run for identification of noisy channels will be taken using this optimal
-threshold. In this run, we can decide to mask the noisy channels or
-to increase its own trigger threshold level if we are using Skiroc2a.
-
-Using this new procedure we manage to reduce the number of masked channels by a factor 2 without any loss of performance,
-at least in the laboratory and using 3 of the 7 SLABs. This new procedure will be tested in the next beam test.
-Also, in order to
-optimize the commissioning of the detector,
-we propose a new set of measurements in the next beam test such as
-a scan of optimal delay of the hold values of the trigger using MIP like particles
-and a threshold scan for the determination of the S/N in the trigger line. This later
-can be done comparing 1 MIP and $\sqrt{2}$ MIP (tilting the detector by 45 degrees) signals.
-
-\section{Performance on positron beam test at DESY}
-\label{sec:beamtest}
-
-The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
-rates from few hundreds of Hz to few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
-These positrons are produced in the following way: first, the electron/positron synchrotron DORIS II 
-is used to produced a photon beam via bremsstralhung when interacting with a carbon fiber target;
-secondly, these photons are then converted to electron/positron pairs; 
-and, finally, the beam energy is selected with dipole magnets and collimators. 
-In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.
-
-The prototype tested in beam in June 2017 consisted of 7 layers as explained in Section \ref{sec:setup}.
+A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
+Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10.
+For the beam test described in Section \ref{sec:beamtest} all the layers were separated by equal distances of 15 mm
+except the last one which was at 60 mm of its nearest. In the following sections, we will refer to layers number 1 to 7, where
+the 1 is the closest to the beam pipe and 7 is the farthest.
 The detector was exposed to a positron beam in the DESY test beam area (line 24).
 By means of an external pulse generator we defined the length of the acquisition window to be
-3.7 ms at a frequency of 5 Hz, emulating in this way similar conditions than the ILC will have.
+3.7 ms at a frequency of 5 Hz.
 The detector was running in power pulsing mode without any extra active cooling system.
@@
 
-\begin{itemize}
-\item Commissioning and calibration without tungsten absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs);
-\item magnetic field tests up to 1 T in the PCMag;
-\item response to electrons with fully equipped detector, i.e. sensitive parts {\it and} W absorber.
-\end{itemize}
-
-For the first two points from above, we used the SiW-ECAL in the tracker mode, {\it i.e.} without 
-intercalated tungsten plates. Due to the low material budget of our setup when the tungsten is not 
-included, a beam of positrons of few GeV of energies provides satisfactory data for calibration since 
-the positrons deposit the minimum amount of energy by ionization.
-The calibration of the detector was realized 
-by directing the 3 GeV positron beam on 81 positions equally distributed over the surface of the 
-detector.
-These data were used for pedestal estimation and energy calibration.
-Calibration and pedestal analysis was done for all single layers not requiring track reconstruction.
-The study of these data is discussed in Section \ref{sec:pedestal} for the pedestal and noise studies and Section \ref{sec:mip} for the results of the calibration.
-
-For the tests inside the magnetic field, a special PVC structure was
+\begin{enumerate}
+\item Calibration without tungsten absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs) directed to 81 position equally distributed over the modules.
+\item Test in magnetic field up to 1 T using the PCMag. For this test a special PVC structure was
 designed and produced to support one single SLAB.	
 The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
-mechanical slab itself were able
-to handle strong magnetic fields; second to prove the stability of the performance during these tests.
-We took several runs, with 0, 0.5 and 1 T magnetic fields with and without 3 GeV positron beam and 
-we observed that the pedestal and noise values are independent of the magnetic field (see Section 
-\ref{sec:magnetic}). The study of the MIP calibration stability will be discussed in future 
-publications where full studies of the data including comparison with simulations should be included.
-
-To fulfill the last point of the list we inserted W plates of different thicknesses between the 
-sensitive layers. Then we performed
-a scan of energies of the positron beam: 1-5.8 GeV.
-We tested the response of the detector with three different configurations of the W repartition.
-The accumulated amount of tungsten, in radiation length units, $X_{0}$, in front of each of the 
-SLABs was:
+mechanical consistency of the SLAB itself are able
+to handle strong magnetic fields; 
+second to check the quality of the data and the performance of the detector during the data taking when running
+in a magnetic field.
+\item Response to electrons of different energies with fully equipped detector, i.e. sensitive parts {\it and} W absorber, with three different repartitions of the absorber material:
 \begin{itemize}
@@
 \end{itemize}
+\end{enumerate}
 
-Preliminary results of the raw electromagnetic shower profiles look promising but will not be 
-discussed in this article since deeper analysis and comparison with montecarlo simulations
-will be needed to extract conclusive results from the data. This will be the topic of a future 
-article, possibly combining data with future beam tests that are currently in preparation. What it
-is included in this article, in Section \ref{sec:showers} is the study of the pedestals in this events.
+First reports on this beam test can be find in
+Refs. \cite{Irles:2018uum,Irles:2018hcd}. In this paper we discuss in more detail
+the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
+We show also results on the pedestal and noise stability when running inside
+a magnetic field in Section \ref{sec:magnet}. Finally, a first peek to the 
+response and stability of the detector in electromagnetic showers events is discussed in 
+Section \ref{sec:showers}.
 
-\subsection{Pedestal and noise studies with the SiW-ECAL in tracker mode}
+\subsection{Response to MIP-acting positrons}
+\label{sec:calib}
+
+\subsubsection{Pedestal and noise determination}
 \label{sec:pedestal}
 
-Due to the way that the SKIROC2 ASICs work, it is possible to extract the pedestals
-simultaneously to the recording of signals from particle interactions. Indeed, when a channel
-is triggered, the rest are read out at the end of the slow clock period (usually called BCID - for bunch crossing identity)  and marked as
-non triggered channels. This allows us to reconstruct the pedestal distribution
-for all channels and for all SCAs. These distributions are fitted with a Gaussian
-and the pedestal value are associated with the mean of the result of the fit.
-These values will be, afterwards, subtracted to the ADC recorded by the SKIROC2 for all channels and SCAs.
-The noise is associated to the widht of the pedestal distribution.
-The calibration runs have been used to calculate the pedestal distribution reference values of the detector.
+The calibration runs have been used to calculate the pedestal distribution reference values 
+and the noise levels (the width of the pedestal distrution) of each channel.
 In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
-subtracting the pedestal mean position.
+subtracting the pedestal mean position. The results of the MIP calibration fit are included (red) and explained in the next version.
+The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range.
+The signal distribution is integrated over all SCAs.
 
@@
   \end{tabular}
-  \caption{Pedestal (blue dashed line) and signal (black continuous line) distribution for one channel in the third layer.
-The results of the MIP calibration fit are included (red).
-The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range.
-The signal distribution is integrated over all SCAs.}
+  \caption{Pedestal (blue dashed line) and signal (black continuous line) distribution for one channel in the third layer.}
 \label{signal_pedestal}
@@
 
-In Figure \ref{pedestal_channel} (left) we observe that both the pedestal position for each SCA in the same channel can be
-different in few \%s. In the case of the pedestal mean position, these differences are even larger between different ASICs in the same
-layer (Figure \ref{pedestal_layer}, left plot) or between layers (Figure \ref{pedestal_all}, left). This is the reason of
-performing the pedestal correction layer-, chip-, channel- and SCA-wisely.
-For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_channel}, \ref{pedestal_layer} and \ref{pedestal_all}.
+The pedestal is calculated as the mean position of
+the ADC distribution of channels without trigger. The noise is
+associated to the width of such distribution.
+The pedestal correction is done layer-, chip-, channel- and SCA-wisely due to the large spread of values between pedestals, as observed in 
+Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
+For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
+From now on, the pedestal correction is applied to all the results presented.
 
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{figs/pedestal/ped_width_layer2_chip4_cell10.eps}
-  \end{tabular}
-  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
-\label{pedestal_channel}
-\end{figure}
+%\begin{figure}[!t]
+%  \centering
+%  \begin{tabular}{ll}
+%    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{figs/pedestal/ped_width_layer2_chip4_cell10.eps}
+%  \end{tabular}
+%  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
+%\label{pedestal_channel}
+%\end{figure}
 
@@
 
-\subsubsection{Pedestal and noise in large magnetic fields}
-\label{sec:magnetic}
+\subsubsection{Energy calibration and tracking efficiency}
+\label{sec:mip}
 
-For the tests inside the magnetic field we used the SLAB of the first layer
-in the special PVC struture mentioned at the begining of this section. We should also mention that
-the PCMag is in a different area (downstream) on the same beam line,
-therefore, due to the presence of additional collimators the beam rates are lower.
-
-We divided the
-data taking in 3 stages in this order:
-a long run (13h) with a magnetic field of 1 T, a second and shorter run of 3 hours with 0.5 T and a final run with the magnet off.
-In the cases were we had beam, we used the 3 GeV positron beam settings impacting in the ASIC number 12.
-
-The comparison of the pedestal values and noise levels between the reference run in the stack
-and the different runs in the magnetic field are shown in Figure \ref{pedestal_magnetic}.
-We see that in both cases, the agreement is perfect within the statistical uncertainties.
-Due to the lower rates in this beam area, the
-analysis is only done up to few SCAs.
-
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{figs/pedestal/1T/summary_noise_chip12.eps}
-  \end{tabular}
-  \caption{Average deviation of the pedestal mean position (left) and width (right) for all channels in the ASIC 12.
-The values are given in MIP units obtained from calibration (see Section \ref{sec:mip}).}
-\label{pedestal_magnetic}
-\end{figure}
-
-\subsection{MIP response and tracking efficiency with the SiW-ECAL in tracker mode}
-\label{sec:mip}
+A Landau function convoluted with a Gaussian is fit to the resulting hit distribution. 
+The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
+conversion from ADC units to energy in MIP units.
+We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
+available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.
 
@@
 
-After the calculation of the pedestals for each channels and SCA, these are subtracted and the same data (without track
-recognision) are used for the calibration.
-A Landau function convoluted by a Gaussian is fit to the resulting hit distribution
-in ADC units.
-The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
-conversion from ADC to energy.
-We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
-available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.
-
 We checked the MIP 
-calibration by selecting tracks that cross the detector parallel to its normal
-and filling a histogram with the energy measured by each channel with a hit.
-We did this for all calibration runs together.
+calibration in all callibrated channels by selecting tracks
+incident perpendicullary to the layers surface.
 The results are shown in figure \ref{mip3peaks} where the single channel energy 
 distribution for MIPs is shown for all calibrated channels in the same distribution. 
-The distribution nicely fits in the 1 MIP spectrum, showing in that way the good
-performance of our default calibration that, for simplicity, was done without requiring
-tracking reconstruction.
-The distribution also reveals the presence of a second and third peak due to events involving multiple 
+The maximum peaks at 1 MIP as expected after a good calibration.
+In addition to this, a second and a third peak
+appear visible. These peaks are due to
+events involving multiple 
 particles crossing the detector.
@@
     \end{tabular}
-    \caption{The single channel energy distribution (for all calibrated channels) for 3 GeV positron tracks acting as MIPs.}
+    \caption{Energy distribution for all callibrated channels when selecting tracks of 3 GeV positron acting as MIPs.}
 \label{mip3peaks}
@@
 the single hit detection efficiency we define a high purity sample of
-events of positrons traversing the detector perpendicularly by selecting
-tracks with at least 4 layers (of 7 possible) with a hit in exactly the same channel. Afterwards we 
+events by selecting
+tracks with at least 4 layers with a hit in exactly the same channel. Afterwards we 
 check if the other layers have or not a hit in the same channel (expanding the search
@@
 Lower efficiencies in the first layer are related to the presence of
-noisy channels not well identified in the commissioning phase that boosted the filling
-of the the 15 SCAs of three ASICs. In the last layer (separated from the
+noisy channels not spotted during the commissioning. In the last layer (separated from the
 other layers by four slots of 1.5 cm instead of only one) we also observe few small deviations
 from the $\sim100\%$ which are indeed
-associated to a slight misalignment of the tracks visible only in the outliers channels. 
+associated to a slight misalignment of the detector.
 If we remove these channels from the analysis
@@
 
-\subsubsection{S/N ratio in the ADC}
+\subsubsection{S/N ratio in the charge measurement for MIP interactions}
 \label{sec:sn}
 
-The signal-over-noise ratio in the ADC (corresponding to the slow shaper of the SKIROC2) is defined 
+The signal-over-noise ratio in the charge measurement (corresponding to the slow shaper of the SKIROC2) is defined 
 as the ratio between the most-probable-value of
 the Landau-gauss function fit to the data (pedestal subtracted) and the noise (the pedestal width). This quantity 
-has been calculated for all channels and all slabs and, in average, it corresponds to 20.4.
+has been calculated for all channels and all layers. The average S/N is to 20.4.
 Results are summarized in Figure \ref{mipandSN}, rightmost plot.
+
+\subsection{Pedestal and noise stability in a magnetic field}
+\label{sec:magnetic}
+
+The data taking inside the magnetic field has been divided in three steps:
+a) a with a magnetic field of 1 T; b) a run with 0.5 T; c) a final run with the magnet off.
+The beam, 3 GeV positrons, was hitting in the area of the PCB readout by the ASIC number 12.
+
+The pedestal positions and noise levels of the channels of the ASIC 12 when the
+SLAB is inside of the PCMag are compared with the results from the calibration run described in the previous section.
+This is shown in Figure \ref{pedestal_magnetic}.
+We see that the agreement is perfect within the statistical uncertainties.
+Due to the lower rates in this beam area, the
+analysis is only done up to few SCAs.
+
+\begin{figure}[!t]
+  \centering
+  \begin{tabular}{ll}
+    \includegraphics[width=2.8in]{figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{figs/pedestal/1T/summary_noise_chip12.eps}
+  \end{tabular}
+  \caption{Average deviation of the pedestal mean position (left) and width (right) for all channels in the ASIC 12.}
+\label{pedestal_magnetic}
+\end{figure}
 
@@
 
-The pedestal stability in events with large amount of charge deposited by the ASICs, as are the 
-electromagnetic shower events, has been also calculated. All the results shown in this section correspond to data taken during the tungsten program, 
-using the W-configuration number 2 when shooting the beam in the ASIC 12 (and partially in the 13). Only the ASIC 12 is used in the analysis. For other configurations and 
-positions of the beam we get comparable results. We used also a calibrated data sample were the pedestal values have been 
-subtracted and the MIP calibration has been applied. 
-Therefore, all energy measurements are given in MIP units and the pedestal
-values are expected to be equal to zero.
+In this section we discuss the pedestal stability in events with large amount of charge collected by the ASICs, as are the 
+electromagnetic shower events. All the results shown in this section correspond to data taken during the tungsten program, 
+using the W-configuration number 2 when shooting the beam in the area registered by the ASIC 12 (and partially in the 13). 
+Only information recorded by ASIC 12 is used in the analysis. For other configurations we get comparable results.
 In order to select a high purity of
@@
     \end{tabular}
-    \caption{Left: mean position of the projection of the pedestal distribution of all channels of ASIC 12 in the Layer 3 calculated when different energies are collected in the ASIC (in bins of 10 MIPs).
-Right: same but as a function of the number of hits.
-In both cases, the results are shown for few SCA.
+    \caption{Left: mean position of the projection of the pedestal distribution of all channels
+      calculated when different energies are collected in the ASIC (in bins of 10 MIPs).
+      Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA.
       The points for the curves with SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
@@
 is plot as a function of the total energy measured by the ASIC (or the total number of hits).
-We see that in all cases, the slopes of the curves 
+We see that in both cases, the shapes of the curves 
 for each SCA are very similar.
-This is feature is known and it is due to the architecture of the SKIROC2 (and 2a) ASICs 
+This feature is known and it is due to the architecture of the SKIROC2 ASICs 
 where high inrush of currents can slightly shift the baseline of the analogue power supply. 
-This feature is foreseen to be removed from the SKIROC3 ASICs.
+%This feature is foreseen to be removed from the SKIROC3 ASICs.
 
@@
 are deposited in the ASIC ({\it i.e.} at larger beam energies or for the layers in the maximum of the shower
-profile). We also observed that this alternation is only SCA dependent and not BCID dependent.
+profile). We also observed that this alternation is only SCA dependent and does not depends
+on the time in which the deposit of energy occurs within the acquisition.
 This is not yet fully understood although the fact that the effect is observed in
-alternate SCAs hints to some issue affecting the digital part of the ASIC 
+alternate SCAs hints that something is affecting to the digital part of the ASIC 
 (where the SCAs enter in play).
-
 Dedicated tests in the laboratory and in the beam are needed in order to clarify this issue.
@@
 
-\subsection{Fake triggers filtering}
+\section{Summary}
+\label{sec:summary}
+
+The R\&D program of the highly granular SiW-ECAL detector is in an exciting phase. 
+After the proof of principle of the imaging calorimetry concept using the physics prototype, the 
+technological prototype is being constructed and tested. In this document we describe the commissioning and
+beam test performance of a prototype built in with the first fully assembled
+detector elements.
+
+A very comprehensive and detailed commissioning procedure has been established and optimized
+allowing us to identify and isolate the different noise sources that could spoil the data taking.
+The beam test has provided a lot of useful data to study 
+the performance of the detector and  to perform
+a channel by channel calibration.
+A full analysis of the MIP calibration within magnetic field and
+the response of the prototype in electromagnetic shower events
+will be covered in a future document.
+In addition, the results shown here serve as input
+for ongoing and future R\&D.
+
+\section{Outlook}
+\label{sec:outlook}
+
+In parallel to the work described here, several R\&D efforts are being carried.
+One of these efforts is directed to the design and test of new ASICs.
+In fact, a new generation of SKIROC2, the 2a, has been delivered
+and it is being tested in the dedicated testboards and it has been integrated in new ASUs.
+In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
+In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
+
+Many efforts are also concentrated in the construction and test of long SLABs
+made of several ASUs enchained since we know that the ILD ECAL will host long layers of up to $\sim$2.5m.
+This device constitutes a technological challenge in both aspects, the mechanical
+(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
+and the electrical (i.e. transmission of signals and high currents).
+For example, interconnections between ASUs and between ASU and interface card are one of
+the most involved parts of the assembly
+and require close collaboration between mechanical and electronic engineers.
+The construction and test of a long SLAB prototype
+of $\sim8$ ASUs is currently ongoing.
+%Therefore, many efforts are focused in the construction and test of such long 
+%layers made of chains of ASUs (up to $\sim$15 ASU) 
+%as well as in the standardization of the interconnections.
+
+In parallel to the ASUs equipped with BGA packaged ASICs, a different proposal for the ASU
+design is being investigated. This is motivated by the high density of channels
+demanded by the Particle Flow algorithms. Indeed, the FEV11 thickness is 1.6 alone and 2.7 mm
+including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
+In this alternative PCB design the ASICs
+are directly placed on board of the PCB in dedicated cavities.
+The ASICS will be in semiconductor packaging and wire bonded to the PCB. This is the so-called COB (chip-on-board) version of the ASU.
+A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
+with a total thickness of 1.2 mm allowing for a potential denisty of 10000 channels/dm$^{3}$ has been produced and tested in the laboratory
+showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{cob}.
+
+\begin{figure}[!t]
+  \centering
+    \includegraphics[width=2.8in]{figs/fev11_cob.png} 
+  \caption{Two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
+\label{cob}
+\end{figure}
+
+Finally, many efforts in the compactification of
+the DAQ and the ASUs ({\it i.e.} the chip on board versions of the 
+ASUs described in Section \ref{sec:ASU}) are being
+conducted by the SiW-ECAL collaboration.
+
+It is foreseen that all these developments, with the exception of the SKIROC3, will be tested with particle beams during 2018-2019.
+
+\acknowledgments
+
+This project has received funding from the European Union{\textquotesingle}s Horizon 2020 Research and Innovation program under Grant Agreement no. 654168.
+This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
+in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
+(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).
+The research leading to these results has received funding from the People Programme (Marie
+Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
+under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
+programme coordinated by Campus France.
+The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).
+
+\appendix
+\section{Apendix: Filtering of fake triggers}
 \label{sec:retriggers}
@@
 This effect creates around 10-15\% of empty events which are easily filter and removed from the
-analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to $\sim3\%$
-  due to a decrease of the OR64 by a factor X.}
+analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to the $\sim3\%$
+thanks to to a decrease of the OR64 size by a factor X.}
 
@@
 
-Another well know issue is related to the appearance of bunches of consecutive fake triggers that
-quickly fill several SCA in consecutive slow clock periods. These events are also
+Another well know issue is the appearance of bunches of consecutive fake triggers, called retriggers,
+that saturates the DAQ. These events are also
 characterized by triggering many channels (some times even all channels of an ASIC) at the same time.
@@
 therefore, any voltage dip can ve seen as signal by the preamplifiers. The presence of a high inrush of current
-due to many channels triggered at the same time can create these voltage dips.
+due to many channels triggered at the same time can create these voltage dips
+and produce the so called plane events (most of the channels trigered at once).
 In previous studies ({\it i.e.} reference \cite{Amjad:2014tha}), the ratio of retriggers and plane events
@@
 
-Studying the MIP calibration data of this beam test we have noticed that most of the retriggers and plane events are originated 
+Studying the MIP calibration data of this beam test we have noticed that the larger concentration of the retriggers and plane events are originated 
 in
-ASICs far from the beam spot. Even more, hot spots tend to appear near the channels 37 and the channels tagged as ``underflowed'' 
-during
-the commissioning phase. The amount these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
+ASICs far from the beam spot. Even more, hot spots tend to appear near the channels 37 and the channels masked
+as suspicious of suffering from routing issues. The amount these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
 interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 KHz) and at higher rates even larger than $40\%$ in other 
@@
 retriggers in other areas of the PCB. 
-This correlation corresponds to $\sim8$ BCIDs (1.6 $\mu$s) which hints
+This correlation corresponds to $\sim$1.6 $\mu$s which hints
 of a distortion on the analogue power supply when
-the signal that informs the DIF that one ASIC memory has been filled is transmitted through the PCB.
+the signal that informs the DIF that one ASIC memory is full is transmitted through the PCB.
 
 All this information and dedicated studies in the laboratory will be used for the
-improvement of the power delivery, the PCB design and for further SKIROC developments 
+improvement of the power supplying system, the PCB design and for further SKIROC developments 
 with the possible approval the ILC in the scope.
-
-\section{Summary and prospects}
-\label{sec:prospects}
-
-The R\&D program of the highly granular SiW-ECAL detector is in an exciting phase. 
-After the proof of principle of the imaging calorimetry concept using the physics prototype, the 
-technological prototype is being constructed and tested. In this document we describe the commissioning and
-beam test performance of a prototype built in with the first fully assembled
-detector elements (still only 7 over the total of $\sim$10000 to be in the ILD).
-
-A very comprehensive and detailed commissioning procedure has been established and optimized
-allowing us to identify and isolate the different noise sources that could spoil the data taking.
-The beam test has provided a lot of useful data, allowing first for the study of 
-the performance of the detector and secondly 
-for its channel by channel calibration. 
-A full analysis including the comparison with simulations of the 
-second part of the data taking program (the electromagnetic showers) is to come.
-During both phases, the commissioning and the beam test,
-we have collected a good amount of data and results
-that will serve as input for future improvements on
-the design of the ASUs, the SKIROC and the upstream DAQ.
-
-In parallel to the work described here, several R\&D efforts are being carried.
-For example, we know that the ILD ECAL will host long layers of up to $\sim$2.5m.
-A long layer constitutes a technological challenge in both aspects, the mechanical
-(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
-and the electrical (i.e. transmission of signals and high currents).
-For example, interconnections between ASUs and between ASU and interface card are one of
-the most involved parts of the assembly
-and require close collaboration between mechanical and electronic engineers.
-Therefore, many efforts are focused in the construction and test of such long 
-layers made of chains of ASUs (up to $\sim$15 ASU) 
-as well as in the standardization of the interconnections. 
-In addition, many efforts in the compactification of
-the DAQ and the ASUs ({\it i.e.} the chip on board versions of the 
-ASUs described in Section \ref{sec:ASU}) are being
-conducted by the SiW-ECAL collaboration.
-
-\acknowledgments
-
-This project has received funding from the European Union{\textquotesingle}s Horizon 2020 Research and Innovation program under Grant Agreement no. 654168.
-This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
-in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
-(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).
-The research leading to these results has received funding from the People Programme (Marie
-Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
-under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
-programme coordinated by Campus France.
-The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).
 

### 2018-06-11 performance-paper-draft/longversion/draft.tex
modify structure to split the paper in two versions: long version with JINST style and short with NIM style. For the short, only a raw copy of the long is done

--- 2018-06-11 performance-paper-draft/draft.tex
@@
 %\begin{tabular}{lll}
-%  \includegraphics[width=1.8in]{figs/test.jpg} &
-%  \includegraphics[width=1.8in]{figs/test2.jpg} &
-%  \includegraphics[width=1.8in]{figs/test3.jpg}
+%  \includegraphics[width=1.8in]{../figs/test.jpg} &
+%  \includegraphics[width=1.8in]{../figs/test2.jpg} &
+%  \includegraphics[width=1.8in]{../figs/test3.jpg}
 %\end{tabular}
@@
   \centering
-    \includegraphics[width=4in]{figs/skiroc2_block.eps}
+    \includegraphics[width=4in]{../figs/skiroc2_block.eps}
 \caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
@@
   \begin{tabular}{l}
-    \includegraphics[width=4in]{figs/ASU_geometry1.eps}  \\
-    \includegraphics[width=4in]{figs/ASU_geometry2.eps}  \\
+    \includegraphics[width=4in]{../figs/ASU_geometry1.eps}  \\
+    \includegraphics[width=4in]{../figs/ASU_geometry2.eps}  \\
   \end{tabular}
@@
   \centering
-    \includegraphics[width=2.8in]{figs/test.jpg} 
+    \includegraphics[width=2.8in]{../figs/test.jpg} 
   \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
@@
 \begin{tabular}{l}
-\includegraphics[width=6.0in]{figs/assembly.png} 
+\includegraphics[width=6.0in]{../figs/assembly.png} 
 \end{tabular}
@@
   \begin{tabular}{l}
-  \includegraphics[width=4in]{figs/commissioning/masked_layer.eps} \\
-  \includegraphics[width=4in]{figs/commissioning/masked_chip.eps}
+  \includegraphics[width=4in]{../figs/commissioning/masked_layer.eps} \\
+  \includegraphics[width=4in]{../figs/commissioning/masked_chip.eps}
   \end{tabular}
@@
   \begin{tabular}{ll}
-  \includegraphics[width=2.8in]{figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{figs/commissioning/scurve_chn2_asic0_layer2.eps}
+  \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn2_asic0_layer2.eps}
   \end{tabular}
@@
   \begin{tabular}{l}
-	\includegraphics[width=4in]{figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
+	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
 	\end{tabular}
@@
   \begin{tabular}{l}
-	\includegraphics[width=4in]{figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
+	\includegraphics[width=4in]{../figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
 	\end{tabular}
@@
   \centering
-  \includegraphics[width=4in]{figs/commissioning/threshold_chip.eps}
+  \includegraphics[width=4in]{../figs/commissioning/threshold_chip.eps}
   \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
@@
 \begin{tabular}{l}
-\includegraphics[width=4.0in]{figs/proto.png} 
+\includegraphics[width=4.0in]{../figs/proto.png} 
 \end{tabular}
@@
   \begin{tabular}{l}
-    \includegraphics[width=4in]{figs/mip_pedestal_example.eps}
+    \includegraphics[width=4in]{../figs/mip_pedestal_example.eps}
   \end{tabular}
@@
 %  \begin{tabular}{ll}
-%    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{figs/pedestal/ped_width_layer2_chip4_cell10.eps}
+%    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{../figs/pedestal/ped_width_layer2_chip4_cell10.eps}
 %  \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{figs/pedestal/width_mean_layer2.eps}
+    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{../figs/pedestal/width_mean_layer2.eps}
   \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/pedestal/h_ped_mean.eps} & \includegraphics[width=2.8in]{figs/pedestal/h_ped_width.eps}
+    \includegraphics[width=2.8in]{../figs/pedestal/h_ped_mean.eps} & \includegraphics[width=2.8in]{../figs/pedestal/h_ped_width.eps}
   \end{tabular}
@@
   \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{figs/MIP/MIPsummary_title.eps} & \includegraphics[width=2.8in]{figs/MIP/SNsummary_title.eps}  
+      \includegraphics[width=2.8in]{../figs/MIP/MIPsummary_title.eps} & \includegraphics[width=2.8in]{../figs/MIP/SNsummary_title.eps}  
   \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=4in]{figs/MIP/MIP3peaks.eps} 
+      \includegraphics[width=4in]{../figs/MIP/MIP3peaks.eps} 
     \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
+      \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
     \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{figs/pedestal/1T/summary_noise_chip12.eps}
+    \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_noise_chip12.eps}
   \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{figs/pedestal/pedestal_vs_nhits_shower.eps} \\
+      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_nhits_shower.eps} \\
     \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{figs/pedestal/pedestal_deviation_layer3.eps} & \includegraphics[width=2.8in]{figs/pedestal/pedestal_deviation_4GeV.eps} \\
+      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_layer3.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_4GeV.eps} \\
     \end{tabular}
@@
   \centering
-    \includegraphics[width=2.8in]{figs/fev11_cob.png} 
+    \includegraphics[width=2.8in]{../figs/fev11_cob.png} 
   \caption{Two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
@@
 \bibliographystyle{JHEP}
-\bibliography{references}
+\bibliography{../references}
 

### 2018-06-11 performance-paper-draft/shortversion/draft.tex
modify structure to split the paper in two versions: long version with JINST style and short with NIM style. For the short, only a raw copy of the long is done

--- 2018-06-11 performance-paper-draft/longversion/draft.tex
@@
-\documentclass[a4paper,11pt]{article}
-\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
+%\documentclass[a4paper,11pt]{article}
+\documentclass[final,3p,times,twocolumn]{elsarticle}
+%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
              % images in pdf, png or jpg format)
 
-\usepackage{jinstpub} % for details on the use of the package, please
+%\usepackage{elsarticle} % for details on the use of the package, please
                      % see the JINST-author-manual
@@
 \usepackage[utf8]{inputenc}
-
+\usepackage{textcomp}
 \usepackage{lineno}
@@
 
-\linenumbers
-
-\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}
+%\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}
 
 % e-mail addresses: only for the forresponding author
-\emailAdd{irles@lal.in2p3.fr}
+%\ead{irles@lal.in2p3.fr}
 %\collaboration[]{on behalf of the CALICE collaboration}
 
-\abstract{
+\begin{document}
+
+\begin{frontmatter}
+  \title{Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC.}
+
+\author{A. Irles}
+    % e-mail addresses: only for the forresponding author
+\ead{irles@lal.in2p3.fr}
+%\collaboration[]{on behalf of the CALICE collaboration}
+
+\begin{keyword}
+  Calorimeter methods, calorimeters, Si and pad detectors
+\end{keyword}
+
+%\maketitle
+%\flushbottom
+
+\begin{abstract}
   High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
@@
   and the performance of the device in a beam test carried at DESY in June 2017.
-}
+\end{abstract}
 
-\keywords{Calorimeter methods, calorimeters, Si and pad detectors}
-
-\begin{document}
-\maketitle
-\flushbottom
+  \end{frontmatter}
+\linenumbers
 
@@
 
-\acknowledgments
+\section*{acknowledgments}
 
@@
 
-\bibliographystyle{JHEP}
+%\bibliographystyle{JHEP}
+\bibliographystyle{elsarticle-num}
 \bibliography{../references}

### 2018-06-12 performance-paper-draft/longversion/draft.tex
Modify Intro and Title of the long paper

@@
 
-\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}
+\title{\boldmath Commissioning of the highly granular SiW-ECAL technological prototype}
 
@@
 the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
-Another example of an $e^{+}e^{-}$ collider project is the Compact Linear Collider (CLIC)
-project\cite{Aicheler:2012bya,Linssen:2012hp,Lebrun:2012hj}
-which will produce collisions with $c.m.e$ of 380 GeV - 3 TeV
-with a detector featuring similar design than the ILD and SiD.
-Both projects will explore with unprecedented precision the origin of the electroweak symmetry breaking and new physics beyond the standard model by exploring final states with heavy bosons (W, Z  and H) and fermions ({\it i.e.} heavy quarks as $c$, $b$ and $t$).
-
-It is known that in a {\it classical} typical multipurpose detector
-of a collider experiment the charged particles momentum is better measured by the tracking system
-the photons energy are only observed in the calorimeter system (mainly in the electromagnetic) if they are not converted
-and the measurement of the neutral hadrons energy can only be done by involving the full calorimeter systems.
-To meet the required precision levels by the ILC or CLIC physics goals,
+To meet the precision levels required by the ILC %or CLIC
+physics goals,
 new techniques relying on single particle separation to make possible the choice of the best information available
@@
 and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
-For this purpose, detectors optimized for PF algorithms have some requirements. Some of them are summarized here:
-
-\begin{itemize}
-\item a highly efficient and "transparent" tracking system between the interaction point and the calorimetry systems;
-\item highly granular ({\it imaging calorimetry}) and compact calorimeter systems featuring minimum dead material;
-\item and high power of particle separation\footnote{
-For that reason the calorimeter systems at ILD will be placed inside the magnetic coil
-providing magnetic fields of 3.5 T}.
-\end{itemize}
-
-The R\&D of highly granular calorimeters for future linear colliders is conducted within the CALICE collaboration and, for now on, we refer the reader to \cite{Sefkow:2015hna} for further information about PF and the CALICE R\&D.
+The detectors optimized for PF algorithms have some requirements. In the case of calorimeters: highly granular, compact
+and hermetic calorimeters. 
+The CALICE collaboration is doing R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
+for future linear colliders.
 
@@
 of a very compact calorimeter with highly granular and compact active layers.
-It will consist of an alveolar structure of carbon fiber into which modules called SLABs made of tungsten
+It will consist of an alveolar structure of carbon fiber into which modules made of tungsten
 plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
@@
 acquisition windows of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. During the idle time, the bias currents of the electronics will be shut down.
-This technique is usually denominated power pulsing.
-In addition to this, to cope with the large amount of channels, the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.
+This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
+the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.
+
+\section{The SiW-ECAL technological prototype}
 
@@
 
-\section{The SiW-ECAL technological prototype}
-
 The new generation prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
@@
 GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
-in particle physics to simulate the passage of particles through matter.
+in particle physics to simulate the passage of particles through matter. In this section we described in detail
+the main features and characteristics of the technollogical prototype.
 

### 2018-06-12 performance-paper-draft/shortversion/draft.tex
First draft of the short version

@@
 \newcommand{\todo}[1]{\textcolor{red}{{#1}}}
+\usepackage[outdir=./]{epstopdf}
 
@@
 \begin{frontmatter}
-  \title{Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC.}
+  \title{Beam test performance of the highly granular SiW-ECAL technological prototype for the ILC.}
 
@@
 \end{frontmatter}
+
 \linenumbers
@@
 
-\subsection{Silicon sensors}
-\label{sec:wafers}
-
-The sensors consist on floating zone silicon wafers 320$\mu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
-The size of the wafer is $9\times9$ cm$^{2}$ and it is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
-A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
-for particles incident perpendicularly to its surface.
-
-The original design of the silicon wafers included an edge termination made of floating guard-rings.
-It was observed in beam tests \cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
-and the channels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
-This coupling lead to fake events in which, at least,
-the channels in the four edges of the wafer are triggered at the same time. 
-This is why these events are called squared events. 
-An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-rings design 
-as well as the internal crosstalk.
-%As outcome of this R\&D program, the technological prototype 
-%is equipped with silicon wafers with:
-It was concluded that using wafers without guard rings and with a width of the peripheral areas lower than 
-500 $\mu$m thanks to the use of stealth dicing technique, the amount of these squared events 
-can be reduced to be almost negligible. This need to be confirmed in beam test.
-Unfortunately, for the interaction with low energy particles as the delivered at the
-DESY beam test facility (see Section \ref{sec:beamtest}) the
-amount of squared events is expected to be negligible, therefore we will not discuss this issue in the following.
-% do any differentiation 
-%of our results depending on the wafer type mounted in the detector.
-
-%\begin{itemize}
-%\item \todo{N wafers type-X with guard-rings of XXX characteristics (continuous, segmented, segmented smaller??)}
-%\item \todo{N wafers type-Y without guard rings and the width of the peripheral dead areas lower than 500 $\mu$m thanks to the use of stealth dicing technique.}
-%\end{itemize}
-
-%For the wafers \todo{type-Y}, the amount of squared events is expected to be reduced by, at least, a \todo{factor XXX}. In both cases, 
-%for interaction with low energy particles as the delivered at the DESY beam test facility (see Section \ref{sec:beamtest}) the
-%amount of squared events is expected to be negligible, therefore we will not do any differentiation 
-%of our results depending on the wafer type mounted in the detector.
-
-%\todo{ Is this needed?
-If so, what are the right plots to show?} Before the assembly of the sensors in the detector, these are characterized one-by-one by measuring the leakage current (of %the order of 1 nA per single diode)
-%as a function of the bias voltage (I-V curve), the full depletion voltage (of 40 V) extracted from C-V curve and
-%the stability in time (leakage current versus time at a nominal bias).
-%The single diodes have capacitances of 8 $pF$.
-
-%\begin{figure}[!t]
-%\centering
-%\begin{tabular}{lll}
-%  \includegraphics[width=1.8in]{../figs/test.jpg} &
-%  \includegraphics[width=1.8in]{../figs/test2.jpg} &
-%  \includegraphics[width=1.8in]{../figs/test3.jpg}
-%\end{tabular}
-%\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: Triptic La Esperanza del Condenado, J. Miró}}
-%\label{shortslab}
-%\end{figure}
-
-\subsection{SKIROC: Silicon pin Kalorimeter Integrated ReadOut Chip}
-\label{sec:skiroc}
-
-The SKIROC\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) is a
-very front end ASIC (application-specific integrated circuits)
-designed for the readout of the Silicon PIN didoes.
-In its version SKIROC2 it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
-Each channel comprises a low noise charge preamplifier of variable gain followed by two branches:
-a fast shaper for the trigger decision and a set of dual gain slow shaper for charge measurement. 
-The gain can be controlled by modifying the feedback capacitance during the configuration of the detector.
-With the slowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs 
-(a slightly less than the desired final value for the ILC). 
-Finally, a Wilkinson type analogue to digital converter fabricates the digitized charge deposition that can be readout. 
-Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as
-triggered or not triggered and the information is stored in 15 cell deep physical switched capacitor array (SCA).
-
-The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
-the bias currents of the ASIC can be switched off during the idle time between bunch trains.
-With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
-meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.
-
-\begin{figure}[!t]
-  \centering
-    \includegraphics[width=4in]{../figs/skiroc2_block.eps}
-\caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
-\label{SKIROC2}
-\end{figure}
-
-\subsection{Active Sensor Units}
-\label{sec:ASU}
-
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{l}
-    \includegraphics[width=4in]{../figs/ASU_geometry1.eps}  \\
-    \includegraphics[width=4in]{../figs/ASU_geometry2.eps}  \\
-  \end{tabular}
-  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back.
-    The channels are separated (in x and y) by 5.5 mm.
-    The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.
-    The areas covered by the different ASICs and channels
-    are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
-  }
-\label{ASU}
-\end{figure}
-
 The entity
-of sensors, thin PCB (printed circuit boards) and ASICs is called Active Signal Units or ASU.
+of sensors, thin PCB (printed circuit boards) and ASICs (application-specific integrated circuits)
+is called Active Signal Units or ASU.
 An individual ASU has a lateral dimension of 18x18 cm$^{2}$.
 The ASUs are currently equipped
-further with 16 SKIROC2 ASICs for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
-The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}. Each ASU is equipped with 4 silicon wafers as the described in Section \ref{sec:wafers}.
-The high voltage is delivered to the wafers using a HV-kapton sheet that covers the full extension of the wafers.
-
-\subsection{Data AcQuisition system}
-\label{sec:DAQ}
-
-The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
-It consists on three modules.
-The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs;
-All DIFs are connected by single HDMI cables to the concentrator cards that make
-the second module: the Gigabit Concentrator Cards (GDCCs).
-%The HDMI connection is used to transmit both slow control and data readout.
-This cards are used to control up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
-The last module, the most downstream, is the clock and control card (CCC) which
-provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
-generated external pulse generator to simulate the ILC spill conditions).
-The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
-%The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition.
-%Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype. 
-%This new version of the DAQ software implements a new mechanism to allow any module to treat and publish data in real time. 
-%Those data are made available to any requesting module, in particular to a new online monitor module developed
-%for this beam test, allowing for quick online checks of the data quality and integrity.
-
-\subsection{Readout layers and SLABs}
-\label{sec:setup}
-
-\begin{figure}[!t]
-  \centering
-    \includegraphics[width=2.8in]{../figs/test.jpg} 
-  \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
-\label{ASU2}
-\end{figure}
-
-The readout layers of the SiW-ECAL consist of a chain of ASUs and an adapter board
+further with 16 SKIROC2\cite{}  (Silicon pin Kalorimeter Integrated ReadOut Chip)
+ASICs for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
+The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}.
+Each ASU is equipped with 4 silicon wafers. The sensors consist on floating zone silicon wafers
+320$\mu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
+The size of the wafer is $9\times9$ cm$^{2}$ and it is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
+A MIP (minimum ionizing particle) traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
+for particles incident perpendicularly to its surface.
+The high voltage is delivered to the wafers using a high voltage kapton sheet that covers the full extension of the wafers.
+The readout layers of the SiW-ECAL consist of a chain of Active Sensor Units (ASUs) and an adapter board
 to a data acquisition system (DAQ) at the beginning of the layer.
-This adapter board is called SMBv4
-and it also serves as to hold other services as power connectors or the super capacitances used for the power pulsing. 
-These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance. 
-The purpose of these capacitances is to provide local storage 
-of the necessary charge to avoid the transport of current pulses over long cables, 
-ensuring in this way the stability of the ASICs during the acquisition.
-
 The readout layers are embedded on a "U" shape carbon structure to protect the wafers.
@@
   \centering
+    \includegraphics[width=0.4\textwidth]{../figs/test.jpg} 
+  \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
+\label{ASU2}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
   \begin{tabular}{l}
-\includegraphics[width=6.0in]{../figs/assembly.png} 
+    \includegraphics[width=0.4\textwidth]{../figs/ASU_geometry1.eps}  \\
+    \includegraphics[width=0.4\textwidth]{../figs/ASU_geometry2.eps}  \\
   \end{tabular}
-\caption{Process flow for the assembly of the SiW-ECAL SLABs.}
-\label{assembly}
+  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back.
+    The channels are separated (in x and y) by 5.5 mm.
+    The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.
+    The areas covered by the different ASICs and channels
+    are labeled with numbers following design and DAQ criteria: from 0-16 in the case of the ASICs and from 0-63 in the case of the channels.
+  }
+\label{ASU}
 \end{figure}
@@
 profiting from the funding of projects like AIDA2020 or the HIGHTEC emblematic project
-of the P2IO. A schematic view of this assembly procedure chain can be seen in
-Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
+of the P2IO.
 
-\section{Commissioning}
-\label{sec:commissioning}
-
-This beam test was prepared by a careful and comprehensive commissioning comprising
-the debug of the
-short SLABSs with special emphasis in the control of the noise and the study of the
-prototype performance in cosmic rays tests.
-
-Earlier experiences with the SKIROC2 ASIC are reported in Refs. \cite{Amjad:2014tha,Suehara:2018mqk}). 
-Internal SKIROC2 parameters found in these references are adopted in the following
-except if the opposite is stated.
-For example, the gain value of 1.2pF for the preamplifier is used. 
-With this gain, the SKIROC2 ensures a linearity better than 90\% 
-for 0.5-200 MIPs, which is enough for 
-electromagnetic showers created by few GeV 
-electrons or positrons.
-% The delay of the trigger signal is the same than in 
-%reference \cite{Amjad:2014tha,Suehara:2018mqk}: 130 DAC for all ASICS. 
-%This value was chosen by selecting the delay in which an injected signal
-%of few MIPs of value get the maximum value of ADC. %Finally, the value of the
-%compensation capacitance at the output of the preamplifier has been set to 6pF instead of 
-%4pF to prevent overshots and ripples of the signal used as input to the trigger
-%decision and ADC lines.
-
-\subsection{Optimization of noise levels}
-\label{sec:comm_noise}
-
-%The purpose of this phase was to monitor and control the
-%noise levels of the prototype.
-%The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
-Studying and control the noise levels
-is crucial since noisy channels may saturate the DAQ faster than physical signals.
-Two different types of noise sources were identified:
-a set of noisy channels randomly distributed in time 
-and noise bursts affecting to all layers at the same time.
-The outcome of this commissioning is summarized in Figure \ref{noisycells}.
-
-The first type of noise source, noise events randomly distributed in time,
-forced us to define a list of channels to be masked in all 
-layers. Again, two different type of noisy channels have been identified. 
-The first group is compose by randomly distributed in space channels.
-The second group is made of
-a fixed list of channels, all in the same positions for all SLABs,
-and all associated to a higher rate of events with underflowed value
-of the read ADC.
-%The latter set of channels were identified by means of the online monitoring
-%tools.
-%As channels are located in the same place for all SLABs,
-%we took the conservative assumption
-%that all modules would have problems in the same set of channels.
-%For example, all channels number 37.
-A large amount of these channels are located
-in areas of the PCB where the density of lines 
-(data and power transmission) is higher than in others.
-This hints for an issue on the routing of the PCB.
-Therefore, these channels are tagged in Figure \ref{noisycells} with the "routing issues" label
-although more tests and deeper inspections of the PCB layout are needed to clarify this issue.
-
-The list of the noisy channels randomly distributed in time and space was
-defined by means of dedicated data taking runs. 
-These runs were characterized by: their short acquisition windows (open to data recording for 
-only 1.1 ms) at low repetition frequencies (5 Hz) to minimize the chances of having real events due to cosmic rays 
-hitting the detector during the
-data taking; and the relatively high trigger threshold values between 250 and 400 DAC 
-(which are equivalent to $\sim$0.5-2 MIP, see Section \ref{sec:comm_trigger} for more 
-information). The full process was an iterative process starting with several repetitions
-of runs at a high threshold value and then some iterations at lower threshold but always 
-higher than 0.5 MIP. 
-In each of the iterations, the channels identified as noisy were masked.
-A full run involved 3-5 threshold values and at least two repetitions per value.
-Again, we decided to follow a conservative approach for list the noisy channels to be masked:
-if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC
-it was added to the list. These channels are labeled as "other" in the first plot in  Figure \ref{noisycells}.
-
-In addition to the different noisy channel types described above, we also have
-masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
-listed as noisy) or if a Si-wafer was misworking (high leakage currents). In these cases 
-and in all mentioned above, the masking involved two steps: disabling of the trigger and 
-the disabling of the power of the preamplifier of that channel.
+The subsequent chain of the data acquisition (DAQ) system \cite{Gastaldi:2014vaa} is inspired by the ILC.
+It consists on three layers of modules.
+The first layer, or most downstream layer, consists on a set of detector interfaces called DIFs which are placed at the beginning of each SLAB holding up to 15 ASUs.
+The second layer is made of concentrator cards module called the Gigabit Concentrator Cards (GDCCs)
+which are used to control up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
+The last layer consist on a clock and control card (CCC) which
+provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
+generated external pulse generator to simulate the ILC spill conditions).
+The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
 
@@
 \begin{tabular}{l}
-  \includegraphics[width=4in]{../figs/commissioning/masked_layer.eps} \\
-  \includegraphics[width=4in]{../figs/commissioning/masked_chip.eps}
+\includegraphics[width=0.4\textwidth]{../figs/proto.png} 
 \end{tabular}
-\caption{Ratio of channels that are marked as noisy in all slabs. 
-Top: inventory of the different type of noisy channels per slab. 
-Bottom: break down of the total number of noisy channels per ASIC. 
-The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
-in the second plot since they are fully masked.}
-\label{noisycells}
+\caption{Prototype with 7 layers inside the aluminum stack.}
+\label{proto}
 \end{figure}
 
-The other source of noise mentioned at the beginining of this section
-consist on noise bursts happening coherently at the same time in all SLABS
-and it was correlated to occasions when the electrical isolation between SLABs was broken.
-This is a hint of a system effect as can be the appearance of
-grounding loops or disturbances in the power supplies.
-The issue was circumvented by improving the electrical isolation of single layers.
-We have also observed that the noise bursts happens only at the end of long acquisitions. Therefore, in addition to the improved isolation,
-we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
-Ddedicated studies in the laboratory are currently pngoingin order to fully understand this issue.
-
-The list of channels mentioned above is discarded from the data taking from now on.
-
-\subsection{Threshold determination}
-\label{sec:comm_trigger}
-
-In order to select the optimal trigger threshold values for the detector operation
-we perform dedicated scans of trigger threshold values
-with all channels enabled (excepted the marked as noisy). 
-The threshold values are given in internal DAC units which are translated to
-meaningful physical quantities in Section \ref{sec:comm_trigger_sn}. 
-The threshold scan curves made of the total number of hits normalized to 1 vs the threshold
-for each channel are modeled by a complementary error function called ThS curves from now on:
-
-\begin{equation}
-ThS(DAC)=p_{0} \times erfc(\frac{DAC-p_{1}}{p_{2}}) = 
-\newline
-\frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} e^{-t^{2}} dt,
-\label{eq_S-curve}
-\end{equation}
-where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
-the 50\% of its maximum and $p_{2}$ give us the width of the ThS curve.
-
-In the absence of external signals (cosmic rays, injected signals, etc) 
-these noise ThS curves show the convolution of the envelope of the 
-electronic noise at the output of the fast shaper (the trigger decision branch on the SKIROC).
-Indeed, the size of this envelope is related to the slow clock frequency.
-
-To reduce to the minimum the presence of cosmic rays signals, 
-we perform runs with short open acquisition windows
-as described in the previous section.
-In Figure \ref{scurve_channels} 
-two result of two threshold scans and the fit by
-a ThS curves for two different channels from the second layer of the setup are shown.
-
-\begin{figure}[!t]
-  \centering
-  \begin{tabular}{ll}
-  \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn2_asic0_layer2.eps}
-  \end{tabular}
-\caption{Two threshold scan curves and their associated ThS curves.}
-\label{scurve_channels}
-\end{figure}
-
-The function from equation \ref{eq_S-curve} was fitted to all
-channels data and all the values of $p_{1}$ and $p_{2}$ were saved.
-The final threshold value of every ASIC, in DAC units, was chosen 
-by taking the
-
-\begin{equation}
-maximum(DAC_{optimal}^{ASIC-j} = <p_{1}^{ASIC-j}> + 5 \times <p_{2}^{ASIC-j}>,230)
-\end{equation}
-
-if at least the the 30\% of the 64 channels ThS curves in the ASIC could be fitted.
-If only less  than the 30\% of curves of the 64 channels were
-succesfully fit, a global DAC value of 250 was set.
-The $<>$ denotes the average over all the channels on the ASIC.
-The choice of these two values was 
-sustained by previous experiences, see for example \cite{Amjad:2014tha}.
-
-The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
-
-\subsection{S/N ratio in the trigger line}
-\label{sec:comm_trigger_sn}
-
-Similar kind of measurements can be done but using external signals. 
-This will allow to calculate the signal over noise (S/N) ratio to trigger 1 MIP signals.
-To calculate the S/N of the trigger we need to compare the 1 MIP ThS curve and 2 MIP ThS curve. The S/N 
-will be defined as the ratio between the distance of both ThS curves at its 50\% and the width of the 
-ThS curve.
-
-In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP ThS curves obtained for several channel
-in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
- signals are directly injected in the preamplifier 
-(via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
-From this plot we can extract a S/N ratio of $\sim$12.8. 
-We do not expect large differences with the results that we would obtain with 
-a full equipped SLABs 
-although this board is thought for commissioning and test of the SKIROC ASICS in an
-"ideal" environment in contrast with the FEV
-ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
-%For example: only power pulsing of the analog power is done in this testboard,
-%there is a set of external capacitors on the board connected to some ASIC pins and
-%usually only one channel is tested. This board allows us to commission and debug the SKIROC itself
-%but not the full system.
-
-\begin{figure}[!t]
-    \centering
-  \begin{tabular}{l}
-	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
-	\end{tabular}
-\caption{ThS curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
-\label{scurves_injection}
-\end{figure}
-
-We have obtained similar results using real signals, in this case cosmic rays signals by using very long
-acquisition windows of 150 ms at 5 Hz. This is shown 
-in Figure \ref{scurves_cosmics}  where 
-we show the result of the fit to the noise ThS curves for all channels individually (in red) in one of the ASICs of 
-the second layer together with the results of the ThS curve obtained with cosmic rays integrated for all channels
-(black points and blue line).
-%For the cosmic ThS curve we took 30 min of data per point using very long spills (150 ms) in 
-%frequencies of 5Hz and we add up the triggers from all channels together. In addition, using the 
-%knowledge of the MIP value (see next section), we performed a simple cut in the ADC
-%to keep only signals corresponding to a MIP 
-%(pedestal subtracted) $\pm30$ ADC counts. With this cut we try reduce the contribution of muons 
-%traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
-%since we were using simple setups with only single slabs. 
-We expect
-a broader distribution of the cosmic ThS curve since muons can traverse
-the detector at different incidence angles.  
-In addition to this, we should remember that the noise ThS curve do correspond to the real noise 
-distribution but only to the envelope of the noise in the fast shaper, therefore the
-distance between the two ThS curves is smaller than the real distance between noise and signal.
-Therefore, if we calculate the S/N 
-using this plot, the value would be unrealistic but at least provides 
-the comparison between the ThS curve for 1 MIP real and injected signals.
-
-\begin{figure}[!t]
-    \centering
-  \begin{tabular}{l}
-	\includegraphics[width=4in]{../figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
-	\end{tabular}
-\caption{ThS curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
-\label{scurves_cosmics}
-\end{figure}
-
-Both ways of estimating the S/N ratio of the trigger have their own limitations
-and dedicted studies in beam test are needed in order to
-precisely determine it.
-In the meanwhile, combining the information contained in the Figs \ref{scurves_injection} and \ref{scurves_cosmics},
-we can estimate the value in energy at wich we have set our trigger threshold.
-This is shown in Figure \ref{trigger_thresholds}.% Two ASICS have a
-%trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=4in]{../figs/commissioning/threshold_chip.eps}
-  \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
-\label{trigger_thresholds}
-\end{figure}
-
-\subsection{Prospects}
-\label{sec:comm_prospects}
-
-All the commissioning procedure described above relies in very conservative decisions
-due to the presence of unknown noise sources during most of the commissioning phase. These sources are
-now well know and isolated and therefore a new ``noise commissioning procedure'' has been studied.
-It will consist in an iterative algorithm that first
-will identify and mask the channels giving underflowed signals and afterwards run a set of acquisitions
-in which the number of triggers per channel will be compared with the number of expected triggers
-assuming only cosmic rays as signal. This will allow us to have an
-unambiguous definition of the noise levels channel per channel instead of 
-defining such levels relatively to the total number
-of recorded triggers per ASIC. Finally, once that the noisy channels
-are identified, the optimization of the threshold levels
-will be performed and a last run for identification of noisy channels will be taken using this optimal
-threshold.
-%In this run, we can decide to mask the noisy channels or
-%to increase its own trigger threshold level if we are using Skiroc2a.
-
-Using this new procedure we manage to reduce the number of masked channels by a factor 2 without any loss of performance,
-at least in the laboratory and using 3 of the 7 SLABs. This new procedure will be tested in the next beam test.
-Also, in order to
-optimize the commissioning of the detector,
-we propose a new set of measurements in the next beam test such as
-a scan of optimal delay of the hold values of the trigger using MIP like particles
-and a threshold scan for the determination of the S/N in the trigger line. This later
-can be done by the comparison of ThS curves taken with 1 MIP and $\sqrt{2}$ MIP signals (tilting the detector by 45 degrees).
+A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
+Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10.
+For the beam test described in Section \ref{sec:beamtest} all the layers were separated by equal distances of 15 mm
+except the last one which was at 60 mm of its nearest. In the following sections, we will refer to layers number 1 to 7, where
+the 1 is the closest to the beam pipe and 7 is the farthest.
+The detector was exposed to a positron beam in the DESY test beam area (line 24).
+During the full data taking period at the DESY beam test facility,
+the detector was running in power pulsing mode without any extra active cooling system.
+and means of an external pulse generator we defined the length of the acquisition window to be
+3.7 ms at a frequency of 5 Hz.
 
@@
 In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.
-
-\begin{figure}[!t]
-\centering
-\begin{tabular}{l}
-\includegraphics[width=4.0in]{../figs/proto.png} 
-\end{tabular}
-\caption{Prototype with 7 layers inside the aluminum stack.}
-\label{proto}
-\end{figure}
-
-A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
-Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10.
-For the beam test described in Section \ref{sec:beamtest} all the layers were separated by equal distances of 15 mm
-except the last one which was at 60 mm of its nearest. In the following sections, we will refer to layers number 1 to 7, where
-the 1 is the closest to the beam pipe and 7 is the farthest.
-The detector was exposed to a positron beam in the DESY test beam area (line 24).
-By means of an external pulse generator we defined the length of the acquisition window to be
-3.7 ms at a frequency of 5 Hz.
-The detector was running in power pulsing mode without any extra active cooling system.
 
@@
 First reports on this beam test can be find in
-Refs. \cite{Irles:2018uum,Irles:2018hcd}. In this paper we discuss in more detail
+Refs. \cite{Irles:2018uum,Irles:2018hcd}. In this paper we discuss in detail
 the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
-We show also results on the pedestal and noise stability when running inside
-a magnetic field in Section \ref{sec:magnet}. Finally, a first peek to the 
-response and stability of the detector in electromagnetic showers events is discussed in 
-Section \ref{sec:showers}.
+We also show the results on the pedestal and noise stability when running inside
+a magnetic field in Section \ref{sec:magnet}. The study of the perfomance of the detector
+for electromagnetic shower events will be covered in future publciations.
+
+\subsection{Commissioning}
+\label{sec:commissioning}
+
+Earlier experiences with the SKIROC2 ASIC are reported in Refs. \cite{Amjad:2014tha,Suehara:2018mqk}). 
+Internal SKIROC2 parameters found in these references are adopted in the following
+except if the opposite is stated.
+For example, the gain value of 1.2pF for the preamplifier is used. 
+With this gain, the SKIROC2 ensures a linearity better than 90\% 
+for 0.5-200 MIPs, which is enough for 
+electromagnetic showers created by few GeV 
+electrons or positrons.
+This beam test was prepared by a careful and comprehensive commissioning comprising
+the debug of the
+short SLABSs with special emphasis in the control of the noise and the study of the
+prototype performance in cosmic rays tests. Dedicated runs at the laboratory were taken
+in order to identify and mask the noisy channels. The outcome of this study
+is that X\% of the channels were masked before putting the detector in front of the beam.
+Two different kinds of noisy channels were found: the ones that are noisy on all
+SLABs and those which are only noisy in one or few of them. Preliminary inspections
+of the PCB hints that the first group is associated to routing issues on the PCB and
+hereafter they are labelled like this. The summary of this study is shown in Figure \ref{noisycells}.
+These channels are removed from the data taking in all the studies shown from now on.
+
+\begin{figure}[!t]
+  \centering
+  \begin{tabular}{l}
+  \includegraphics[width=0.4\textwidth]{../figs/commissioning/masked_layer.eps} \\
+  \includegraphics[width=0.4\textwidth]{../figs/commissioning/masked_chip.eps}
+  \end{tabular}
+\caption{Ratio of channels that are marked as noisy in all slabs. 
+Top: inventory of the different type of noisy channels per slab. 
+Bottom: break down of the total number of noisy channels per ASIC. 
+The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
+in the second plot since they are fully masked.}
+\label{noisycells}
+\end{figure}
+
+\subsubsection{Trigger threshold optimization}
+\label{sec:comm_trigger}
+
+\todo{Autotrigger stuf.
+In order to select the optimal trigger threshold values for the detector operation
+we perform dedicated scans of trigger threshold values
+with all channels enabled (excepted the marked as noisy). }
+The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.4\textwidth]{../figs/commissioning/threshold_chip.eps}
+  \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
+\label{trigger_thresholds}
+\end{figure}
+
+\subsubsection{S/N ratio in the trigger line}
+\label{sec:comm_trigger_sn}
+
+In Figure \ref{scurves_injection} we see threshold scans curves
+ curves obtained for several channel
+in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
+ signals are directly injected in the preamplifier 
+(via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
+From this plot we can extract a S/N ratio of $\sim$12.8. 
+Unfortunately, this results has obtained using
+a dedicated board thought for commissioning and test of the SKIROC ASICS in an
+"ideal" environment in contrast with the fully equipped
+ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
+We do not expect large differences with the results that we would obtain with 
+a full equipped SLABs but dedicated runs in beam test will be needed.
+
+\begin{figure}[!t]
+    \centering
+  \begin{tabular}{l}
+	\includegraphics[width=0.4\textwidth]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
+	\end{tabular}
+\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard.
+From this plot, we extract a $S/N = 12.8$ in the trigger line.
+\todo{We need to use charge in the axis}}
+\label{scurves_injection}
+\end{figure}
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=4in]{../figs/mip_pedestal_example.eps}
+    \includegraphics[width=0.4\textwidth]{../figs/mip_pedestal_example.eps}
   \end{tabular}
@@
 The pedestal correction is done layer-, chip-, channel- and SCA-wisely due to the large spread of values between pedestals, as observed in 
-Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
-For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
+Figure \ref{pedestal_layer} (upper plot) and Figure \ref{pedestal_all} (also upper plot).
+For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the lower plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
 From now on, the pedestal correction is applied to all the results presented.
-
-%\begin{figure}[!t]
-%  \centering
-%  \begin{tabular}{ll}
-%    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{../figs/pedestal/ped_width_layer2_chip4_cell10.eps}
-%  \end{tabular}
-%  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
-%\label{pedestal_channel}
-%\end{figure}
 
@@
   \centering
-  \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{../figs/pedestal/width_mean_layer2.eps}
+  \begin{tabular}{l}
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/ped_mean_layer2.eps} \\
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/width_mean_layer2.eps}
   \end{tabular}
@@
   \centering
-  \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/h_ped_mean.eps} & \includegraphics[width=2.8in]{../figs/pedestal/h_ped_width.eps}
+  \begin{tabular}{l}
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/h_ped_mean.eps} \\
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/h_ped_width.eps}
   \end{tabular}
-  \caption{Pedestal mean position (left) and width (right) for all channels and all SCAs in the setup.}
+  \caption{Pedestal mean position (upper) and width (lower) for all channels and all SCAs in the setup.}
 \label{pedestal_all}
@@
 We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
-available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.
+available channels being fitted. Results are summarized in figure \ref{mipandSN}, upper plot.
 
@@
   \centering
-  \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/MIP/MIPsummary_title.eps} & \includegraphics[width=2.8in]{../figs/MIP/SNsummary_title.eps}  
+  \begin{tabular}{l}
+    \includegraphics[width=0.4\textwidth]{../figs/MIP/MIPsummary_title.eps} \\
+    \includegraphics[width=0.4\textwidth]{../figs/MIP/SNsummary_title.eps}  
   \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=4in]{../figs/MIP/MIP3peaks.eps} 
+      \includegraphics[width=0.4\textwidth]{../figs/MIP/MIP3peaks.eps} 
     \end{tabular}
@@
   \centering 
-    \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
+    \begin{tabular}{l}
+      \includegraphics[width=0.4\textwidth]{../figs/MIP/efficiency_nhits4_chips.eps} \\
+      \includegraphics[width=0.4\textwidth]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} 
     \end{tabular}
-    \caption{Left: MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.
-Right: same figures with a zoom in the y-axis.
+    \caption{Upper plot: MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.
+Lower plot: same figures with a zoom in the y-axis.
 In both cases, the average efficiency of the 64 channels in each ASIC is shown.}
@@
   \centering
-  \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_noise_chip12.eps}
+  \begin{tabular}{l}
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/1T/summary_pedestal_chip12.eps} \\
+    \includegraphics[width=0.4\textwidth]{../figs/pedestal/1T/summary_noise_chip12.eps}
   \end{tabular}
@@
 
-\subsection{Pedestal stability in electromagnetic shower events}
-\label{sec:showers}
-
-In this section we discuss the pedestal stability in events with large amount of charge collected by the ASICs, as are the 
-electromagnetic shower events. All the results shown in this section correspond to data taken during the tungsten program, 
-using the W-configuration number 2 when shooting the beam in the area registered by the ASIC 12 (and partially in the 13). 
-Only information recorded by ASIC 12 is used in the analysis. For other configurations we get comparable results.
-In order to select a high purity of
-electromagnetic shower like the events, 
-we used a simple criteria: select only events with at least 6 of the layers with at least a hit with E > 0.5 MIP.
-
-\begin{figure}[!t]
-  \centering 
-    \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_nhits_shower.eps} \\
-    \end{tabular}
-    \caption{Left: mean position of the projection of the pedestal distribution of all channels
-      calculated when different energies are collected in the ASIC (in bins of 10 MIPs).
-      Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA.
-      The points for the curves with SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
-\label{pedestal_shower_1}
-\end{figure}
-
-Two main observations have been extracted from the recalculation of the pedestals and its comparison
-with the values obtained previously during the calibration runs. The first observation
-consists in a relatively small 
-drift of the pedestal values
-towards lower values when the collected energy is high (or when the number of triggered channels is large).
-%For events with 80 MIPs collected in the ASIC, we have an average drift of the pedestal of $\sim$ 0.05 MIP. 
-This is shown in Figure \ref{pedestal_shower_1} for several SCAs where the
-average of the projection of the pedestal distribution for all channels non triggered in ASIC 12 of layer 3 
-is plot as a function of the total energy measured by the ASIC (or the total number of hits).
-We see that in both cases, the shapes of the curves 
-for each SCA are very similar.
-This feature is known and it is due to the architecture of the SKIROC2 ASICs 
-where high inrush of currents can slightly shift the baseline of the analogue power supply. 
-%This feature is foreseen to be removed from the SKIROC3 ASICs.
-
-The second observation extracted from this analysis can be also seen in Figure \ref{pedestal_shower_1} but
-more clearly in Figure \ref{pedestal_shower_2}: in addition
-to the small drift of the pedestal value an SCA-alternate global shift
-is observed. We see that the effect is enhanced when large amounts of charge
-are deposited in the ASIC ({\it i.e.} at larger beam energies or for the layers in the maximum of the shower
-profile). We also observed that this alternation is only SCA dependent and does not depends
-on the time in which the deposit of energy occurs within the acquisition.
-This is not yet fully understood although the fact that the effect is observed in
-alternate SCAs hints that something is affecting to the digital part of the ASIC 
-(where the SCAs enter in play).
-Dedicated tests in the laboratory and in the beam are needed in order to clarify this issue.
-
-\begin{figure}[!t]
-  \centering 
-    \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_layer3.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_4GeV.eps} \\
-    \end{tabular}
-    \caption{Left: average value on each SCA of the calculated pedestals for all channels of ASIC 12 in the Layer 3 for different energies of the beam.
-Right: same but fixing the energy of the beam and comparing several layers.}
-\label{pedestal_shower_2}
-\end{figure}
-
-\section{Summary}
+\section{Summary  and outlook}
 \label{sec:summary}
@@
 beam test performance of a prototype built in with the first fully assembled
-detector elements.
+detector elements. In contrast with previous beam test, in this one we have fully
+assembled detector elements meeting ILD requirements and the higher level of
+density channel and total granularity achieved so far by this calorimeter.
 
@@
 will be covered in a future document.
-In addition, the results shown here serve as input
-for ongoing and future R\&D.
 
-\section{Outlook}
-\label{sec:outlook}
+In parallel to the work described here, several R\&D efforts are being carried
+and the results shown here are crucial for the next steps in the R\&D program.
 
-In parallel to the work described here, several R\&D efforts are being carried.
 One of these efforts is directed to the design and test of new ASICs.
 In fact, a new generation of SKIROC2, the 2a, has been delivered
-and it is being tested in the dedicated testboards and it has been integrated in new ASUs.
-In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
-In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
+and it is being tested in the dedicated testboards and in a new generation of ASUs.
+%In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
+%In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
 
@@
 of $\sim8$ ASUs is currently ongoing.
-%Therefore, many efforts are focused in the construction and test of such long 
-%layers made of chains of ASUs (up to $\sim$15 ASU) 
-%as well as in the standardization of the interconnections.
 
@@
 with a total thickness of 1.2 mm allowing for a potential denisty of 10000 channels/dm$^{3}$ has been produced and tested in the laboratory
-showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{cob}.
-
-\begin{figure}[!t]
-  \centering
-    \includegraphics[width=2.8in]{../figs/fev11_cob.png} 
-  \caption{Two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
-\label{cob}
-\end{figure}
-
-Finally, many efforts in the compactification of
-the DAQ and the ASUs ({\it i.e.} the chip on board versions of the 
-ASUs described in Section \ref{sec:ASU}) are being
-conducted by the SiW-ECAL collaboration.
+showing its readiness for tests with particle beams.% A sample can be seen in Figure \ref{cob}.
+In addition, many efforts in the compactification of
+the DAQ and the SLABs are currently being carried by the SiW-ECAL collaboration.
 
@@
 
-\appendix
-\section{Apendix: Filtering of fake triggers}
-\label{sec:retriggers}
-
-Several types of fake signals have been observed in the technollogical prototype since its construction and test. A detailed description of them
-can be found in previous articles, as for example, in Ref. \cite{Amjad:2014tha}. All these fake signals are easily identified
-and tagged during the data acquisition and removed afterwards from the analysis
-not introducing any significance loss of performance as can be seen, for example, in the hit detection efficiency plots (see Section \ref{sec:mip}).
-In the following, we briefly describe the status of the monitoring, debugging and filtering
-of such kind of events.
-
-\subsubsection*{Empty triggers}
-
-Empty trigger events are a well known feature of SKIROC2. The SKIROC2 uses
-an OR64 signal to mark the the change to a new SCA when a signal over threshold is
-detected. The empty triggers appear when during
-the acquisition the rising edge of the slow clock falls during the OR64 signal
-and therefore the change to a new SCA is validated twice.
-This effect creates around 10-15\% of empty events which are easily filter and removed from the
-analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to the $\sim3\%$
-thanks to to a decrease of the OR64 size by a factor X.}
-
-\subsubsection*{Plane events and retriggers}
-
-Another well know issue is the appearance of bunches of consecutive fake triggers, called retriggers,
-that saturates the DAQ. These events are also
-characterized by triggering many channels (some times even all channels of an ASIC) at the same time.
-Although the ultimate reason of the appearance of these events remains unknown we
-think that they may be related to some distortion of the
-power supply baselines. We know that the SKIROC2 and 2a preamplifiers are referenced to the analog power supply level,
-therefore, any voltage dip can ve seen as signal by the preamplifiers. The presence of a high inrush of current
-due to many channels triggered at the same time can create these voltage dips
-and produce the so called plane events (most of the channels trigered at once).
-In previous studies ({\it i.e.} reference \cite{Amjad:2014tha}), the ratio of retriggers and plane events
-was reduced by improving the power supply stabilization capacitances. It is important to remark that
-all layers and all ASICs analog and digital levels are powered using the same power supply.
-Moreover, the high voltage power supply for the polarization of the PIN diode it is also common for all layers.
-Therefore any noise in
-these power supplies or any overload of an ASIC may participate in the creation of fake signals
-in different ASICs and layers.
-
-Studying the MIP calibration data of this beam test we have noticed that the larger concentration of the retriggers and plane events are originated 
-in
-ASICs far from the beam spot. Even more, hot spots tend to appear near the channels 37 and the channels masked
-as suspicious of suffering from routing issues. The amount these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
-interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 KHz) and at higher rates even larger than $40\%$ in other 
-ASICs far from the beam spot.
-Moreover, it has been noticed a correlation between the time that an ASIC was full and the time of the appearance of some 
-retriggers in other areas of the PCB. 
-This correlation corresponds to $\sim$1.6 $\mu$s which hints
-of a distortion on the analogue power supply when
-the signal that informs the DIF that one ASIC memory is full is transmitted through the PCB.
-
-All this information and dedicated studies in the laboratory will be used for the
-improvement of the power supplying system, the PCB design and for further SKIROC developments 
-with the possible approval the ILC in the scope.
-
-% We suggest to always provide author, title and journal data:
-% in short all the informations that clearly identify a document.
-
 %\bibliographystyle{JHEP}

### 2018-06-13 performance-paper-draft/longversion/draft.tex
Second iteration of the long version of the paper

@@
 and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
-The detectors optimized for PF algorithms have some requirements. In the case of calorimeters: highly granular, compact
+The PF algorithms impose some special requirements in the design of the detectors.
+For example, it requires highly granular, compact
 and hermetic calorimeters.
-The CALICE collaboration is doing R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
-for future linear colliders.
 
-In this document we will focus in the description of the silicon-tungsten electromagnetic calorimeter,
-SiW-ECAL, its commissioning and its performance in beam test.
-The SiW-ECAL is the baseline choice for the ILD ECAL. It consists in a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
+The CALICE collaboration is driving most of the efforts on R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
+for future linear colliders by investigating and building prototypes for several
+calorimeter concepts. One of these calorimeters 
+is the silicon-tungsten electromagnetic calorimeter, SiW-ECAL.
+The SiW-ECAL is the baseline choice for the ILD electromagnetic calorimeter.
+It consists in a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
 It has silicon (Si) as active material and tungsten (W) as absorber material.
@@
 of a very compact calorimeter with highly granular and compact active layers.
-It will consist of an alveolar structure of carbon fiber into which modules made of tungsten
+It will be built an alveolar structure of carbon fiber into which modules made of tungsten
 plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
-embedded in the SLABs. The silicon sensors will be segmented
+embedded in the detector units. The silicon sensors will be segmented
 in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million channels will constitute the ECAL for ILD.
@@
 The active layers were made of a matrix of 3x3 Si wafers of 500 $\mu$m thickness. Each of these wafers was segmented in matrices of
-6x6 squared channels of 1x1 $cm^{2}$, allowing for density of 1500 channels/dm$^{3}$
+6x6 squared channels of 1x1 $cm^{2}$, allowing for a potential density of 1500 channels/dm$^{3}$ assuming
+the ILD baseline design constraints on the material repartition and compactness.
 The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
@@
 amount of squared events is expected to be negligible, therefore we will not discuss this issue in the following.
-% do any differentiation 
-%of our results depending on the wafer type mounted in the detector.
-
-%\begin{itemize}
-%\item \todo{N wafers type-X with guard-rings of XXX characteristics (continuous, segmented, segmented smaller??)}
-%\item \todo{N wafers type-Y without guard rings and the width of the peripheral dead areas lower than 500 $\mu$m thanks to the use of stealth dicing technique.}
-%\end{itemize}
-
-%For the wafers \todo{type-Y}, the amount of squared events is expected to be reduced by, at least, a \todo{factor XXX}. In both cases, 
-%for interaction with low energy particles as the delivered at the DESY beam test facility (see Section \ref{sec:beamtest}) the
-%amount of squared events is expected to be negligible, therefore we will not do any differentiation 
-%of our results depending on the wafer type mounted in the detector.
-
-%\todo{ Is this needed?
-If so, what are the right plots to show?} Before the assembly of the sensors in the detector, these are characterized one-by-one by measuring the leakage current (of %the order of 1 nA per single diode)
-%as a function of the bias voltage (I-V curve), the full depletion voltage (of 40 V) extracted from C-V curve and
-%the stability in time (leakage current versus time at a nominal bias).
-%The single diodes have capacitances of 8 $pF$.
-
-%\begin{figure}[!t]
-%\centering
-%\begin{tabular}{lll}
-%  \includegraphics[width=1.8in]{../figs/test.jpg} &
-%  \includegraphics[width=1.8in]{../figs/test2.jpg} &
-%  \includegraphics[width=1.8in]{../figs/test3.jpg}
-%\end{tabular}
-%\caption{I-V curve, C-V curve, leakage current vs time. \todo{Temporary picture: Triptic La Esperanza del Condenado, J. Miró}}
-%\label{shortslab}
-%\end{figure}
 
@@
   \centering
-    \includegraphics[width=2.8in]{../figs/test.jpg} 
-  \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
+    \includegraphics[width=6in]{../figs/short_slab_bga.jpg} 
+  \caption{Open single SLAB with FEV11 ASU, 16 SKIROC 2 and the interface card visibles. }
 \label{ASU2}
@@
 Figure \ref{ASU2}.
-With current SLABs, a potential density of
-4000 channels/dm$^{3}$ is achievable. This number should be compared with
-the density achieved for previous beam tests: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.
+The PCB thickness is 1.6 alone and 2.7 mm
+including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
+With these characteristics, a potential density of
+3160 channels/dm$^{3}$ is achievable for the baseline design 
+of the ILD. This number should be compared with
+the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.
+
+The SiW-ECAL detector designed for the ILD requires of the order
+of $10^{5}$ highly integrated detection like the ones described in this text.
+For the production of the small sample of SLABs studied in this document,
+a scalable working procedure has been established among several groups \cite{Boudry:2318814}
+profiting from the funding of projects like AIDA2020 or the HIGHTEC emblematic project
+of the P2IO. A schematic view of this assembly procedure chain can be seen in
+Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
 
@@
 \end{figure}
-
-The SiW-ECAL detector designed for the ILD requires of the order
-of $10^{5}$ highly integrated detection like the ones described in this text.
-For the production of the small sample of SLABs studied in this document,
-a scalable working procedure has been established among several groups \cite{Boudry:2318814}
-profiting from the funding of projects like AIDA2020 or the HIGHTEC emblematic project
-of the P2IO. A schematic view of this assembly procedure chain can be seen in
-Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
 
@@
 
-\subsubsection{Pedestal and noise determination}
-\label{sec:pedestal}
-
 The calibration runs have been used to calculate the pedestal distribution reference values 
@@
 In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
-subtracting the pedestal mean position. The results of the MIP calibration fit are included (red) and explained in the next version.
+subtracting the pedestal mean position. The results of the MIP calibration fit are shown in red (see Section \ref{sec:mip} for more details)
 The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range.
 The signal distribution is integrated over all SCAs.
+
+\subsubsection{Pedestal and noise determination}
+\label{sec:pedestal}
 
@@
 
-A Landau function convoluted with a Gaussian is fit to the resulting hit distribution. 
+After the pedestals are calculated and subtracted to the hit distributions, those are fit by
+a Landau function convoluted with a Gaussian.
 The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
@@
 
-In parallel to the ASUs equipped with BGA packaged ASICs, a different proposal for the ASU
+In parallel, a different proposal for a thiner ASU
 design is being investigated. This is motivated by the high density of channels
-demanded by the Particle Flow algorithms. Indeed, the FEV11 thickness is 1.6 alone and 2.7 mm
-including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
+demanded by the Particle Flow algorithms. 
 In this alternative PCB design the ASICs
@@
 A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
-with a total thickness of 1.2 mm allowing for a potential denisty of 10000 channels/dm$^{3}$ has been produced and tested in the laboratory
+with a total thickness of 1.2 mm (to be compared with the 2.7 of the LFBGA solution)
+has been produced and tested in the laboratory
 showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{cob}.
+These new boards maximize the density of channels (4800 channels/dm$^{3}$) for the ECAL of the ILD
+and will allow to satisfy the requirement of having 30 active layers in 20 cm length
+for the barrel areas of the ECAL.
 
@@
 
-Finally, many efforts in the compactification of
-the DAQ and the ASUs ({\it i.e.} the chip on board versions of the 
-ASUs described in Section \ref{sec:ASU}) are being
-conducted by the SiW-ECAL collaboration.
+Finally, intensive R\&D on the compactification of
+the DAQ towards meeting the ILD tight space requirements is being done by the SiW-ECAL collaboration.
 
@@
 and therefore the change to a new SCA is validated twice.
-This effect creates around 10-15\% of empty events which are easily filter and removed from the
-analysis. \todo{The ratio of empty triggers in the new SKIROC2a is reduced to the $\sim3\%$
-thanks to to a decrease of the OR64 size by a factor X.}
+This effect creates around 17\% of empty events which are easily filter and removed from the
+analysis. The ratio of empty triggers in the new SKIROC2a has been reduced to the $\sim2-3\%$.
 
@@
 Another well know issue is the appearance of bunches of consecutive fake triggers, called retriggers,
-that saturates the DAQ. These events are also
-characterized by triggering many channels (some times even all channels of an ASIC) at the same time.
-Although the ultimate reason of the appearance of these events remains unknown we
-think that they may be related to some distortion of the
+that saturates the DAQ. 
+Although the ultimate reason of the appearance of these events remains not clear, it
+is suspected that they are related to distortions of the
 power supply baselines. We know that the SKIROC2 and 2a preamplifiers are referenced to the analog power supply level,
-therefore, any voltage dip can ve seen as signal by the preamplifiers. The presence of a high inrush of current
+therefore, any voltage dip can ve seen as signal by the preamplifiers.
+Moreover the presence of a high inrush of current
 due to many channels triggered at the same time can create these voltage dips
-and produce the so called plane events (most of the channels trigered at once).
+and also produce the so called plane events (most of the channels trigered at once).
 In previous studies ({\it i.e.} reference \cite{Amjad:2014tha}), the ratio of retriggers and plane events
@@
 all layers and all ASICs analog and digital levels are powered using the same power supply.
-Moreover, the high voltage power supply for the polarization of the PIN diode it is also common for all layers.
+Moreover, the high voltage power supply for the polarization of the PIN diode is also common for all layers
+and the grounding levels of the low and high voltages supplied are shared within the slab.
 Therefore any noise in
@@
 
-Studying the MIP calibration data of this beam test we have noticed that the larger concentration of the retriggers and plane events are originated 
-in
-ASICs far from the beam spot. Even more, hot spots tend to appear near the channels 37 and the channels masked
-as suspicious of suffering from routing issues. The amount these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
+Studying the MIP calibration data of this beam test we have noticed that the 
+concentration of the retriggers and plane events in
+ASICs far from the beam spot is higher than in the ASICs that are reading
+out the information of real hits. Even more, this concentration is even higher near the channels
+37 and the channels masked as suspicious of suffering from routing issues.
+The ratio these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
 interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 KHz) and at higher rates even larger than $40\%$ in other 
@@
 
-All this information and dedicated studies in the laboratory will be used for the
-improvement of the power supplying system, the PCB design and for further SKIROC developments 
-with the possible approval the ILC in the scope.
+We should point out that these events are easilly filtered out during the analysis (or even during the online monitoring)
+and that no impact is observed
+in the data, {\it i.e.} in the MIP detection efficiency.
+
+%All this information and dedicated studies in the laboratory will be used for the
+%improvement of the power supplying system, the PCB design and for further SKIROC developments 
+%with the possible approval the ILC in the scope.
 

### 2018-06-13 performance-paper-draft/longversion/draft.tex
2nd iteration of the long version of the paper. Small correction in the desnity of channels comparison

@@
 meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.
+This feature is used for all data discussed in this paper
+and for first time in long periods of data taking in beam test.
 
@@
 of the ILD. This number should be compared with
-the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.
+the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
+With the first versions
+of the technollogical prototype we reached similar potential density level waw reached but equipping only a
+quarter of the ASUs surface \cite{Amjad:2014tha}.
 

### 2018-06-13 performance-paper-draft/longversion/draft.tex
2nd iteration long paper: correct the summary and other minor changes

@@
 beam test performance of a prototype built in with the first fully assembled
-detector elements.
+detector elements, in contrast with previous beam tests. In addition,
+with the setup used in this beam test we reached levels of granularity
+similar to the targets of the ILD detector for the ILC. This is also the first time
+that a SiW-ECAL prototype continuously takes data in a beam test running in power pulsing mode, one of the crucial
+features for the detectors for the ILC. Finally, we tested the performance of the detector
+modules working for long periods inside magnetic fields.
 
@@
 the performance of the detector and to perform
-a channel by channel calibration.
-A full analysis of the MIP calibration within magnetic field and
-the response of the prototype in electromagnetic shower events
-will be covered in a future document.
-In addition, the results shown here serve as input
-for ongoing and future R\&D.
+a channel by channel calibration, showing a good homogenity with a spread of the 5\% for all channels.
+The signal over noise of the detector has been evaluated to be 12.8 for the trigger
+decission and 20.4 for the charge measurement using, in both cases, MIP signals as reference.
 

### 2018-06-13 performance-paper-draft/shortversion/draft.tex
Short version, first iteration

@@
 
-\author{A. Irles}
+\author{corresponding author}
     % e-mail addresses: only for the forresponding author
@@
 This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
-the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.
+the calorimeters should work in self-trigger mode (each channel featuring a discriminator for internal trigger decision) and zero suppression mode.
 
@@
 
-The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
+The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype \cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
 It was successfully tested at DESY, FNAL and CERN running in front of another prototype from the CALICE
@@
 For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
-It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
+It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material
+adding a total of 24 $X_{0}$.
 The active layers were made of a matrix of 3x3 Si wafers of 500 $\mu$m thickness. Each of these wafers was segmented in matrices of
 6x6 squared channels of 1x1 $cm^{2}$, allowing for density of 1500 channels/dm$^{3}$
-The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
-(0.4, 1.6 and 2.4 $X_{0}$) making a total of 24 $X_{0}$.
 That very first prototype offered a signal over noise on the measured charge of 7.5 for MIP like 
-particles. More results proving the good performance of the technology and the PF can be found in
-references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
+particles.
 
@@
 The ASUs are currently equipped
-further with 16 SKIROC2\cite{}  (Silicon pin Kalorimeter Integrated ReadOut Chip)
+further with 16 SKIROC2\cite{Callier:2011zz,Amjad:2014tha,Suehara:2018mqk}  (Silicon pin Kalorimeter Integrated ReadOut Chip)
 ASICs for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
+Each channel of the SKIROC is made of a variable-gain preamplifier followed by two
+two branches: a fast line for trigger decission and a slow line for dual-gain charge measurement.
+The charges stored in the buffers of a switched capacitor array are converted by a 12-bit Wilkinson ADC.
+The ASIC also features power pulsing that allow to reduce its consomation to
+25 $\mu$W per channel. This feature is used for all data discussed in this paper
+and for first time in long periods of data taking in beam test.
 The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}.
@@
 The size of the wafer is $9\times9$ cm$^{2}$ and it is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
-A MIP (minimum ionizing particle) traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
+A MIP (minimum ionizing particle) traversing the PIN parallel to its normal will create
+$\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
 for particles incident perpendicularly to its surface.
 The high voltage is delivered to the wafers using a high voltage kapton sheet that covers the full extension of the wafers.
-The readout layers of the SiW-ECAL consist of a chain of Active Sensor Units (ASUs) and an adapter board
+
+The readout layers of the SiW-ECAL consist of a chain of ASUs and an adapter board
 to a data acquisition system (DAQ) at the beginning of the layer.
@@
 This ensemble is denominated SLAB
-(``short'' for 1 ASU ensembles or ``long'' for several ASUs enchained) and it can be seen in
-Figure \ref{ASU2}.
-With current SLABs, a potential density of
-4000 channels/dm$^{3}$ is achievable. This number should be compared with
-the density achieved for previous beam tests: 1500 channels/dm$^{3}$ \cite{Amjad:2014tha}.
-
-\begin{figure}[!t]
-  \centering
-    \includegraphics[width=0.4\textwidth]{../figs/test.jpg} 
-  \caption{\todo{Temporary picture: La Esperanza del Condenado, J. Miró}: Open single SLAB with FEV11 ASU, 16 SKIROC 2, interface card and DIF visibles. }
-\label{ASU2}
-\end{figure}
+(``short'' for 1 ASU ensembles or ``long'' for ensembles of several ASUs enchained).
+With current SLABs design, a potential density of
+3100 channels/dm$^{3}$ is achievable for the baseline ILD spatial constraints and $X_{0}$ requirements.
+This number should be compared with
+the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$. With the first versions
+of the technollogical prototype similar potential density level was reached but equipping only a
+quarter of the ASUs surface \cite{Amjad:2014tha}.
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/ASU_geometry1.eps}  \\
-    \includegraphics[width=0.4\textwidth]{../figs/ASU_geometry2.eps}  \\
+    \includegraphics[width=0.45\textwidth]{../figs/ASU_geometry1.eps}  \\
+    \includegraphics[width=0.45\textwidth]{../figs/ASU_geometry2.eps}  \\
   \end{tabular}
@@
 of $10^{5}$ highly integrated detection like the ones described in this text.
-For the production of the small sample of SLABs studied in this document,
+For the production of the sample of SLABs studied in this document,
 a scalable working procedure has been established among several groups \cite{Boudry:2318814}
-profiting from the funding of projects like AIDA2020 or the HIGHTEC emblematic project
+profiting from the funding of projects like the AIDA2020 or the HIGHTEC emblematic project
 of the P2IO.
 
-The subsequent chain of the data acquisition (DAQ) system \cite{Gastaldi:2014vaa} is inspired by the ILC.
-It consists on three layers of modules.
-The first layer, or most downstream layer, consists on a set of detector interfaces called DIFs which are placed at the beginning of each SLAB holding up to 15 ASUs.
-The second layer is made of concentrator cards module called the Gigabit Concentrator Cards (GDCCs)
+The subsequent chain of the data acquisition (DAQ) system \cite{Gastaldi:2014vaa} consists on three layers of modules.
+The first layer, or most downstream layer, consists on a set of detector interfaces called DIFs which are connected
+at the beginning of each SLAB to the ASUs via the adapter boards. They manage the communication with up to 15 ASUs.
+The second layer is made of concentrator card modules called the Gigabit Concentrator Cards (GDCCs)
 which are used to control up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
@@
 \begin{tabular}{l}
-\includegraphics[width=0.4\textwidth]{../figs/proto.png} 
+\includegraphics[width=0.45\textwidth]{../figs/proto.png} 
 \end{tabular}
@@
 in a magnetic field.
-\item Response to electrons of different energies with fully equipped detector, i.e. sensitive parts {\it and} W absorber, with three different repartitions of the absorber material:
-\begin{itemize}
-\item W-configuration 1: $0.6,1.2,1.8,2.4,3.6,4.8$ and $6.6~X_{0}$
-\item W-configuration 2: $1.2,1.8,2.4,3.6,4.8,6.6$ and $8.4~X_{0}$
-\item W-configuration 3: $1.8,2.4,3.6,4.8,6.6,8.4$ and $10.2~X_{0}$
-\end{itemize}
+\item Response to electrons of different energies with fully equipped detector, i.e. sensitive parts {\it and} W absorber.
 \end{enumerate}
@@
 a magnetic field in Section \ref{sec:magnet}. The study of the perfomance of the detector
-for electromagnetic shower events will be covered in future publciations.
+for electromagnetic shower events will be covered in future publications.
 
-\subsection{Commissioning}
+\subsection{Commissioning of the detector}
 \label{sec:commissioning}
@@
 electrons or positrons.
-This beam test was prepared by a careful and comprehensive commissioning comprising
-the debug of the
-short SLABSs with special emphasis in the control of the noise and the study of the
-prototype performance in cosmic rays tests. Dedicated runs at the laboratory were taken
-in order to identify and mask the noisy channels. The outcome of this study
-is that X\% of the channels were masked before putting the detector in front of the beam.
+
+The commissioning of the prototype for this beam test was focus in
+the control of the noise. Therefore, dedicated runs at the laboratory were taken
+in order to identify and mask the noisy channels.
 Two different kinds of noisy channels were found: the ones that are noisy on all
-SLABs and those which are only noisy in one or few of them. Preliminary inspections
+SLABs and those which are only noisy in one or a few of them. Preliminary inspections
 of the PCB hints that the first group is associated to routing issues on the PCB and
-hereafter they are labelled like this. The summary of this study is shown in Figure \ref{noisycells}.
+hereafter they are labelled like this. In addition, if a silicon wafer presented a problem
+(high leaking currents) or an ASIC was labelled as fulty (more than 70\% of channels identified as noisy)
+the corresponding sectors of the SLAB were fully masked.
+The summary of this study is shown in Figure \ref{noisycells}.
 These channels are removed from the data taking in all the studies shown from now on.
@@
   \begin{tabular}{l}
-  \includegraphics[width=0.4\textwidth]{../figs/commissioning/masked_layer.eps} \\
-  \includegraphics[width=0.4\textwidth]{../figs/commissioning/masked_chip.eps}
+  \includegraphics[width=0.45\textwidth]{../figs/commissioning/masked_layer.eps} \\
+  \includegraphics[width=0.45\textwidth]{../figs/commissioning/masked_chip.eps}
   \end{tabular}
@@
 
-\subsubsection{Trigger threshold optimization}
+\subsubsection{Trigger threshold optimization and S/N ratio in the trigger decission}
 \label{sec:comm_trigger}
 
-\todo{Autotrigger stuf.
-In order to select the optimal trigger threshold values for the detector operation
-we perform dedicated scans of trigger threshold values
-with all channels enabled (excepted the marked as noisy). }
-The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=0.4\textwidth]{../figs/commissioning/threshold_chip.eps}
-  \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
-\label{trigger_thresholds}
-\end{figure}
-
-\subsubsection{S/N ratio in the trigger line}
-\label{sec:comm_trigger_sn}
-
+The threshold of the auto-trigger is optimized to minimize the noise hits
+but maximizing at the same time the efficiency for measuring the signals associated
+to particles crossing the detector. For this purpose, dedicated scans of trigger threshold values
+with only noise signals or with injected signals of different sizes are done.
 In Figure \ref{scurves_injection} we see threshold scans curves
- curves obtained for several channel
-in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
- signals are directly injected in the preamplifier 
+ curves obtained for several channels
+in a SKIROC testboard \cite{uehara:2018mqk} in which a single SKIROC2 in BGA package is placed and signals of 1 MIP and 2 MIPs size
+are directly injected in the preamplifier 
 (via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}). 
-From this plot we can extract a S/N ratio of $\sim$12.8. 
-Unfortunately, this results has obtained using
-a dedicated board thought for commissioning and test of the SKIROC ASICS in an
-"ideal" environment in contrast with the fully equipped
-ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
-We do not expect large differences with the results that we would obtain with 
-a full equipped SLABs but dedicated runs in beam test will be needed.
+From this plot we can extract a S/N ratio of $\sim$12.8. Similar results are expected for
+fully equipped ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
+The final choice of the trigger threshold values for all ASICs is shown in Figure \ref{trigger_thresholds}.
 
@@
   \begin{tabular}{l}
-	\includegraphics[width=0.4\textwidth]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
+	\includegraphics[width=0.45\textwidth]{../figs/commissioning/scurve_pp_fastshaper_ch_au.eps} \\
 	\end{tabular}
-\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard.
-From this plot, we extract a $S/N = 12.8$ in the trigger line.
-\todo{We need to use charge in the axis}}
+\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
 \label{scurves_injection}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.45\textwidth]{../figs/commissioning/threshold_chip.eps}
+  \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
+\label{trigger_thresholds}
 \end{figure}
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/mip_pedestal_example.eps}
+    \includegraphics[width=0.45\textwidth]{../figs/mip_pedestal_example.eps}
   \end{tabular}
@@
 The pedestal correction is done layer-, chip-, channel- and SCA-wisely due to the large spread of values between pedestals, as observed in 
-Figure \ref{pedestal_layer} (upper plot) and Figure \ref{pedestal_all} (also upper plot).
-For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the lower plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
+Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
+For the noise, the dispersion is much smaller ($\sim 5 \%$). This is shown in the right plots of Figures \ref{pedestal_layer} and \ref{pedestal_all}.
 From now on, the pedestal correction is applied to all the results presented.
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/ped_mean_layer2.eps} \\
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/width_mean_layer2.eps}
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/ped_mean_layer2.eps} \\
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/width_mean_layer2.eps}
   \end{tabular}
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/h_ped_mean.eps} \\
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/h_ped_width.eps}
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/h_ped_mean.eps} \\
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/h_ped_width.eps}
   \end{tabular}
@@
 We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
-available channels being fitted. Results are summarized in figure \ref{mipandSN}, upper plot.
+available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/MIP/MIPsummary_title.eps} \\
-    \includegraphics[width=0.4\textwidth]{../figs/MIP/SNsummary_title.eps}  
+    \includegraphics[width=0.45\textwidth]{../figs/MIP/MIPsummary_title.eps} \\
+    \includegraphics[width=0.45\textwidth]{../figs/MIP/SNsummary_title.eps}  
   \end{tabular}
-\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated channels.}
+\caption{Result of the MIP calibration and signal over noise for the measured charge for all calibrated channels.}
 \label{mipandSN}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=0.4\textwidth]{../figs/MIP/MIP3peaks.eps} 
+      \includegraphics[width=0.45\textwidth]{../figs/MIP/MIP3peaks.eps} 
     \end{tabular}
@@
     \begin{tabular}{l}
-      \includegraphics[width=0.4\textwidth]{../figs/MIP/efficiency_nhits4_chips.eps} \\
-      \includegraphics[width=0.4\textwidth]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} 
+      \includegraphics[width=0.45\textwidth]{../figs/MIP/efficiency_nhits4_chips.eps} \\
+      \includegraphics[width=0.45\textwidth]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} 
     \end{tabular}
@@
 has been calculated for all channels and all layers. The average S/N is to 20.4.
-Results are summarized in Figure \ref{mipandSN}, rightmost plot.
+Results are summarized in Figure \ref{mipandSN}, lower plot.
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/1T/summary_pedestal_chip12.eps} \\
-    \includegraphics[width=0.4\textwidth]{../figs/pedestal/1T/summary_noise_chip12.eps}
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/1T/summary_pedestal_chip12.eps} \\
+    \includegraphics[width=0.45\textwidth]{../figs/pedestal/1T/summary_noise_chip12.eps}
   \end{tabular}
@@
 beam test performance of a prototype built in with the first fully assembled
-detector elements. In contrast with previous beam test, in this one we have fully
-assembled detector elements meeting ILD requirements and the higher level of
-density channel and total granularity achieved so far by this calorimeter.
+detector elements, in contrast with previous beam tests. In addition,
+with the setup used in this beam test we reached levels of granularity
+similar to the targets of the ILD detector for the ILC. This is also the first time
+that a SiW-ECAL prototype continuously takes data in a beam test running in power pulsing mode, one of the crucial
+features for the detectors for the ILC. Finally, we tested the performance of the detector
+modules working for long periods inside magnetic fields.
 
@@
 the performance of the detector and to perform
-a channel by channel calibration.
-A full analysis of the MIP calibration within magnetic field and
-the response of the prototype in electromagnetic shower events
-will be covered in a future document.
-
-In parallel to the work described here, several R\&D efforts are being carried
-and the results shown here are crucial for the next steps in the R\&D program.
-
-One of these efforts is directed to the design and test of new ASICs.
-In fact, a new generation of SKIROC2, the 2a, has been delivered
-and it is being tested in the dedicated testboards and in a new generation of ASUs.
-%In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
-%In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
-
-Many efforts are also concentrated in the construction and test of long SLABs
-made of several ASUs enchained since we know that the ILD ECAL will host long layers of up to $\sim$2.5m.
-This device constitutes a technological challenge in both aspects, the mechanical
-(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
-and the electrical (i.e. transmission of signals and high currents).
-For example, interconnections between ASUs and between ASU and interface card are one of
-the most involved parts of the assembly
-and require close collaboration between mechanical and electronic engineers.
-The construction and test of a long SLAB prototype
-of $\sim8$ ASUs is currently ongoing.
-
-In parallel to the ASUs equipped with BGA packaged ASICs, a different proposal for the ASU
-design is being investigated. This is motivated by the high density of channels
-demanded by the Particle Flow algorithms. Indeed, the FEV11 thickness is 1.6 alone and 2.7 mm
-including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
-In this alternative PCB design the ASICs
-are directly placed on board of the PCB in dedicated cavities.
-The ASICS will be in semiconductor packaging and wire bonded to the PCB. This is the so-called COB (chip-on-board) version of the ASU.
-A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
-with a total thickness of 1.2 mm allowing for a potential denisty of 10000 channels/dm$^{3}$ has been produced and tested in the laboratory
-showing its readiness for tests with particle beams.% A sample can be seen in Figure \ref{cob}.
-In addition, many efforts in the compactification of
-the DAQ and the SLABs are currently being carried by the SiW-ECAL collaboration.
-
-It is foreseen that all these developments, with the exception of the SKIROC3, will be tested with particle beams during 2018-2019.
+a channel by channel calibration, showing a good homogenity with a spread of the 5\% for all channels.
+The signal over noise of the detector has been evaluated to be 12.8 for the trigger
+decission and 20.4 for the charge measurement using, in both cases, MIP signals as reference.
 

### 2018-08-07 performance-paper-draft/longversion/draft.tex
Revision from comments. Abstracts and Sections 1,2,3 corrected. To be done: following sections + update Fig 5a to use separate bars + figure 7 use DAC in the x-axis

@@
   The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
-  design and R\&D is tailored to the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
-  In this document we present and discuss the commissioning of the prototype
-  and the performance of the device in a beam test carried at DESY in June 2017.
+  design and R\&D is oriented at the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
+  In this article we present the commissioning and the performance of the prototype in our beam test carried at DESY in June 2017.
 }
@@
 The SiW-ECAL is the baseline choice for the ILD electromagnetic calorimeter.
-It consists in a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
+It consists of a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
 It has silicon (Si) as active material and tungsten (W) as absorber material.
@@
 embedded in the detector units. The silicon sensors will be segmented
-in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million channels will constitute the ECAL for ILD.
+in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD.
 The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs.
 To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
-foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive within
-acquisition windows of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. During the idle time, the bias currents of the electronics will be shut down.
+foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive in spills
+of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. The data acquisition will be gated during these short windows and during the idle time the bias currents of the electronics will be shut down.
 This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
@@
 
-The new generation prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
+The current prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
 power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
@@
 
-The sensors consist on floating zone silicon wafers 320$\mu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
-The size of the wafer is $9\times9$ cm$^{2}$ and it is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
+The sensors consist of high resistivity (bigger than 5000 $\Omega\cdot$cm)
+%floating zone
+silicon wafers with a thickness of 320$\mu$m.
+The size of the wafers is $9\times9$ cm$^{2}$ and they are each subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
 A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
@@
 It was observed in beam tests \cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
-and the channels at the edge was not negligible in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV).
-This coupling lead to fake events in which, at least,
-the channels in the four edges of the wafer are triggered at the same time. 
-This is why these events are called squared events. 
+and the channels at the edge created not negligible rates off fake
+events in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV)
 An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-rings design 
-as well as the internal crosstalk.
-%As outcome of this R\&D program, the technological prototype 
-%is equipped with silicon wafers with:
-It was concluded that using wafers without guard rings and with a width of the peripheral areas lower than 
-500 $\mu$m thanks to the use of stealth dicing technique, the amount of these squared events 
-can be reduced to be almost negligible. This need to be confirmed in beam test.
-Unfortunately, for the interaction with low energy particles as the delivered at the
-DESY beam test facility (see Section \ref{sec:beamtest}) the
-amount of squared events is expected to be negligible, therefore we will not discuss this issue in the following.
+as well as the internal crosstalk. It was concluded that using wafers without guard rings and with a width of the peripheral areas lower than 
+500$\mu$m thanks to the use of stealth dicing technique, the amount of these squared events 
+can be reduced to be at negligible level.
+
+For the setup described this article we used different solutions for the edge terminations.
+For all of them, the levels of fake events are at negligible level due to
+the low energy of the beam used to test the prototype. Therefore, they are not further described here.
 
@@
 \label{sec:skiroc}
+
+\begin{figure}[!ht]
+  \centering
+    \includegraphics[width=4in]{../figs/skiroc2_block.eps}
+\caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
+\label{SKIROC2}
+\end{figure}
 
@@
 In its version SKIROC2 it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
+A schematic view of the analog part of the SKIROC2 is shown in Figure \ref{SKIROC2}.
 Each channel comprises a low noise charge preamplifier of variable gain followed by two branches:
@@
 The gain can be controlled by modifying the feedback capacitance during the configuration of the detector.
-With the slowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs 
-(a slightly less than the desired final value for the ILC). 
+With the lowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs. 
 Finally, a Wilkinson type analogue to digital converter fabricates the digitized charge deposition that can be readout. 
@@
 The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
-the bias currents of the ASIC can be switched off during the idle time between bunch trains.
+the bias currents of the ASIC can be shut down during the idle time between bunch trains.
 With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
-meeting the ILC requirements. All the results shown in this paper are obtained in power pulsing mode.
-This feature is used for all data discussed in this paper
+meeting the ILC requirements. 
+The power pulsing feature is used for all the results discussed in this paper
 and for first time in long periods of data taking in beam test.
-
-\begin{figure}[!t]
-  \centering
-    \includegraphics[width=4in]{../figs/skiroc2_block.eps}
-\caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
-\label{SKIROC2}
-\end{figure}
 
@@
 
+Current version of the PCB is called the FEV11. It has a thickness of 1.6mm and 2.7mm
+if we include on top the ASICs in its current packaging (1.1 mm thick LFBGA package).
+With these characteristics, a potential density of
+3800 channels/dm$^{3}$ is achievable keeping the space and
+interaction length requirements of the the baseline design of the ECAL forthe ILD.
+This number should be compared with
+the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
+With the first versions
+of the technollogical prototype we reached similar potential density level as in
+the current version but equipping only a
+quarter of the ASUs surface \cite{Amjad:2014tha}.
+
 \subsection{Data AcQuisition system}
@@
 
-The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system is inspired by the ILC.
-It consists on three modules.
-The first module is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs;
-All DIFs are connected by single HDMI cables to the concentrator cards that make
-the second module: the Gigabit Concentrator Cards (GDCCs).
-%The HDMI connection is used to transmit both slow control and data readout.
-This cards are used to control up to 7 DIFs collecting all data from them and distributing among them the system clock and fast commands.
-The last module, the most downstream, is the clock and control card (CCC) which
+The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system consists of three components, enumerate from upstream to downstream from the data flow perspective:
+
+\begin{enumerate}
+\item The first component is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs.
+\item All DIFs are connected by single HDMI cables to the concentrator cards as the second component: the Gigabit Concentrator Cards (GDCCs).
+These cards are used to control up to 7 DIFs.
+They collect all data from the DIFs and distribute among them the system clock and fast commands.
+  \item The most downstream component, is the clock and control card (CCC) which
 provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
 generated external pulse generator to simulate the ILC spill conditions).
+\end{enumerate}
+
 The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~\cite{Rubio-Roy:2017ere,Magniette:2018wdz}.
-%The Pyrame framework provides basic blocks (called modules) of control-command or data acquisition.
-%Calicoes is specific the implementation of these blocks for control-command and data acquisition of the SiW-ECAL prototype. 
-%This new version of the DAQ software implements a new mechanism to allow any module to treat and publish data in real time. 
-%Those data are made available to any requesting module, in particular to a new online monitor module developed
-%for this beam test, allowing for quick online checks of the data quality and integrity.
 
-\subsection{Readout layers and SLABs}
+\subsection{Fully equipped readout modules: the SLABs}
 \label{sec:setup}
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
   \centering
@@
 
-The readout layers of the SiW-ECAL consist of a chain of ASUs and an adapter board
-to a data acquisition system (DAQ) at the beginning of the layer.
-This adapter board is called SMBv4
-and it also serves as to hold other services as power connectors or the super capacitances used for the power pulsing. 
+A full equipped readout module is shown in Fig. \ref{ASU2}. These modules are called
+SLABs and consist of a chain of one or several fully equipped ASUs
+connected to a data acquisition system (DAQ) through an adapter board, called SMBv4.
+The SMBv4 also serves as to hold other
+services as power connectors or the super capacitances used for the power pulsing. 
 These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance. 
-The purpose of these capacitances is to provide local storage 
-of the necessary charge to avoid the transport of current pulses over long cables, 
-ensuring in this way the stability of the ASICs during the acquisition.
-
-The readout layers are embedded on a "U" shape carbon structure to protect the wafers.
+The capacitances are extra dimensioned to provide enough local storage 
+of power to assure stable low voltage levels during the power pulsing. %In this configuration
+%the high currents are still crossing the interconnections/
+The readout modules are embedded on a "U" shape carbon structure to protect the wafers.
 The full system is then covered by two aluminum plates
 to provide electromagnetic shielding and mechanical stability.
-This ensemble is denominated SLAB
-(``short'' for 1 ASU ensembles or ``long'' for several ASUs enchained) and it can be seen in
-Figure \ref{ASU2}.
-The PCB thickness is 1.6 alone and 2.7 mm
-including the ASICs in its current packaging: 1.1 mm thick LFBGA package.
-With these characteristics, a potential density of
-3160 channels/dm$^{3}$ is achievable for the baseline design 
-of the ILD. This number should be compared with
-the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
-With the first versions
-of the technollogical prototype we reached similar potential density level waw reached but equipping only a
-quarter of the ASUs surface \cite{Amjad:2014tha}.
 
-The SiW-ECAL detector designed for the ILD requires of the order
-of $10^{5}$ highly integrated detection like the ones described in this text.
 For the production of the small sample of SLABs studied in this document,
@@
 Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
+This process is to be extrapolated to a full assembly procedure for
+e.g. the ILD detector.
 
@@
 \begin{tabular}{l}
-\includegraphics[width=6.0in]{../figs/assembly.png} 
+\includegraphics[width=4.0in]{../figs/assembly.png} 
 \end{tabular}
@@
 
+\subsection{The prototype setup}
+\label{sec:setup2}
+
+A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
+Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10, in slots separated by 15mm each.
+The first six layers were placed in the first six slots and the last one was in the last slot. In the following sections, we will refer to layers number 1 to 7, where
+the 1 is the closest to the beam pipe and 7 is the farthest.
+This setup is used for commissioning (Section \ref{sec:commissioning}) and for the beam test
+(Section \ref{sec:beamtest}). In both cases, the detector was
+running in power pulsing mode.
+
+\begin{figure}[!ht]
+\centering
+\begin{tabular}{l}
+\includegraphics[width=4.0in]{../figs/proto.png} 
+\end{tabular}
+\caption{Prototype with 7 layers inside the aluminum stack.}
+\label{proto}
+\end{figure}
+
 \section{Commissioning}
@@
 
-This beam test was prepared by a careful and comprehensive commissioning comprising
+This beam test was prepared by a commissioning phase comprising
 the debug of the
 short SLABSs with special emphasis in the control of the noise and the study of the
-prototype performance in cosmic rays tests.
+prototype performance in cosmic ray tests.
 
-Earlier experiences with the SKIROC2 ASIC are reported in Refs. \cite{Amjad:2014tha,Suehara:2018mqk}). 
-Internal SKIROC2 parameters found in these references are adopted in the following
-except if the opposite is stated.
-For example, the gain value of 1.2pF for the preamplifier is used. 
-With this gain, the SKIROC2 ensures a linearity better than 90\% 
-for 0.5-200 MIPs, which is enough for 
+Earlier experiences with the SKIROC2 ASIC are reported in
+Refs. \cite{Amjad:2014tha,Suehara:2018mqk}). 
+Internal SKIROC2 parameters reported in these references are adopted in the following
+unless stated otherwise.
+For example, a gain value of 1.2pF for the preamplifier is used. 
+With this gain, the SKIROC2 features a linearity better than 90\% 
+for 0.5-200 MIPs, which is sufficient for 
 electromagnetic showers created by few GeV 
 electrons or positrons.
-% The delay of the trigger signal is the same than in 
-%reference \cite{Amjad:2014tha,Suehara:2018mqk}: 130 DAC for all ASICS. 
-%This value was chosen by selecting the delay in which an injected signal
-%of few MIPs of value get the maximum value of ADC. %Finally, the value of the
-%compensation capacitance at the output of the preamplifier has been set to 6pF instead of 
-%4pF to prevent overshots and ripples of the signal used as input to the trigger
-%decision and ADC lines.
 
-\subsection{Optimization of noise levels}
+The main goal of the the commissioning  procedure is 
+the optimization of the trigger thresholds to levels in which we are able
+to record physics signals bellow the MIP level without saturating our DAQ with
+noise signals. This requires a careful and systematic procedure to:
+
+\begin{enumerate}
+  \item identify the readout channels that are noisy in high trigger threshold above MIP signal conditions
+  \item and select the optimal trigger threshold levels.
+\end{enumerate}
+
+During the commissioning, we observed the repetition of coherent noise events affecting to several
+SLABs at the end of acquisitions with long gating time. The situation
+could be remedied by improving the isolation of the individual SLABs and by reducing the
+data taking to short gating times.
+
+All runs dedicated to the commissioning were characterized by:
+\begin{itemize}
+  \item their short gating windows for the acqusition (1-2ms)
+   at low repetition frequencies (1-5 Hz) to minimize the chances of having real events due to cosmic rays during the data taking and the coherent noise events due to grounding issues;
+ \item and the relatively high trigger threshold values between 400 and 250 DAC 
+(which are equivalent to $\sim$2 and $\sim$0.5 MIP respectively, see Section \ref{sec:comm_trigger} for more information).
+\end{itemize}
+
+\subsection{Tagging and control of the noisy channels.}
 \label{sec:comm_noise}
 
-%The purpose of this phase was to monitor and control the
-%noise levels of the prototype.
-%The commissioning includes the definition of trigger threshold values and a list of noisy channels to be masked.
-Studying and control the noise levels
-is crucial since noisy channels may saturate the DAQ faster than physical signals.
-Two different types of noise sources were identified:
-a set of noisy channels randomly distributed in time 
-and noise bursts affecting to all layers at the same time.
-The outcome of this commissioning is summarized in Figure \ref{noisycells}.
+We found to different types of noisy channels. One set consists of
+channels randomy distributed along the surface of every ASU and the oter consists
+of channels systematically noisy in all the ASUs. Preliminary inspections of the PCB layout
+hint that the channels in the latter set are noisy due to
+improvable routing of the PCB.
+Deeper studies on the PCB routing must be conducted to clarify this.
+All the noisy channels have been identified and masked and the power
+of their preamplifiers has beem disabled. All the results shown in the following
+sections are obtained in these conditions.
 
-The first type of noise source, noise events randomly distributed in time,
-forced us to define a list of channels to be masked in all 
-layers. Again, two different type of noisy channels have been identified. 
-The first group is compose by randomly distributed in space channels.
-The second group is made of
-a fixed list of channels, all in the same positions for all SLABs,
-and all associated to a higher rate of events with underflowed value
-of the read ADC.
-%The latter set of channels were identified by means of the online monitoring
-%tools.
-%As channels are located in the same place for all SLABs,
-%we took the conservative assumption
-%that all modules would have problems in the same set of channels.
-%For example, all channels number 37.
-A large amount of these channels are located
-in areas of the PCB where the density of lines 
-(data and power transmission) is higher than in others.
-This hints for an issue on the routing of the PCB.
-Therefore, these channels are tagged in Figure \ref{noisycells} with the "routing issues" label
-although more tests and deeper inspections of the PCB layout are needed to clarify this issue.
+The list of the noisy channels was
+obtained by means of dedicated data taking runs. In these runs
+we scan trigger thresholds and progressively mask channels that exhibit counts. 
+In each step, the decission of tagging a channel as noisy was taking following the next rules:
 
-The list of the noisy channels randomly distributed in time and space was
-defined by means of dedicated data taking runs. 
-These runs were characterized by: their short acquisition windows (open to data recording for 
-only 1.1 ms) at low repetition frequencies (5 Hz) to minimize the chances of having real events due to cosmic rays 
-hitting the detector during the
-data taking; and the relatively high trigger threshold values between 250 and 400 DAC 
-(which are equivalent to $\sim$0.5-2 MIP, see Section \ref{sec:comm_trigger} for more 
-information). The full process was an iterative process starting with several repetitions
-of runs at a high threshold value and then some iterations at lower threshold but always 
-higher than 0.5 MIP. 
-In each of the iterations, the channels identified as noisy were masked.
-A full run involved 3-5 threshold values and at least two repetitions per value.
-Again, we decided to follow a conservative approach for list the noisy channels to be masked:
-if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC
-it was added to the list. These channels are labeled as "other" in the first plot in  Figure \ref{noisycells}.
+\begin{itemize}
+\item if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC it was added to the list;
+\item if a channel was tagged as noisy in, at least, three of the SLABs, it was tagged as noisy for all and added to the list of channels being suspect of suffer from routing issues.
+\end{itemize}
 
@@
 masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
-listed as noisy) or if a Si-wafer was misworking (high leakage currents). In these cases 
-and in all mentioned above, the masking involved two steps: disabling of the trigger and 
-the disabling of the power of the preamplifier of that channel.
+listed as noisy) or if a Si-wafer was damaged (high leakage currents).
+The results of this study is summarized in Figure \ref{noisycells}.
 
@@
   \end{tabular}
-\caption{Ratio of channels that are marked as noisy in all slabs. 
+\caption{Fraction of channels that are tagged as noisy in all slabs. 
 Top: inventory of the different type of noisy channels per slab. 
@@
 
-The other source of noise mentioned at the beginining of this section
-consist on noise bursts happening coherently at the same time in all SLABS
-and it was correlated to occasions when the electrical isolation between SLABs was broken.
-This is a hint of a system effect as can be the appearance of
-grounding loops or disturbances in the power supplies.
-The issue was circumvented by improving the electrical isolation of single layers.
-We have also observed that the noise bursts happens only at the end of long acquisitions. Therefore, in addition to the improved isolation,
-we selected short enough acquisitions windows (which indeed are the most appropriate to the high rates of particles in the DESY beam).
-Ddedicated studies in the laboratory are currently pngoingin order to fully understand this issue.
-
-The list of channels mentioned above is discarded from the data taking from now on.
-
-\subsection{Threshold determination}
+\subsection{Optimal trigger threshold determination}
 \label{sec:comm_trigger}
 
-In order to select the optimal trigger threshold values for the detector operation
-we perform dedicated scans of trigger threshold values
-with all channels enabled (excepted the marked as noisy). 
-The threshold values are given in internal DAC units which are translated to
-meaningful physical quantities in Section \ref{sec:comm_trigger_sn}. 
-The threshold scan curves made of the total number of hits normalized to 1 vs the threshold
-for each channel are modeled by a complementary error function called ThS curves from now on:
+After the noisy channels have been masked, dedicated trigger threshold
+scan run are taken, and the results are shown in threshold scan curves where the
+x-axis represents the threshold value\footnote{The threshold values are given in internal DAC units which are translated to
+meaningful physical quantities in Section \ref{sec:comm_trigger_sn}.} and the y-axis
+the number of recorded signals normalized to 1.
+In the absence of external signals (cosmic rays, injected signals, etc) 
+the falling edge position in the threshold scan curves
+is due to the electronic noise
+at the output of the fast shaper (the trigger decision branch on the SKIROC)
+and it depends on the slow clock frequency.
+These threshold scan curves are approximated by a complementary error function:
 
 \begin{equation}
-ThS(DAC)=p_{0} \times erfc(\frac{DAC-p_{1}}{p_{2}}) = 
-\newline
 \frac{2p_{0}}{\sqrt(\pi)} \int_{\frac{DAC-p_{1}}{p_{2}}}^{\infty} e^{-t^{2}} dt,
@@
 
-In the absence of external signals (cosmic rays, injected signals, etc) 
-these noise ThS curves show the convolution of the envelope of the 
-electronic noise at the output of the fast shaper (the trigger decision branch on the SKIROC).
-Indeed, the size of this envelope is related to the slow clock frequency.
+In Figure \ref{scurve_channels} 
+two threshold scans curves are shown together with the fit by
+the theoretical function for two different channels from the second
+layer of the setup are shown.
 
-To reduce to the minimum the presence of cosmic rays signals, 
-we perform runs with short open acquisition windows
-as described in the previous section.
-In Figure \ref{scurve_channels} 
-two result of two threshold scans and the fit by
-a ThS curves for two different channels from the second layer of the setup are shown.
-
-\begin{figure}[!t]
+\begin{figure}[!ht]
   \centering
@@
   \end{tabular}
-\caption{Two threshold scan curves and their associated ThS curves.}
+\caption{Two threshold scan curves.}
 \label{scurve_channels}
@@
 
-The function from equation \ref{eq_S-curve} was fitted to all
-channels data and all the values of $p_{1}$ and $p_{2}$ were saved.
+For every ASICs, after performing the fit of the theoretical curves
+to the threshold scans, the average values of the   $p_{1}$ and $p_{2}$ are calculated.
+These are represented by $<p_{1,2}^{ASIC}>$ in the following.
 The final threshold value of every ASIC, in DAC units, was chosen 
-by taking the
+using the following formula
+\begin{equation}
+DAC_{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
+\end{equation}
+This formula was applied 
+if at least the the 30\% of the 64 channels in the ASIC could be fitted.
+If not, a global DAC value of 250 was set.
 
-\begin{equation}
-maximum(DAC_{optimal}^{ASIC-j} = <p_{1}^{ASIC-j}> + 5 \times <p_{2}^{ASIC-j}>,230)
-\end{equation}
+The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}, in internal DAC units and in MIPs. In the next section we explain how the conversion is done.
 
-if at least the the 30\% of the 64 channels ThS curves in the ASIC could be fitted.
-If only less  than the 30\% of curves of the 64 channels were
-succesfully fit, a global DAC value of 250 was set.
-The $<>$ denotes the average over all the channels on the ASIC.
-The choice of these two values was 
-sustained by previous experiences, see for example \cite{Amjad:2014tha}.
-
-The optimal trigger threshold values for all ASICs are shown in Figure \ref{trigger_thresholds}.
-
-\subsection{S/N ratio in the trigger line}
+\subsection{S/N ratio in the trigger branch}
 \label{sec:comm_trigger_sn}
 
-Similar kind of measurements can be done but using external signals. 
-This will allow to calculate the signal over noise (S/N) ratio to trigger 1 MIP signals.
-To calculate the S/N of the trigger we need to compare the 1 MIP ThS curve and 2 MIP ThS curve. The S/N 
-will be defined as the ratio between the distance of both ThS curves at its 50\% and the width of the 
-ThS curve.
-
-In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP ThS curves obtained for several channel
+Performing threshold scan scurves using
+real signals allow to calculate the signal over noise (S/N) ratio to trigger.
+For that we compare the curves for 1 MIP and 2 MIP injected signals.
+The S/N is, therefore, defined as the ratio between the distance of both curves at its
+50\% and the width of the curves.
+In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP curves obtained for several channel
 in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
@@
 (via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}).
-From this plot we can extract a S/N ratio of $\sim$12.8. 
-We do not expect large differences with the results that we would obtain with 
-a full equipped SLABs 
-although this board is thought for commissioning and test of the SKIROC ASICS in an
-"ideal" environment in contrast with the FEV
-ASUS that are optimized to meet the detector requirement and to hold several ASICs at the same time.
-%For example: only power pulsing of the analog power is done in this testboard,
-%there is a set of external capacitors on the board connected to some ASIC pins and
-%usually only one channel is tested. This board allows us to commission and debug the SKIROC itself
-%but not the full system.
 
@@
 	\end{tabular}
-\caption{ThS curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard. From this plot, we extract a $S/N = 12.8$ in the trigger line.}
+\caption{Threshold scan curves with charge injection (1 MIP in blue and 2 MIPs in red) for two different channels in a SKIROC2 testboard.}
 \label{scurves_injection}
@@
 
-We have obtained similar results using real signals, in this case cosmic rays signals by using very long
-acquisition windows of 150 ms at 5 Hz. This is shown 
+We have obtained similar results using real signals, in this case cosmic rays signals. This is shown 
 in Figure \ref{scurves_cosmics}  where 
-we show the result of the fit to the noise ThS curves for all channels individually (in red) in one of the ASICs of 
-the second layer together with the results of the ThS curve obtained with cosmic rays integrated for all channels
-(black points and blue line).
-%For the cosmic ThS curve we took 30 min of data per point using very long spills (150 ms) in 
-%frequencies of 5Hz and we add up the triggers from all channels together. In addition, using the 
-%knowledge of the MIP value (see next section), we performed a simple cut in the ADC
-%to keep only signals corresponding to a MIP 
-%(pedestal subtracted) $\pm30$ ADC counts. With this cut we try reduce the contribution of muons 
-%traversing the wafers with very large angles but we don't have a way to select perpendicular tracks 
-%since we were using simple setups with only single slabs. 
-We expect
-a broader distribution of the cosmic ThS curve since muons can traverse
-the detector at different incidence angles.  
-In addition to this, we should remember that the noise ThS curve do correspond to the real noise 
-distribution but only to the envelope of the noise in the fast shaper, therefore the
-distance between the two ThS curves is smaller than the real distance between noise and signal.
-Therefore, if we calculate the S/N 
-using this plot, the value would be unrealistic but at least provides 
-the comparison between the ThS curve for 1 MIP real and injected signals.
+we show the result of the fit to the threshold scan curves cosmic rays integrated for all channels
+in one ASIC. For completeness, the fit of threshold scan curves for all channels
+in the same ASIC are also shown.
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
     \centering
@@
 	\end{tabular}
-\caption{ThS curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
+\caption{Threshold scan curves for noise (channel by channel, only the result of the fit) and cosmic rays (all channels together) for one ASIC in layer 2.}
 \label{scurves_cosmics}
@@
 
-Both ways of estimating the S/N ratio of the trigger have their own limitations
-and dedicted studies in beam test are needed in order to
-precisely determine it.
-In the meanwhile, combining the information contained in the Figs \ref{scurves_injection} and \ref{scurves_cosmics},
-we can estimate the value in energy at wich we have set our trigger threshold.
-This is shown in Figure \ref{trigger_thresholds}.% Two ASICS have a
-%trigger threshold value of 0.67 MIP. The 11\% of the ASICs have a trigger threshold between 0.5 and 0.55 MIP and the rest, 87\%, have trigger thresholds slightly lower 0.5 MIP.
+From these two results we extract the value of
+\begin{equation}
+  S/N=12.9\pm3.4
+\end{equation}
+for the trigger branch. The central value is calculated from the comparison of the blue and red curves
+in Figure \ref{SKIROC2} and using the width of the 1 MIP curve in the denominator. The estimated
+uncertainty has two components: the difference of width between the 1 and 2 MIP curves of injected signals and the differences (width and middle point) between the 1 MIP curves for injected and
+cosmic ray signals.
+
+Dedicated studies in beam test are needed in order to
+reduce the uncertainty of this measurement.
+However, by combining the information contained in the Figs \ref{scurves_injection} and \ref{scurves_cosmics}, we can also estimate the energy that corresponds
+to a given trigger threshold.
+This is shown in Figure \ref{trigger_thresholds}, where the chosen threholds of every ASIC being tested
+in beam are shown.
 
@@
 
-All the commissioning procedure described above relies in very conservative decisions
-due to the presence of unknown noise sources during most of the commissioning phase. These sources are
-now well know and isolated and therefore a new ``noise commissioning procedure'' has been studied.
-It will consist in an iterative algorithm that first
-will identify and mask the channels giving underflowed signals and afterwards run a set of acquisitions
+The commissioning procedure described above relies on very conservative decisions
+due to the presence of unknown noise sources during largest of the commissioning phase.
+These sources are
+now well know and therefore a new ``noise commissioning procedure'' has been studied.
+It will consist on an iterative algorithm that first
+will identify and mask the channels
 in which the number of triggers per channel will be compared with the number of expected triggers
-assuming only cosmic rays as signal. This will allow us to have an
-unambiguous definition of the noise levels channel per channel instead of 
-defining such levels relatively to the total number
-of recorded triggers per ASIC. Finally, once that the noisy channels
-are identified, the optimization of the threshold levels
-will be performed and a last run for identification of noisy channels will be taken using this optimal
-threshold.
-%In this run, we can decide to mask the noisy channels or
-%to increase its own trigger threshold level if we are using Skiroc2a.
+assuming only cosmic rays as signal. This will allow us to have a
+definition of the noise levels for each channel independently
+instead of relative to the total number of triggers recorded by
+the ASIC. Finally, once the noisy channels
+are identified, the threshold  are further optimized
+with a last run for the identification of the residual noisy channels.
 
-Using this new procedure we manage to reduce the number of masked channels by a factor 2 without any loss of performance,
-at least in the laboratory and using 3 of the 7 SLABs. This new procedure will be tested in the next beam test.
+Using this new procedure we manage to reduce the number of masked channels by a factor of two
+without any loss of performance, at least in the laboratory and using 3 of the 7 SLABs.
+This new procedure will alo be applied in the next beam test.
 Also, in order to
@@
 we propose a new set of measurements in the next beam test such as
-a scan of optimal delay of the hold values of the trigger using MIP like particles
-and a threshold scan for the determination of the S/N in the trigger line. This later
-can be done by the comparison of ThS curves taken with 1 MIP and $\sqrt{2}$ MIP signals (tilting the detector by 45 degrees).
+a threshold scan for the determination of the S/N in the trigger line. The later
+can be done by the comparison of threshold curves taken with incident MIP-acting particles
+and MIP-acting particles traversing the detector tilted by 45 degrees with respect to the beam direction.
 
@@
 showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{cob}.
-These new boards maximize the density of channels (4800 channels/dm$^{3}$) for the ECAL of the ILD
-and will allow to satisfy the requirement of having 30 active layers in 20 cm length
-for the barrel areas of the ECAL.
+These new boards maximize the density of channels (6000 channels/dm$^{3}$) for the ECAL of the ILD
+and will allow to satisfy the baseline requirements of the ECAL for the ILD.
 

### 2018-08-20 performance-paper-draft/longversion/draft.tex
All changes implemented. One last revision missing.

@@
   High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
-  of the final state of the particles produced in the collissions
+  of the final state of the particles produced in the collisions
   The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
@@
 linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
-This project will provide collisions of polarized beams with centre-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
+This project will provide collisions of polarized beams with center-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
 These collisions will be studied by two multipurpose detectors:
@@
 in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD.
-The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs.
+The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs, where the MIP acronym stands 
+for the energy deposited by a minimum-inonizing-particle.
 To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
-foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive in spills
+foreseen for the ILC: the $e^{+}e^{-}$ bunches trains will arrive in spills
 of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. The data acquisition will be gated during these short windows and during the idle time the bias currents of the electronics will be shut down.
@@
 in particle physics to simulate the passage of particles through matter. In this section we described in detail
-the main features and characteristics of the technollogical prototype.
+the main features and characteristics of the technological prototype.
 
@@
 With the first versions
-of the technollogical prototype we reached similar potential density level as in
+of the technological prototype we reached similar potential density level as in
 the current version but equipping only a
@@
 
-A photograph showing the SiW-ECAL technollogical prototype setup can be seen in Figure \ref{proto}.
-Current prototype consists on 7 layers of SLABs housed by a PVC and aluminum structure that can hold up to 10, in slots separated by 15mm each.
-The first six layers were placed in the first six slots and the last one was in the last slot. In the following sections, we will refer to layers number 1 to 7, where
+A picture showing the SiW-ECAL technological prototype setup can be seen in Figure \ref{proto}.
+The current prototype consists on 7 layers of SLABs housed in a PVC and aluminum structure that can host up to 10 layers in slots separated by 15mm each.
+The first six layers were placed in the first six slots and the last one was in the last slot, with respect to the beam. In the following sections, we will refer to layers number 1 to 7, where
 the 1 is the closest to the beam pipe and 7 is the farthest.
@@
 \begin{itemize}
-  \item their short gating windows for the acqusition (1-2ms)
+  \item their short gating windows for the acquisition (1-2ms)
    at low repetition frequencies (1-5 Hz) to minimize the chances of having real events due to cosmic rays during the data taking and the coherent noise events due to grounding issues;
- \item and the relatively high trigger threshold values between 400 and 250 DAC 
-(which are equivalent to $\sim$2 and $\sim$0.5 MIP respectively, see Section \ref{sec:comm_trigger} for more information).
+ \item and the relatively high trigger threshold values, between 2 and 0.5 MIPs.
 \end{itemize}
@@
 We found to different types of noisy channels. One set consists of
-channels randomy distributed along the surface of every ASU and the oter consists
-of channels systematically noisy in all the ASUs. Preliminary inspections of the PCB layout
-hint that the channels in the latter set are noisy due to
+channels randomly distributed along the surface of every ASU and the other consists
+of channels located in specific areas and systematically noisy in all the ASUs. Preliminary inspections of the PCB layout
+hint that the channels in the latter set may be noisy due to
 improvable routing of the PCB.
@@
 All the noisy channels have been identified and masked and the power
-of their preamplifiers has beem disabled. All the results shown in the following
+of their preamplifiers has been disabled. All the results shown in the following
 sections are obtained in these conditions.
@@
 we scan trigger thresholds and progressively mask channels that exhibit counts. 
-In each step, the decission of tagging a channel as noisy was taking following the next rules:
+In each step, the decision of tagging a channel as noisy was taking following the next rules:
 
@@
 \caption{Fraction of channels that are tagged as noisy in all slabs. 
-Top: inventory of the different type of noisy channels per slab. 
+Top: different type of noisy channels per slab. 
 Bottom: break down of the total number of noisy channels per ASIC. 
@@
 scan run are taken, and the results are shown in threshold scan curves where the
-x-axis represents the threshold value\footnote{The threshold values are given in internal DAC units which are translated to
-meaningful physical quantities in Section \ref{sec:comm_trigger_sn}.} and the y-axis
-the number of recorded signals normalized to 1.
+x-axis represents the threshold value and the y-axis
+the number of recorded signals normalized to 1. The threshold values are given in internal DAC units
+which are translated to meaningful physical quantities in Section \ref{sec:comm_trigger_sn}.
 In the absence of external signals (cosmic rays, injected signals, etc) 
@@
 where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
-the 50\% of its maximum and $p_{2}$ give us the width of the ThS curve.
+the 50\% of its maximum and $p_{2}$ give us the width of the threshold scan curve.
 
@@
 \begin{equation}
-DAC_{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
+Threshold{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
 \end{equation}
@@
 if at least the the 30\% of the 64 channels in the ASIC could be fitted.
-If not, a global DAC value of 250 was set.
+If not, a global threshold value of 250 was set.
 
@@
   \begin{tabular}{l}
-	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch.eps} \\
+	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch_DAC.eps} \\
 	\end{tabular}
@@
 without any loss of performance, at least in the laboratory and using 3 of the 7 SLABs.
-This new procedure will alo be applied in the next beam test.
+This new procedure will also be applied in the next beam test.
 Also, in order to
@@
 
-\section{Performance on positron beam test at DESY}
+\section{Performance in a beam test with positrons at DESY}
 \label{sec:beamtest}
 
-The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
-rates from few hundreds of Hz to few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
-The particles beam ies produced as follows: first, the electron/positron synchrotron DORIS II 
-is used to produced a photon beam via bremsstralhung when interacting with a carbon fiber target;
-secondly, these photons are then converted to electron/positron pairs; 
-and, finally, the beam energy is selected with dipole magnets and collimators. 
-In addition, DESY gives acces to a bore 1 T solenoid, the PCMag.
+The beam line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
+rates from a few hundreds of Hz to a few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
+In addition, DESY gives access to a bore 1 T solenoid, the PCMag.
 
@@
 \begin{enumerate}
-\item Calibration without tungsten absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs) directed to 81 position equally distributed over the modules.
+\item Calibration without tungsten absorber using 3 GeV positrons acting MIPs directed to 81 position equally distributed over the modules.
 \item Test in magnetic field up to 1 T using the PCMag. For this test a special PVC structure was
@@
 First reports on this beam test can be find in
-Refs. \cite{Irles:2018uum,Irles:2018hcd}. In this paper we discuss in more detail
-the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
+Refs. \cite{Irles:2018uum,Irles:2018hcd}. These results have extended and
+are discussed in the following sections. In Section \ref{sec:calib} we discuss in detail
+the results of the pedestal, noise and MIP calibration.
 We show also results on the pedestal and noise stability when running inside
-a magnetic field in Section \ref{sec:magnet}. Finally, a first peek to the 
-response and stability of the detector in electromagnetic showers events is discussed in 
-Section \ref{sec:showers}.
+a magnetic field in Section \ref{sec:magnetic} and in electromagnetic shower
+events in Section \ref{sec:showers}. The study of the calibration of the prototype
+in electromagnetic shower events is due to a future publication.
 
-\subsection{Response to MIP-acting positrons}
+\subsection{Noise studies and MIP calibration}
 \label{sec:calib}
 
-The calibration runs have been used to calculate the pedestal distribution reference values 
-and the noise levels (the width of the pedestal distrution) of each channel.
 In Figure \ref{signal_pedestal} we show the signal and pedestal distribution of a single channel after
-subtracting the pedestal mean position. The results of the MIP calibration fit are shown in red (see Section \ref{sec:mip} for more details)
-The pedestal distribution is shown only for the first SCA to keep the y-axis within a reasonable range.
+subtracting the pedestal mean position. The results of the MIP calibration fit are shown in red.
 The signal distribution is integrated over all SCAs.
+For cosmetic reasons the pedestal distribution is shown only for the first SCA.
 
-\subsubsection{Pedestal and noise determination}
-\label{sec:pedestal}
+%\subsubsection{Pedestal and noise determination}
+%\label{sec:pedestal}
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
   \centering
@@
 The pedestal is calculated as the mean position of
-the ADC distribution of channels without trigger. The noise is
-associated to the width of such distribution.
-The pedestal correction is done layer-, chip-, channel- and SCA-wisely due to the large spread of values between pedestals, as observed in 
+the distribution of the ADC values for all channels without trigger. The noise is
+associated to the width of the distribution.
+The pedestal correction is done layer-, chip-, channel- and SCA-wise due to the large spread of values between pedestals, as observed in 
 Figure \ref{pedestal_layer} (left plot) and Figure \ref{pedestal_all} (also left plot).
@@
 From now on, the pedestal correction is applied to all the results presented.
-
-%\begin{figure}[!t]
-%  \centering
-%  \begin{tabular}{ll}
-%    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2_chip4_cell10.eps} & \includegraphics[width=2.8in]{../figs/pedestal/ped_width_layer2_chip4_cell10.eps}
-%  \end{tabular}
-%  \caption{Pedestal mean position (left) and width (right) for one channel in the second layer.}
-%\label{pedestal_channel}
-%\end{figure}
+The resulting spectra are fit by
+a Landau function convoluted with a Gaussian.
+The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
+conversion from ADC units to energy in MIP units.
+The fit succeeded in 98\% of the cases and the spread of the resulting MPV is 5\%.
+The remaining channels will be discarded. Results are summarized in figure \ref{mipandSN}, leftmost plot.
 
@@
   \end{tabular}
-  \caption{Pedestal mean position (upper plot) and width (lower plot) for all channels in one layer. The data is grouped on bunches in which the value in the x-axis
-    corresponds to the value of the channel number plus the value of the ASIC number multiplied by 100. The black points show the value for the first SCA
-    and the red points show the average value for all the others SCAs (with the standard deviation of the sample as error bar).}
+  \caption{Pedestal mean position (left plot) and width (right plot) for all channels in one layer.}
 \label{pedestal_layer}
@@
 
-\subsubsection{Energy calibration and tracking efficiency}
-\label{sec:mip}
-
-After the pedestals are calculated and subtracted to the hit distributions, those are fit by
-a Landau function convoluted with a Gaussian.
-The most-probable-value of the convoluted function is taken as the MIP value, allowing thus for a direct
-conversion from ADC units to energy in MIP units.
-We have obtained a raw energy calibration spread of the 5\% among all channels with the 98\% of all 
-available channels being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.
-
 \begin{figure}[!t]
@@
 
-We checked the MIP 
-calibration in all callibrated channels by selecting tracks
-incident perpendicullary to the layers surface.
-The results are shown in figure \ref{mip3peaks} where the single channel energy 
-distribution for MIPs is shown for all calibrated channels in the same distribution. 
+As a sumamry Figure \ref{mip3peaks} shows the response of all channels integrated over the calibration run.
+This plot is obtained after further refinement of the sample by selecting incident tracks.
 The maximum peaks at 1 MIP as expected after a good calibration.
-In addition to this, a second and a third peak
-appear visible. These peaks are due to
+In addition to this, a second and a third peaks
+are visible as shoulders. These shoulder are associated to 
 events involving multiple 
@@
     \end{tabular}
-    \caption{Energy distribution for all callibrated channels when selecting tracks of 3 GeV positron acting as MIPs.}
+    \caption{Energy distribution for all calibrated channels when selecting incident tracks of 3 GeV positron acting as MIPs.}
 \label{mip3peaks}
@@
 tracks with at least 4 layers with a hit in exactly the same channel. Afterwards we 
-check if the other layers have or not a hit in the same channel (expanding the search
-to the closest neighbouring channels) with energy larger or equal than 0.3 MIP.
-Finally, we repeat this for all layers 
-and channels. The results are shown in Figure \ref{efficiency}. Except few exceptions, the efficiency is 
+check which layers have or not a hit in the same or in the closest neighboring channels with energy larger or equal than 0.3 MIP.
+We repeat this procedure for all channels.
+The results are shown in Figure \ref{efficiency}. Except few exceptions, the efficiency is 
 compatible with $100\%$.
 Lower efficiencies in the first layer are related to the presence of
-noisy channels not spotted during the commissioning. In the last layer (separated from the
-other layers by four slots of 1.5 cm instead of only one) we also observe few small deviations
-from the $\sim100\%$ which are indeed
-associated to a slight misalignment of the detector.
-If we remove these channels from the analysis
-the full efficiency is recovered.
+noisy channels not spotted during the commissioning. In the last layer we also observe few small deviations
+which are associated to the outliers channels, hinting for a small misalignment of the last layer.
 
@@
   \centering 
-    \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips.eps} & \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
-    \end{tabular}
-    \caption{Left: MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.
-Right: same figures with a zoom in the y-axis.
-In both cases, the average efficiency of the 64 channels in each ASIC is shown.}
+   % \begin{tabular}{ll}
+  \includegraphics[width=4in]{../figs/MIP/efficiency_nhits4_chips.eps}
+  %& \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
+  %  \end{tabular}
+  \caption{MIP detection efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.}
 \label{efficiency}
@@
 the Landau-gauss function fit to the data (pedestal subtracted) and the noise (the pedestal width). This quantity 
-has been calculated for all channels and all layers. The average S/N is to 20.4.
+has been calculated for all channels and all layers. 
 Results are summarized in Figure \ref{mipandSN}, rightmost plot.
@@
 
-The data taking inside the magnetic field has been divided in three steps:
-a) a with a magnetic field of 1 T; b) a run with 0.5 T; c) a final run with the magnet off.
-The beam, 3 GeV positrons, was hitting in the area of the PCB readout by the ASIC number 12.
+The data taking inside the magnetic field has been divided in three runs:
+\begin{enumerate}
+\item a with a magnetic field of 1 T;
+\item a run with 0.5 T;
+\item and a final run with the magnet off.
+\end{enumerate}
 
+The beam, 3 GeV positrons, was directed in the area of the PCB readout by the ASIC number 12.
 The pedestal positions and noise levels of the channels of the ASIC 12 when the
@@
 This is shown in Figure \ref{pedestal_magnetic}.
-We see that the agreement is perfect within the statistical uncertainties.
+We see that the agreement is perfectly good within the statistical uncertainties.
 Due to the lower rates in this beam area, the
@@
 using the W-configuration number 2 when shooting the beam in the area registered by the ASIC 12 (and partially in the 13). 
-Only information recorded by ASIC 12 is used in the analysis. For other configurations we get comparable results.
+For simplicity, only information recorded by ASIC 12 will be shown. 
 In order to select a high purity of
@@
 
-\begin{figure}[!t]
+\begin{figure}[!ht]
   \centering 
@@
       Right: same but as a function of the number of hits. In both cases, the results are shown for few SCA.
-      The points for the curves with SCA larger than zero are slightly shifted in the x-axis to optimize the visualization.}
+      The points for the curves with SCA different than zero are slightly shifted in the x-axis to optimize the visualization.}
 \label{pedestal_shower_1}
@@
 drift of the pedestal values
-towards lower values when the collected energy is high (or when the number of triggered channels is large).
-%For events with 80 MIPs collected in the ASIC, we have an average drift of the pedestal of $\sim$ 0.05 MIP. 
-This is shown in Figure \ref{pedestal_shower_1} for several SCAs where the
-average of the projection of the pedestal distribution for all channels non triggered in ASIC 12 of layer 3 
-is plot as a function of the total energy measured by the ASIC (or the total number of hits).
-We see that in both cases, the shapes of the curves 
-for each SCA are very similar.
+towards lower values when the collected energy is high {\it i.e.} when the number of triggered channels is large.
+This is shown in Figure \ref{pedestal_shower_1} for several SCAs.
+A small dependence, in all SCAs, of the pedestal position on the amount of charge collected by the
+ASIC is observed.
 This feature is known and it is due to the architecture of the SKIROC2 ASICs 
 where high inrush of currents can slightly shift the baseline of the analogue power supply. 
-%This feature is foreseen to be removed from the SKIROC3 ASICs.
-
 The second observation extracted from this analysis can be also seen in Figure \ref{pedestal_shower_1} but
@@
     \end{tabular}
-    \caption{Left: average value on each SCA of the calculated pedestals for all channels of ASIC 12 in the Layer 3 for different energies of the beam.
-Right: same but fixing the energy of the beam and comparing several layers.}
+    \caption{Average value over all channels in ASIC 12 of the pedestals position for each SCA in electromagnetic shower events.}
 \label{pedestal_shower_2}
@@
 the performance of the detector and to perform
-a channel by channel calibration, showing a good homogenity with a spread of the 5\% for all channels.
-The signal over noise of the detector has been evaluated to be 12.8 for the trigger
-decission and 20.4 for the charge measurement using, in both cases, MIP signals as reference.
+a channel by channel calibration, showing a good homogeneity with a spread of the 5\% for all channels.
+The signal over noise, S/N, of the detector has been evaluated to be $12.9\pm3.4$ for the trigger
+decission and $20.4\pm1.5$ for the charge measurement.
 
@@
 In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
-In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operaton, {\it i.e.} full zero suppression, reduced power consumption etc.
+In contrast with SKIROC2/2a, the new ASIC will be fully optimized for ILC operation, {\it i.e.} full zero suppression, reduced power consumption etc.
 
@@
 This device constitutes a technological challenge in both aspects, the mechanical
-(very thin and long structure with fragile sensors in the bottom, complicated assembly procedure...)
-and the electrical (i.e. transmission of signals and high currents).
+(very thin and long structure with fragile sensors in the bottom make complicated the assembly procedure and the handling...)
+and the electrical (we need to ensure and control the transmission of signals and high currents along the full device).
 For example, interconnections between ASUs and between ASU and interface card are one of
@@
 and require close collaboration between mechanical and electronic engineers.
-The construction and test of a long SLAB prototype
-of $\sim8$ ASUs is currently ongoing.
-%Therefore, many efforts are focused in the construction and test of such long 
-%layers made of chains of ASUs (up to $\sim$15 ASU) 
-%as well as in the standardization of the interconnections.
+A first long SLAB prototype
+of $\sim8$ ASUs has been already tested in beam test also in DESY in 2018.
 
@@
 Finally, intensive R\&D on the compactification of
-the DAQ towards meeting the ILD tight space requirements is being done by the SiW-ECAL collaboration.
+the DAQ to meet the tight space requirements for the ILD is being done by the SiW-ECAL collaboration.
 
@@
 and tagged during the data acquisition and removed afterwards from the analysis
-not introducing any significance loss of performance as can be seen, for example, in the hit detection efficiency plots (see Section \ref{sec:mip}).
+not introducing any significance loss of performance as can be seen, for example,
+in the hit detection efficiency plots (see Section \ref{sec:calib}).
 In the following, we briefly describe the status of the monitoring, debugging and filtering
@@
 This effect creates around 17\% of empty events which are easily filter and removed from the
-analysis. The ratio of empty triggers in the new SKIROC2a has been reduced to the $\sim2-3\%$.
+analysis. The ratio of empty triggers in the new SKIROC2a has been reduced to the $\sim2-3\%$
+by reducing the length of the OR64 signal.
 
@@
 and also produce the so called plane events (most of the channels trigered at once).
-In previous studies ({\it i.e.} reference \cite{Amjad:2014tha}), the ratio of retriggers and plane events
-was reduced by improving the power supply stabilization capacitances. It is important to remark that
-all layers and all ASICs analog and digital levels are powered using the same power supply.
-Moreover, the high voltage power supply for the polarization of the PIN diode is also common for all layers
-and the grounding levels of the low and high voltages supplied are shared within the slab.
-Therefore any noise in
-these power supplies or any overload of an ASIC may participate in the creation of fake signals
-in different ASICs and layers.
+In previous studies the ratio of retriggers and plane events
+was reduced by improving the power supply stabilization capacitances. %It is important to remark that
+%all layers and all ASICs analog and digital levels are powered using the same power supply.
+%Moreover, the high voltage power supply for the polarization of the PIN diode is also common for all layers
+%and the grounding levels of the low and high voltages supplied are shared within the slab.
+%Therefore any noise in
+%these power supplies or any overload of an ASIC may participate in the creation of fake signals
+%in different ASICs and layers.
 
@@
 ASICs far from the beam spot is higher than in the ASICs that are reading
-out the information of real hits. Even more, this concentration is even higher near the channels
-37 and the channels masked as suspicious of suffering from routing issues.
+out the information of real hits. We have also observed that the concentration of these events
+is higher in the nearby of channels that were masked as suspicious of suffering from routing issues.
 The ratio these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
@@
 the signal that informs the DIF that one ASIC memory is full is transmitted through the PCB.
-
-We should point out that these events are easilly filtered out during the analysis (or even during the online monitoring)
-and that no impact is observed
-in the data, {\it i.e.} in the MIP detection efficiency.
 

### 2018-08-20 performance-paper-draft/longversion/draft.tex
Ready to circulate. Only the author list is missing

@@
   of the final state of the particles produced in the collisions
-  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
+  Thia precission will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
   The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
   design and R\&D is oriented at the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
-  In this article we present the commissioning and the performance of the prototype in our beam test carried at DESY in June 2017.
+  In this article we present the commissioning and the performance of the prototype in a beam test carried at DESY in June 2017.
 }
@@
 linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
-This project will provide collisions of polarized beams with center-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
+This project will provide collisions of polarized beams with center-of-mass energies of 250 GeV - 1 TeV.
 These collisions will be studied by two multipurpose detectors:
@@
 silicon wafers with a thickness of 320$\mu$m.
-The size of the wafers is $9\times9$ cm$^{2}$ and they are each subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
+The size of the wafers is $9\times9$ cm$^{2}$ and each of them is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
 A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
 for particles incident perpendicularly to its surface.
-
 The original design of the silicon wafers included an edge termination made of floating guard-rings.
@@
 can be reduced to be at negligible level.
-
 For the setup described this article we used different solutions for the edge terminations.
-For all of them, the levels of fake events are at negligible level due to
-the low energy of the beam used to test the prototype. Therefore, they are not further described here.
+For all of them, the expected levels of fake events are negligible due to
+the low energy of the interactions studied in this paper:
+MIP like particles or electromagnetic showers created by particles of few GeV
+from the DESY beam. Therefore, they are not further discussed here.
 
@@
 very front end ASIC (application-specific integrated circuits)
-designed for the readout of the Silicon PIN didoes.
+designed for the readout of silicon PIN diodes.
 In its version SKIROC2 it consists of 64 channels in AMS 0.35 $\mu$m SiGe technology.
@@
 Each channel comprises a low noise charge preamplifier of variable gain followed by two branches:
-a fast shaper for the trigger decision and a set of dual gain slow shaper for charge measurement. 
+a fast shaper for the trigger decision and a set of dual gain slow shapers for charge measurement. 
 The gain can be controlled by modifying the feedback capacitance during the configuration of the detector.
@@
 Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as
-triggered or not triggered and the information is stored in 15 cell deep physical switched capacitor array (SCA).
+triggered or not triggered and the information is stored in a 15 cell deep physical switched capacitor array (SCA).
 
@@
   \end{tabular}
-  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the Si-Sensors are in glued in the back.
+  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the PCB is in the top
+    and the sensors are in glued in the back.
     The channels are separated (in x and y) by 5.5 mm.
@@
 
-Current version of the PCB is called the FEV11. It has a thickness of 1.6mm and 2.7mm
-if we include on top the ASICs in its current packaging (1.1 mm thick LFBGA package).
+The current version of the PCB is called the FEV11. It has a thickness of 1.6mm which
+grows up to 2.7mm when the ASICs in its current packaging (1.1 mm thick LFBGA package) are
+bonded in top of it.
 With these characteristics, a potential density of
@@
 
-The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system consists of three components, enumerate from upstream to downstream from the data flow perspective:
+The subsequent chain of the data acquisition (DAQ)\cite{Gastaldi:2014vaa} system consists of three components.
+They are enumerated from upstream to downstream from the data flow perspective:
 
@@
   \item The most downstream component, is the clock and control card (CCC) which
-provides a clock, control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
+provides a clock, the control fan-out of up to 8 GDCCs and accepts and distributes external signals (i.e. signals
 generated external pulse generator to simulate the ILC spill conditions).
@@
 
-A full equipped readout module is shown in Fig. \ref{ASU2}. These modules are called
+A fully equipped readout module is shown in Fig. \ref{ASU2}. These modules are called
 SLABs and consist of a chain of one or several fully equipped ASUs
@@
 services as power connectors or the super capacitances used for the power pulsing. 
-These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance. 
-The capacitances are extra dimensioned to provide enough local storage 
+These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance
+are extra dimensioned to provide enough local storage 
 of power to assure stable low voltage levels during the power pulsing. %In this configuration
 %the high currents are still crossing the interconnections/
-The readout modules are embedded on a "U" shape carbon structure to protect the wafers.
+The readout modules are embedded on a "U" shaped carbon structure to protect the wafers.
 The full system is then covered by two aluminum plates
@@
 The current prototype consists on 7 layers of SLABs housed in a PVC and aluminum structure that can host up to 10 layers in slots separated by 15mm each.
-The first six layers were placed in the first six slots and the last one was in the last slot, with respect to the beam. In the following sections, we will refer to layers number 1 to 7, where
+The first six layers were placed in the first six slots and the last one was in the last slot,
+with respect to the beam pipe. In the following sections, we will refer to layers number 1 to 7, where
 the 1 is the closest to the beam pipe and 7 is the farthest.
@@
 
-This beam test was prepared by a commissioning phase comprising
-the debug of the
-short SLABSs with special emphasis in the control of the noise and the study of the
-prototype performance in cosmic ray tests.
-
 Earlier experiences with the SKIROC2 ASIC are reported in
@@
 \begin{enumerate}
-  \item identify the readout channels that are noisy in high trigger threshold above MIP signal conditions
+  \item identify the readout channels that are noisy in high trigger threshold above MIP signal conditions;
   \item and select the optimal trigger threshold levels.
@@
 data taking to short gating times.
-
-All runs dedicated to the commissioning were characterized by:
-\begin{itemize}
-  \item their short gating windows for the acquisition (1-2ms)
-   at low repetition frequencies (1-5 Hz) to minimize the chances of having real events due to cosmic rays during the data taking and the coherent noise events due to grounding issues;
- \item and the relatively high trigger threshold values, between 2 and 0.5 MIPs.
-\end{itemize}
+In any case, all runs dedicated to the commissioning are usually characterized by their short gating windows for the acquisition (1-2ms)
+at low repetition frequencies (1-5 Hz)
+to minimize the chances of having real events due to cosmic
+rays during the data taking.
 
@@
 
-We found to different types of noisy channels. One set consists of
+The list of the noisy channels was
+obtained by means of dedicated data taking runs. In these runs
+we scan relatively high trigger thresholds (between 1-3 MIPs) and progressively mask channels that exhibit counts. 
+In each step, the decision of tagging a channel as noisy was taking following the next rules:
+
+\begin{itemize}
+\item if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC it was added to the list;
+\item if a channel was tagged as noisy in, at least, three of the SLABs, it was tagged as noisy for all and added to the list of channels being suspect of suffer from routing issues.
+\end{itemize}
+
+Following this procedure, we found to different types of noisy channels. One set consists of
 channels randomly distributed along the surface of every ASU and the other consists
@@
 
-The list of the noisy channels was
-obtained by means of dedicated data taking runs. In these runs
-we scan trigger thresholds and progressively mask channels that exhibit counts. 
-In each step, the decision of tagging a channel as noisy was taking following the next rules:
-
-\begin{itemize}
-\item if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC it was added to the list;
-\item if a channel was tagged as noisy in, at least, three of the SLABs, it was tagged as noisy for all and added to the list of channels being suspect of suffer from routing issues.
-\end{itemize}
-
 In addition to the different noisy channel types described above, we also have
-masked full sectors of the SLABs if an ASIC was faulty (at least 70\% of channels 
+masked full sectors of the SLABs if an ASIC was tagged as faulty (at least 70\% of channels 
 listed as noisy) or if a Si-wafer was damaged (high leakage currents).
@@
 After the noisy channels have been masked, dedicated trigger threshold
-scan run are taken, and the results are shown in threshold scan curves where the
+scan runs are taken, and the results are shown in the threshold scan curves where the
 x-axis represents the threshold value and the y-axis
@@
 the 50\% of its maximum and $p_{2}$ give us the width of the threshold scan curve. 
-
 In Figure \ref{scurve_channels} 
 two threshold scans curves are shown together with the fit by
-the theoretical function for two different channels from the second
-layer of the setup are shown.
+the theoretical function.
 
@@
 These are represented by $<p_{1,2}^{ASIC}>$ in the following.
-The final threshold value of every ASIC, in DAC units, was chosen 
+The optimal threshold value of every ASIC, in DAC units, was chosen 
 using the following formula
 \begin{equation}
-Threshold{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
+DAC_{optimal}^{ASIC} =maximum(<p_{1}^{ASIC}> + 5 \times <p_{2}^{ASIC}>,230).
 \end{equation}
@@
 Performing threshold scan scurves using
-real signals allow to calculate the signal over noise (S/N) ratio to trigger.
+real signals allow to calculate the signal over noise (S/N) ratio.
 For that we compare the curves for 1 MIP and 2 MIP injected signals.
-The S/N is, therefore, defined as the ratio between the distance of both curves at its
+The S/N is, in the following, defined as the ratio between the distance of both curves at its
 50\% and the width of the curves.
@@
 \end{equation}
-for the trigger branch. The central value is calculated from the comparison of the blue and red curves
-in Figure \ref{SKIROC2} and using the width of the 1 MIP curve in the denominator. The estimated
+for the trigger branch. The central value is calculated from Figure \ref{SKIROC2} by
+the comparison of the 1 and 2 MIP curves and using the width of the 1 MIP curve in the denominator. The estimated
 uncertainty has two components: the difference of width between the 1 and 2 MIP curves of injected signals and the differences (width and middle point) between the 1 MIP curves for injected and
@@
 These sources are
-now well know and therefore a new ``noise commissioning procedure'' has been studied.
+now well know and therefore a new noise commissioning procedure has been studied.
 It will consist on an iterative algorithm that first
@@
 definition of the noise levels for each channel independently
-instead of relative to the total number of triggers recorded by
+instead of relatively to the total number of triggers recorded by
 the ASIC. Finally, once the noisy channels
@@
 The beam line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
-rates from a few hundreds of Hz to a few KHz with a maximum of $\sim 3$ KHz for 2-3 GeV. 
+rates from a few hundreds of Hz to a few kHz with a maximum of $\sim 3$ kHz for 2-3 GeV. 
 In addition, DESY gives access to a bore 1 T solenoid, the PCMag.
@@
 
-\subsection{Noise studies and MIP calibration}
+\subsection{Noise study and MIP calibration}
 \label{sec:calib}
@@
 
-As a sumamry Figure \ref{mip3peaks} shows the response of all channels integrated over the calibration run.
+The Figure \ref{mip3peaks} shows the response of all channels integrated over the calibration run.
 This plot is obtained after further refinement of the sample by selecting incident tracks.
@@
 In addition to this, a second and a third peaks
-are visible as shoulders. These shoulder are associated to 
+are visible as shoulders. These shoulders are associated to 
 events involving multiple 
@@
 compatible with $100\%$.
-Lower efficiencies in the first layer are related to the presence of
-noisy channels not spotted during the commissioning. In the last layer we also observe few small deviations
+The low efficiencies in the first layer are related to the presence of
+noisy channels not spotted during the commissioning. These channels
+may saturate de acquisition in their ASICs. In the last layer we also observe a few small deviations
 which are associated to the outliers channels, hinting for a small misalignment of the last layer.
@@
 
-\subsubsection{S/N ratio in the charge measurement for MIP interactions}
+\subsubsection{Power of signal separation for MIP-size signals}
 \label{sec:sn}
 
-The signal-over-noise ratio in the charge measurement (corresponding to the slow shaper of the SKIROC2) is defined 
+The power of signal separation for MIP size signals is defined 
 as the ratio between the most-probable-value of
@@
 Results are summarized in Figure \ref{mipandSN}, rightmost plot.
+It is important to remark that this definition corresponds to what
+has been called so far as the S/N of the SiW-ECAL (see for example Ref. \cite{Amjad:2014tha}).
+However, we think that it is more correct to define the S/N of the detector
+in the trigger decission line and use the power of signal separation concept
+for the the quantity described at the beginning of the paragraph.
 
@@
 a channel by channel calibration, showing a good homogeneity with a spread of the 5\% for all channels.
-The signal over noise, S/N, of the detector has been evaluated to be $12.9\pm3.4$ for the trigger
-decission and $20.4\pm1.5$ for the charge measurement.
+The signal over noise, S/N, of the detector has been evaluated to be $12.9\pm3.4$.
+The power of signal separation for signals of 1 MIP is $20.4\pm1.5$.
 
@@
 One of these efforts is directed to the design and test of new ASICs.
-In fact, a new generation of SKIROC2, the 2a, has been delivered
-and it is being tested in the dedicated testboards and it has been integrated in new ASUs.
+In fact, a new generation of the SKIROC, the 2a, has been delivered, tested in the dedicated testboards
+and it has been integrated in new ASUs.
 In addition, a new generation of the ASIC, SKIROC3, is foreseen for the final detector construction.
@@
 A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
-with a total thickness of 1.2 mm (to be compared with the 2.7 of the LFBGA solution)
+with a total thickness of 1.2 mm (to be compared with the 2.7 of the LFBGA solution in the FEV11)
 has been produced and tested in the laboratory
@@
 The ratio these events have been estimated to be of $1-3\%$ in the ASICs where high frequency
-interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 KHz) and at higher rates even larger than $40\%$ in other 
+interactions are produced ({\it i.e.} using 3 GeV positrons ate 2-3 kHz) and at higher rates even larger than $40\%$ in other 
 ASICs far from the beam spot. 

### 2019-04-04 performance-paper-draft/NIMsub_arxiv1902.00110/v0/draft.tex
Up to date to the arxiv submissions

%\documentclass[a4paper,11pt]{article}
\documentclass[final,3p,times,twocolumn]{elsarticle}
%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

%\usepackage{elsarticle} % for details on the use of the package, please
                     % see the JINST-author-manual

\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{lineno}
\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{{#1}}}
\usepackage[outdir=./]{epstopdf}
\usepackage{upgreek}
\usepackage{amsmath}
%\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}

% e-mail addresses: only for the forresponding author
%\ead{irles@lal.in2p3.fr}
%\collaboration[]{on behalf of the CALICE collaboration}

\begin{document}

\begin{frontmatter}
  \title{Beam test performance of the highly granular SiW-ECAL technological prototype for the ILC.}

  % \ead{irles@lal.in2p3.fr}

  \author[kyushu]{K.\,Kawagoe}
  \author[kyushu]{Y.\,Miura}
  \author[kyushu]{I.\,Sekiya}
  \author[kyushu]{T.\,Suehara}
  \author[kyushu]{T.\,Yoshioka}

  \author[lal]{S.\,Bilokin\corref{cor_iphc}}
  \author[lal]{J.\,Bonis}
  \author[lal]{P.\,Cornebise}
  \author[lal]{A.\,Gallas}
  \author[lal]{\underline{A.\,Irles}\corref{cor1}}
  \ead{irles@lal.in2p3.fr}
  \author[lal]{R.\,P\"oschl}
  \author[lal]{F.\,Richard}
  \author[lal]{A.\,Thiebault}
  \author[lal]{D.\,Zerwas}

  \author[llr]{M.\,Anduze}
  \author[llr]{V.\,Balagura}
  \author[llr]{V.\,Boudry}
  \author[llr]{J-C.\,Brient}
  \author[llr]{E.\,Edy}
  \author[llr]{G.\,Fayolle}
  \author[llr]{M.\,Frotin}
  \author[llr]{F.\,Gastaldi}
  \author[llr]{R.\,Guillaumat}
  \author[llr]{A.\,Lobanov}
  \author[llr]{M.\,Louzir}
  \author[llr]{F.\,Magniette}
  \author[llr]{J.\,Nanni}
  \author[llr]{M.\,Rubio-Roy\corref{cor_iphc}}
  \author[llr]{K.\,Shpak}
  \author[llr]{H.\,Videau}
  \author[llr,ihep]{D.\,Yu}

  \author[omega]{S.\,Callier}
  \author[omega]{F.\,Dulucq}
  \author[omega]{Ch.\,de la Taille}
  \author[omega]{N.\,Seguin-Moreau}

  \author[lpnhe]{J.E.\,Augustin}
  \author[lpnhe]{R.\,Cornat}
  \author[lpnhe]{J.\,David}
  \author[lpnhe]{P.\,Ghislain}
  \author[lpnhe]{D.\,Lacour}
  \author[lpnhe]{L.\,Lavergne\corref{cor_iphc}}
  \author[lpnhe]{J.M.\, Parraud}

  \author[skku]{J.\,S.\,Chai}

  \author[kek]{D.\,Jeans}

  %%%%
  \address[kyushu]{Department of Physics and Research Center for Advanced Particle Physics, 
      Kyushu University, 744 Motooka, Nishi-ku, Fukuoka 819-0395, Japan }

  \address[lal]{Laboratoire de l'Acc\'elerateur Lin\'eaire (LAL), CNRS/IN2P3 et
      Universit\'e de Paris-Sud XI, Centre Scientifique d'Orsay B\^atiment 200, BP 34, F-91898 Orsay 
    CEDEX, France}

  \address[llr]{Laboratoire Leprince-Ringuet (LLR)
    -- \'{E}cole polytechnique, CNRS/IN2P3, F-91128 Palaiseau Cedex, France }
  \address[ihep]{Institute of High Energy Physics of Beijing (IHEP), 19 Yuquan Rd, Shijingshan Qu, Beijing Shi, China}

  \address[omega]{Laboratoire OMEGA -- \'{E}cole polytechnique-CNRS/IN2P3, F-91128 Palaiseau Cedex, France}

  \address[lpnhe]{Laboratoire de Physique Nucl\'eaire et de Hautes Energies 
    (LPNHE), Universit\'e Sorbonne, UPD, CNRS/IN2P3, 4 Place Jussieu, 75005 Paris, France }

  \address[skku]{Department of Electrical and Computer Engineering, Sungkyunkwan Universtity, 16419, Suwon, Gyeonggi-do, Korea}
  \address[kek]{Institute of Particle and Nuclear Studies, KEK, 1-1 Oho, Tsukuba, Ibaraki 305-0801, Japan }

  \cortext[cor_iphc]{S.\,Bilokin is now at IPHC CNRS/IN2P3 from Strasbourg (France);  M.\,Rubio-Roy is now at SPINTEC CNRS from Grenoble (France); and L.\,Lavergne is now at IRAP from Toulouse (France)}
  \cortext[cor1]{Corresponding author}

\begin{keyword}
  Calorimeter methods, calorimeters, Si and pad detectors
\end{keyword}

%\maketitle
%\flushbottom

\begin{abstract}
The technological  prototype of the CALICE highly granular silicon-tungsten electromagnetic 
calorimeter (SiW-ECAL) tested in beam at DESY in 2017. 
In this test the setup comprised seven layers of 1024 channels and a size of $18\times18$ cm$^2$ each.
This article presents key performance results in terms of signal over noise ratios at different levels of the readout chain 
and a study of the uniformity of the detector response.   
\end{abstract}

\end{frontmatter}

\linenumbers

\section{Introduction}

The International Linear Collider, ILC \cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya},
is a next generation of $e^{+}e^{-}$
linear colliders project. It will
provide collisions of polarized beams with center-of-mass energies between 250 GeV and 1 TeV.
These collisions will be studied by multipurpose detectors.
The two proposed projects~\cite{Behnke:2013lya} --  the International
Large Detector (ILD) and the Silicon Detector
(SiD) -- are designed for the use of Particle Flow (PF) technique  \cite{Brient:2002gh,Morgunov:2004ed}, for the
reconstruction of the final state particles.
The PF techniques rely on single particle separation
to allow for the selection of the best information available
in the full detector to determine the final states of the collisions.
They allow reducing the impact of the poor resolution of the calorimeter systems
(compared with trackers) in the overall reconstruction
but require detectors with highly granular, compact
and hermetic calorimetric systems. Furthermore, the PF capabilities are enhanced when the calorimeters
are placed inside a large magnetic field that favors the separation of charged particles. 
This in turn calls for a compact design of the calorimeters.
Most of the R\&D efforts of such calorimeters 
for future linear colliders are carried out by the CALICE collaboration.

This document reports on the performance 
in beam test of the technological prototype of the silicon-tungsten electromagnetic calorimeter,
the SiW-ECAL.
The SiW-ECAL is the baseline choice for the ILD ECAL. It will be placed, together with the hadronic calorimeter
of the ILD, inside a magnetic field of at least 3T.
Silicon constitutes the active and tungsten the passive material of the detector. 
The overall thickness is 24 radiation
lengths ($X_{0}$) or about 1 interaction length.
The choice of silicon and tungsten makes possible the design
of a very compact calorimeter with high granularity in 3 dimensions. The baseline design
for the ILD foresees 26-30 layers in the barrel region enclosed in about 23 cm thick structures.
The active sensors will be segmented in squared cells of $5\times5$ mm$^2$,
for a total of $\sim$80 million readout channels for the barrel region of the ECAL of the ILD.
The dynamic range in each channel will range from 0.5 to 3000 MIPs, where the MIP acronym stands 
for both the most probable value of the energy deposited by a minimum-ionizing-particle and the particle itself.
In order to minimize external services and maximize the hermeticity, the very-front-end (VFE) electronics
must be embedded in the calorimeter modules and be cooled only passively.
In turn, to reduce overall power consumption, the SiW-ECAL will exploit the particular bunch structure
foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive within
time windows of $\sim$1-2 ms width separated by $\sim200$ ms.
The data acquisition will be gated during these 1-2 ms and
the bias currents of the electronics will be shut down to save power during the idle time.
This technique is usually denominated as power pulsing. Finally,
the calorimeters will operate in self-trigger mode (each channel featuring a discriminator for internal trigger decision) and on-chip zero suppression mode.

\section{The SiW-ECAL technological prototype}

The first SiW-ECAL prototype was the so-called SiW-ECAL physics prototype \cite{Anduze:2008hq}.
It was extensively tested at DESY, FNAL and CERN~\cite{Adloff:2011ha,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
The VFE was placed outside the active area with no particular constraints on power consumption.
It consisted of 30 layers of silicon sensors alternated with tungsten plates 
yielding a total of 24 $X_{0}$.
The active layers were made of a matrix of $3\times3$ silicon sensors of 500 $\upmu$m thickness. Each of these sensors was segmented in matrices of
$6\times6$ squared pixels of $10\times10$ mm$^2$.

The new generation prototype dubbed the SiW-ECAL technological prototype addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector.

\begin{figure*}[!ht]
\centering
\begin{tabular}{l}
  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
  \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
\end{tabular}
\caption{Top: prototype with 7 layers inside the mechanical housing. Bottom: schematic view of the readout modules
  including the surface repartition readout by each ASIC, numbered from 0 to 15. Notice that the adapter board and DAQ-detector interface drawings are not at scale.}
\label{proto}
\end{figure*}

A picture showing the SiW-ECAL technological prototype setup tested at DESY (Hamburg) in summer
2017 can be seen in Figure \ref{proto}.
The setup consists of 7 layers housed in a PVC and aluminum structure that can host up to 10 layers
in slots with a $15-$mm pitch. The first six layers were placed in the first six slots
and the 7th in the last one.
From now on, the layers will be referenced by their numbers from 1 to 7.
The detector was commissioned in the laboratory
and afterwards exposed to a low energy positron beam in the DESY test beam area (line 24) \cite{Diener:2018qap} the first layer located at the most upstream on the beam.
All results presented here are obtained with the detector running in power pulsing mode
and with gated acquisitions of $1-3$ ms at frequencies of 1-5 Hz.

Each layer consists of a readout module
on top of a carbon cradle that protects the sensors
and the sides of the module. The readout module is further wrapped by two aluminum plates
that provide electromagnetic shielding and mechanical stability.
The readout module itself consists of an Active Signal Unit (ASU) and an adapter board
to a data acquisition system (DAQ)\cite{Gastaldi:2014vaa,Rubio-Roy:2017ere,Magniette:2018wdz} at the beginning of the module.
In the picture, the ASU is covered 
by an aluminum plate marked by the red number 1.
The ASU consist of a $18\times18$ cm$^2$ sized printed circuit board, PCB,
equipped with 16 VFE ASICs and 4 silicon sensors glued onto the other side.
The PCB features 1024 square pads of $5.5\times5.5$ mm$^2$ that are readout by the ASICs.
Part of the adapter board is also covered by the aluminum plate and the uncovered part 
is seen over the red number 2 in the picture. 
The adapter board also holds other
services e.g. the super capacitance used for the power pulsing. 
This decoupling capacitor of 400 mF with 16 m$\Omega$ of equivalent serial resistance
provides enough local storage 
of power to assure stable low voltage supply during the power pulsing. This capacitor
is seen just above the red number 2.
The first component
of the DAQ system, the detector interface board described in \cite{Gastaldi:2014vaa}, is identified in the picture by a red
number 3.
For simplicity, the rest of the DAQ system is not shown.

The VFE ASICs are 16 SKIROC2 \cite{Callier:2011zz,Amjad:2014tha,Suehara:2018mqk}
(Silicon pin Kalorimeter Integrated ReadOut Chip), 
that have been designed for the readout of silicon PIN diodes.
The SKIROC2 in LFBGA package are bump bonded to the PCB.
The version of the ASUs tested in this beam test has a thickness
of 2.8 mm including the ASICs in its current packaging.
Each of these SKIROC2 comprises 64 readout channels
made of a variable-gain preamplifier followed by two branches:
a fast line for the self-trigger decision and a slow line for dual-gain charge measurement.
The gain on the preamplifier is set by changing the feedback capacitor, $C_{f}$.
The fast line consists of a high gain variable CRRC shaper followed by
a low offset discriminator to make the trigger decision.
A common 10-bit DAC provides the threshold of the discriminator.
The slow line is made of a low gain and a high gain CRRC
shapers to handle a large dynamic range.
When a channel triggers, a track and hold cell is used to record the signal at its peaking time
in the dual gain line. The levels of all the others
channels are then also recorded.
% A bandgap ensures the stability with
%respect to supply voltage and temperature for all the requested
%references in the analogue core.
The triggers are timestamped within each gated acquisition with a slow clock
of 5 MHz. The timestamp numbers are called brunch crossing identifiers (BCID).
The charges are stored in the buffers of a switched capacitor array, SCA, and later converted by a 12-bit Wilkinson ADC.
The ASIC consumes, in the power pulsing conditions as foreseen for the ILC, 
27 $\upmu$W per channel.

The four sensors consist of $90\times90$ mm$^{2}$ silicon sensors of
320$\pm15\,\upmu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
Each sensor is subdivided in an array of 256 PIN diodes of $5.5\times5.5$ mm$^2$
connected each to the PCB pads by a dot of conductive glue.
The high voltage to deplete the sensors is delivered to the sensors via a
100 $\upmu$m copper foil isolated from the rest of the setup by a kapton sheet.
It has been estimated that
a MIP traversing the PIN perpendicular to its surface produces, in average,
a signal of 4 fC.

\section{Performance at positron beam test at DESY}
\label{sec:beamtest}

The beam line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates from a few hundreds of Hz to a few kHz with a maximum of $\sim 3$ kHz for 2-3 GeV. 
In addition, DESY gives access to a bore 1 T solenoid.

The physics program of the beam test can be summarized as follows:

\begin{enumerate}
\item Calibration without tungsten absorber using 3 GeV positrons interacting, in the first approach, as MIPs.
  The beam was normally directed to 81 positions equally distributed over the modules surface.
\item Test in a magnetic field up to 1 T using, also without tungsten and with 3 GeV positrons. For this test, a PVC structure was
designed and produced to support one single readout module.	
%The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
%readout module itself are able
%to handle strong magnetic fields; 
%second to check the quality of the data and the performance of the detector during the data taking when running
%in a magnetic field.
\item Response to electrons of different energies with a fully equipped detector, {\it i.e}\@. sensitive parts {\it and} tungsten absorber. 
\end{enumerate}

In this paper, we discuss in detail the results of the commissioning of the prototype in Section \ref{sec:commissioning}
and the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
We also show the results on the pedestal and noise stability when the readout modules are placed inside
a magnetic field, in Section \ref{sec:magnetic}. %The study of the performance of the detector
%for electromagnetic shower events is not covered in this document and will be the topic of a future paper.

\subsection{Commissioning of the detector}
\label{sec:commissioning}

Earlier experience with the SKIROC2 ASIC is been reported in \cite{Amjad:2014tha,Balagura:2017pka,Suehara:2018mqk}. 
For the following, the internal SKIROC2 parameters determined in these references are adopted
except if otherwise stated.
Since most of the data taking program consisted of the recording
of MIP level signals, we set a low value of the feedback capacitance of the preamplifier to $C_{f}=1.2$ pF  to obtain
gains of $71.25\,{\rm mV/fC}$ and $7.125\,{\rm mV/fC}$ in the dual-gain charge measurement.
With the higher of both gains, the SKIROC2 ensures a linearity better than 90\% 
for 0.5-200 MIPs, sufficient for
the analysis of electromagnetic showers created by few GeV positrons. All data presented here
were taken with the higher of the two gains.
%Once that the default internal settings of the SKIROC
%are defined, the commissioning was focus on the masking of the noisy channels
%and the optimization of the self-trigger thresholds.

\subsubsection{Masking of noisy readout channels}
\label{sec:noisy}

As a very first step channels are disabled that triggered already at
a threshold above 1 MIP noise runs.
For details the reader is referred to \cite{Bilokin:2018gfn}. The disabled channels can be classified into four categories:

\begin{itemize}
\item Routing issues: The same channels trigger in all layers. This hints at a issue with the routing of the PCB. 
  Following a conservative approach, we added to this set all channels that were noisy in at least three modules.
\item ASIC issues: In case 70\% of the channels of an ASIC triggered at, the entire ASIC was disabled.
  \item Sensor issues: If a wafer showed problems like  e.g. high leakage currents, all channels connected to the wafer were disabled.  
\item Others.
\end{itemize}

\begin{figure}[h!]
  \includegraphics[width=0.5\textwidth]{masked_layer-eps-converted-to.pdf} 
\caption{Fraction of channels with counts above one MIP in noise runs and that have been disabled for the data taking.}
\label{noisycells}
\end{figure}

All these channels have been disabled for the data taking.

\subsubsection{Trigger threshold optimization and signal-over-noise ratio for the trigger}
\label{sec:comm_trigger}

The threshold of the internal trigger can be optimized by means of dedicated scans of trigger threshold values
with only noise signals or with injected signals of different amplitudes.
%In the absence of external signals,
%the shape and position of the threshold scan curves shows the
%full envelope of the noise in the fast shaper which
%not only depends on the electronic noise but also on the slow clock frequency, making its interpretation
%not clear. 
The trigger thresholds used for data taking of the individual channels
are determined by lowering successively the trigger thresholds of the
channels and recording the number of counts. The resulting curves can be approximated by an inverted error function.
%Anyway, as the first goal is to set the trigger thresholds high enough to filter out most of the
%noise events independently of its origin, we made the optimization of the trigger threshold values by performing dedicated
%threshold scan runs with only noise. For that end, for a fixed amount of time, we counted the times that
%every channel recorded at least one trigger as a function of
%the internal trigger threshold. The resulting curve of acquisitions with triggers vs trigger threshold was
%interpreted as the integral of the noise spectrum, assumed as gaussian.
A value of the optimal threshold was calculated for every channel by shifting the threshold
from the threshold at the 50\% of the curve plus 3 times the width of the curve, 
with the width defined as half the difference between the thresholds
at which the curve is equal to $50\pm34\%$. The average of the optimal thresholds for all channels
is used as the optimal global threshold to be used by the ASIC.
If the analysis has failed in more than 50\% of the channels ({\it i.e.} because they are masked),
an {\it ad-hoc} high value of the threshold is chosen for the ASIC (250 in DAC units).

Note here that the width of the curve defined before depends on the ratio
of the frequency of the white noise of the electronics and the clock speed of the readout.
Therefore, the width is not a proper measurement of the detector noise.
To achieve this the scan has to be repeated with external signals.
These can either be provided by signals generated by beam particles or by injecting signals into the channels.
Here we follow the second approach. Amplitudes equivalent to 1 and 2 MIPs were injected into channels of an ASIC mounted on a testboard.

%With this procedure, we fulfill the first requirement: set the trigger thresholds high enough to filter the noise.
%We still need to know what is the size of signals that we can trigger on.
%For this we need to perform a calibration of the trigger thresholds
%and for that we need to perform the scans with calibrated external signals as input.
%We planned to do this with beam particle by performing
%scans with the beam hitting the detector at different angles. Unfortunately, due to tightness
%of the program this could not be done
%at the beam test described in this document. Instead
%we used injected signals directly on the SKIROCs. Again we face the issue that
%this capability is not included in all our modules so
%we did it in a SKIROC testboard \cite{Suehara:2018mqk} in which a single SKIROC2 in BGA package is placed and signals of
%the equivalent size of the expected for 1 MIP and 2 MIPs
%are directly injected in the preamplifier (via a 3 pF capacitor located in the injection line).
The result of these scans is shown in Figure \ref{scurves_injection} for several channels of one SKIROCs.
These curves allow for the trigger threshold calibration and the
estimation of signal-over-noise ratio for the trigger, $(S/N)_{trigger}$, defined as the ratio between the distance of the
1 MIP and 2 MIP threshold curves scans at its 50\% of efficiency and the width of the 1 MIP threshold scan curve.
From the measurement shown in Figure \ref{scurves_injection} we extract a $(S/N)_{trigger}$ ratio of about 12.8.

\begin{figure}[h!t]
    \centering
  \begin{tabular}{l}
	\includegraphics[width=0.35\textwidth]{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
	\end{tabular}
\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for different channels in a SKIROC2 testboard. From this plot, we extract a $(S/N)_{trigger}$ of about 12.8 in the trigger line.}
\label{scurves_injection}
\end{figure}

The trigger threshold calibration (from DAC units to MIPs) is extracted from these curves following a simple formula:

\begin{equation}
	\begin{split}
1 -Threshold[MIP] = \\
\frac{DAC_{50\%}(1\,MIP)-Threshold[DAC]}{DAC_{50\%}(2\,MIP)-DAC_{50\%}(1\,MIP)}
	\end{split}
\end{equation}

where $DAC_{50\%}(X\,MIP)$ stands for the DAC value in the $50\%$ point of the threshold scan curve obtained with $X$ MIP signals.
This calibration has been applied to all readout modules: see Figure \ref{trigger_thresholds}.
Further dedicated data taking runs with particle beams are needed in the future to measure the uncertainty and spread between SKIROCs and
modules of the used calibration.
%but the first studies using cosmic rays have shown compatible results~\cite{} with the injection tests with 1 MIP signals.

\begin{figure}[h!t]
  \centering
  \includegraphics[width=0.5\textwidth]{threshold_chip-eps-converted-to.pdf}
  \caption{Summary of the trigger threshold settings in the internal DAC units and in MIP units.}
\label{trigger_thresholds}
\end{figure}

\subsection{Response to 3 GeV positrons acting as MIPs}
\label{sec:calib}

All the analyses presented here rely on the selection and identification
of tracks-like events. The first step of the reconstruction is the rejection
of two types of fake events due to the ASIC
design: {\it a)} triggers in consecutive BCIDs
due to the preamplifiers sensitivity to instabilities of the power supply; {\it b)}
an artifact of the event validation logical sequence of the ASIC. These fake
events are removed offline using timing information.
Residual electromagnetic showers are rejected by requiring
less than 5 triggers per module.
Tracks are therefore reconstructed by creating clustered
events from the seven layers grouped using their time stamp, allowing for a
tolerance on the BCID of $\pm1$. An event is accepted if at least
three of the layers were clustered together in a track traversing the modules in the
same position
for all modules with a tolerance of $\pm5.5$ {\rm mm} per layer.

\subsubsection{Pedestal and noise determination}
\label{sec:pedestal}

The pedestal distribution for each channel and SCA corresponds to the
distribution of ADC counts recorded by the channel when another one was triggered.
The distributions are fit by a Gaussian. The mean of the Gaussian
is interpreted as the pedestal position. The width of the pedestal is associated to the 
standard deviation of the Gaussian.
Both values are calculated for all ASICS, channels and SCA under test.
Using these calculated pedestal positions, the pedestal subtraction to all measured charges in ADC counts is performed.
This process is done in a layer, ASIC, channel and SCA basis.
As a summary, all the calculated pedestal positions and widths of the ADC for all non-triggered and non-masked
channels and SCAs are shown in Figure \ref{pedestal_all}.
The non-gaussian spread of the pedestal position is explained by the fact that each SCA has its own pedestal value. More important is that the 
width of the distributions is very similar for all
channels and SCAs.
This is a proof of the homogeneity of the noise levels within the system.

\begin{figure}[h!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=0.5\textwidth]{h_ped_mean_notitle-eps-converted-to.pdf} \\
    \includegraphics[width=0.5\textwidth]{h_ped_width_notitle-eps-converted-to.pdf}
  \end{tabular}
  \caption{Pedestal mean position (upper) and width (lower) for all channels and all SCAs in the setup.}
\label{pedestal_all}
\end{figure}

\subsubsection{MIP calibration}
\label{sec:mip}

For all channels under test, the resulting charge spectrum of the triggered channels
after pedestal correction are fit by a Landau function convoluted with a Gaussian if the number of events was
larger than 1000. %In the example shown in Figure \ref{signal_pedestal}, this is represented
%by the red curve. In blue it is shown an example of pedestal distribution but only for one SCA
%to make scale of the y-axis reasonable.
The most-probable-value of the Landau function is taken as the MIP value, allowing thus for a direct
conversion from ADC counts to energy in MIP units.

%\begin{figure}[!ht]
%  \centering
%  \begin{tabular}{l}
%    \includegraphics[width=0.45\textwidth]{mip_pedestal_example-eps-converted-to.pdf}
%  \end{tabular}
%  \caption{Representative sample of distributions of the pedestal (blue dashed line) and MIP signal (black continuous line) for one channel.
%    In red, the result of the fit of the MIP distribution.}
%\label{signal_pedestal}
%\end{figure}

The fit succeeded in 98\% of the cases and the spread of the resulting MIP calibration is 5\%.
The remaining channels are discarded in the following analysis. Results are summarized in Figure \ref{mip}.

\begin{figure}[h!t]
  \centering
  \includegraphics[width=0.5\textwidth]{MIP_summary-eps-converted-to.pdf} \\
\caption{Result of the MIP calibration for all calibrated channels.}
\label{mip}
\end{figure}

\subsubsection{Signal-over-noise ratio for the charge measurement of triggered channels}
\label{sec:sn}

The signal over-noise-ratio for the charge measurement of triggered channels, $(S/N)_{charge}$, is defined 
as the ratio of the calculated MIP values to the noise (the pedestal width) for each channel and SCA.
This quantity has been calculated for all channels under test, giving:
\begin{equation}
(S/N)_{charge}=20.4\pm1.5
\end{equation}

The results are summarized in Figure \ref{mipandSN}.
%The large size of this value allows for a highly efficient offline filtering out of small spurious triggers.
The excellent ratio ensures that low energetic hits just above the trigger threshold can actually be used for the event reconstruction.

\begin{figure}[h!t]
  \centering
  \includegraphics[width=0.5\textwidth]{SN_summary-eps-converted-to.pdf}  
\caption{Distribution of the $(S/N)_{charge}$ for all calibrated channels.}
\label{mipandSN}
\end{figure}

\subsubsection{MIP detection efficiency}
\label{sec:mip}

To evaluate 
the single hit detection efficiency we increased the purity of our tracks sample
by requiring tracks with at least 4 layers with a hit in exactly the same channel.
For the remaining three layers the search region is extended to the eight channels
surrounding the target channel. Residual spurious signals are filtered by requiring a minimal energy deposition of 0.3 MIP.
%Afterwards we 
%check, among the seven layers, which have or not a hit in the same or in eight neighboring channels (if calibrated)
%with energy larger or equal than 0.3 MIP
%to filter out spurious signals.  
%We repeat this procedure for all channels.
The averaged results for every ASIC are shown in Figure \ref{efficiency}.
Except for a few exceptions, the efficiency is 
compatible with $100\%$.
The low efficiencies in the first layer are related to the presence of
noisy channels not spotted during the commissioning. These channels
saturate the DAQ in their ASICs earlier than in others.
In the last layer we also observe few small deviations
which are associated to channels in the periphery, hinting for a small misalignment of the last layer.

\begin{figure}[!t]
  \centering 
  \includegraphics[width=0.5\textwidth]{efficiency_nhits4_chips-eps-converted-to.pdf} \\
  \caption{MIP detection efficiency in high purity samples of tracks of MIP-like acting particles for all layers. The average for all readout channels in each ASICs is shown. The error bars correspond to the standard deviation of the efficiency distribution of all channels in th ASIC.}
\label{efficiency}
\end{figure}

\subsection{Pedestal and noise stability in a magnetic field}
\label{sec:magnetic}

Data were recorded without magnetic field as reference for values of the magnetic field of 0.5 T and 1T, respectively. 
%The study of the performance of the modules inside
%inside magnetic fields has been divided in three consecutive steps:
%a run with a magnetic field of 1 T; a second run with 0.5 T; and a final run with the magnet off.
The beam, 3 GeV positrons, was incident on the area of the PCB readout by the ASIC number 12.

The pedestal position and width of all channels
in the readout module inside of the magnetic field are compared with
their values obtained in Section \ref{sec:calib}.
This is shown in Figure \ref{pedestal_magnetic}.
We see that the agreement is perfect within the statistical uncertainties.
Due to the lower rates in this beam area, the
analysis is only done up to few memory cells and at least 500 entries are required in order to calculate the pedestals
for comparison with the default values.

\begin{figure}[!t]
  \centering
  \begin{tabular}{l}
    \includegraphics[width=0.5\textwidth]{1T_summary_pedestal-eps-converted-to.pdf} \\
    \includegraphics[width=0.5\textwidth]{1T_summary_noise-eps-converted-to.pdf}
  \end{tabular}
  \caption{Average deviation of the pedestal mean position (up) and width (down). The error bars correspond to one standard deviation of the averaged values.}
\label{pedestal_magnetic}
\end{figure}

\section{Summary and outlook}
\label{sec:summary}

In this document we present the results
on the commissioning in beam of a small but fully equipped SiW-ECAL technological prototype
made of readout modules featuring the main characteristics foreseen for future high energy $e^{+}e^{-}$ collider detectors.
%It is the first time that results obtained with data taken by the SiW-ECAL continuosly
%operated in power pulsing are published.
%For the first time results
% SETUP dedicated for physics program with electromagnetic showers.
For the first time results are presented for detection units featuring 1024 channels as
designed for e.g. the ILD Detector in a setup optimized for a physics program dedicated to the study
of electromagnetic showers. The seven layers under study were operated in power pulsed mode.
Therefore this article constitutes a first reference for the detector performance in this operation mode.  
The beam test has allowed for studying in detail 
the performance of the detector.
The detector response is homogeneous with
98\% of the non masked channels calibrated
at a spread of the 5\%.
The signal over noise on the trigger has been evaluated to be about 12.8, a value that allows to
for setting trigger below the MIP level with high efficiency 
although new dedicated beam tests are required to know the uncertainty and spread
of this value 
among different modules and ASICS.
The signal over noise on the charge measurement for triggered channels is 20.4, which 
ensures that all channels with a trigger just about noise level can be used in the data analysis.
The MIP detection efficiency in tracks has been evaluated to be compatible with the 100\% in most of the channels.

\section*{Acknowledgments}

This project has received funding from the European Union{\textquotesingle}s Horizon 2020 Research and Innovation program under Grant Agreement no. 654168.
This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).
The research leading to these results has received funding from the People Programme (Marie
Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
programme coordinated by Campus France.
The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).

%\bibliographystyle{JHEP}
\section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{../../references}

\end{document}

### 2019-04-04 performance-paper-draft/commissioning_arxiv1810.05133/arxiv-v0/draft_arxiv-v0.tex
Up to date to the arxiv submissions

--- 2018-08-20 performance-paper-draft/longversion/draft.tex
@@
 
-\linenumbers
+%\linenumbers
 
@@
 
+\author{\centering S.\,Bilokin\footnote{ Now at IPHC, Strasbourg.}, J.\,Bonis, P.\,Cornebise, A.\,Gallas, A.\,Irles,  R.\,P\"oschl, F.\,Richard, A.\,Thiebault, D.
+\,Zerwas \\ {\it Laboratoire de l'Acc\'elerateur Lin\'eaire, CNRS/IN2P3 et Universit\'e de Paris-Sud XI, Centre Scientifique d'Orsay B\^atiment 200, BP 34, F-91898 Orsay 
+CEDEX, France } 
+\\ M.\,Anduze, V.\,Balagura, V.\,Boudry, J-C.\,Brient, E.\,Edy, G.\,Fayolle, M.\,Frotin, F.\,Gastaldi, A.\,Lobanov, F.\,Magniette, J.\,Nanni, M.\,Rubio-
+Roy \footnote{ Now at Spintec, Grenoble} , K.\,Shpak, H.\,Videau, D.\,Yu\footnote{ Now at IHEP, Beijing.} \\ {\it Laboratoire Leprince-Ringuet (LLR) -- \'{E}cole Polytechnique, 
+CNRS/IN2P3, Palaiseau, F-91128 France } 
+\\ S.\,Callier, F.\,Dulucq, Ch.\,de la Taille, N.\,Seguin-Moreau \\ {\it Laboratoire OMEGA -- \'{E}cole Polytechnique-CNRS/
+IN2P3, Palaiseau, F-91128 France } 
+\\ J.E.\,Augustin, R.\,Cornat, J.\,David, P.\,Ghislain, D.\,Lacour, L.\,Lavergne\footnote{ Now at IRAP, Toulouse.}, J.M.\, Parraud \\ {\it Laboratoire de Physique Nucl\'eaire et de Hautes Energies 
+(LPNHE), Sorbonne Universit\'e, UPD, CNRS/IN2P3, 4 Place Jussieu, 75005 Paris, France } 
+\\ K.\,Kawagoe, Y.\,Miura, I.\,Sekiya, T.\,Suehara, T.\,Yoshioka, \\ {\it Department of Physics and Research Center for Advanced Particle Physics, 
+ Kyushu University, 744 Motooka, Nishi-ku, Fukuoka 819-0395, Japan } 
+\\ D.\,Jeans \\ {\it Institute of Particle and Nuclear Studies, KEK, 1-1 Oho, Tsukuba, Ibaraki 305-0801, Japan } 
+\\ J.\,S.\,Chai \\ {\it Department of Electrical and Computer Engineering, Sungkyunkwan Universtity, 16419, Suwon, Gyeonggi-do, Korea}}
+
 % e-mail addresses: only for the forresponding author
+%\collaboration[]{on behalf of the CALICE collaboration}
 \emailAdd{irles@lal.in2p3.fr}
-%\collaboration[]{on behalf of the CALICE collaboration}
 
 \abstract{
-  High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
-  of the final state of the particles produced in the collisions
-  Thia precission will be achieved thanks to the Particle Flow algorithms (PF) which require compact, highly granular and hermetic calorimeters systems.
-  The Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL) technological prototype
-  design and R\&D is oriented at the baseline design of the ECAL of the International Large Detector (ILD) for the ILC.
-  In this article we present the commissioning and the performance of the prototype in a beam test carried at DESY in June 2017.
+In this article we describe the commissioning and a first analysis of the the beam test performance of a small prototype of a highly granular silicon tungsten calorimeter.
+The prototype features detector elements with a channel number similar to that envisaged for e.g.
+the ILD Detector of the International Linear Collider (ILC).
+The analysis demonstrates the capability of the detector to record signals as low as 0.5 MIP.
+Further, no loss of performance has been observed when operating the detector in a high magnetic field.
 }
@@
 linear colliders such the ILC\cite{Behnke:2013xla,Baer:2013cma,Adolphsen:2013jya,Adolphsen:2013kya,Behnke:2013lya}.
-This project will provide collisions of polarized beams with center-of-mass energies of 250 GeV - 1 TeV.
-These collisions will be studied by two multipurpose detectors:
+This project will provide collisions of polarized beams with center-of-mass energies of 250 GeV to 1 TeV
+studied by multipurpose detectors. Two projects are proposed:
 the International Large Detector (ILD) and the Silicon Detector (SiD)\cite{Behnke:2013lya}.
-To meet the precision levels required by the ILC %or CLIC
-physics goals,
-new techniques relying on single particle separation to make possible the choice of the best information available
-in the full detector to measure the energy of the final state objects have been developed.
-These techniques are called Particle Flow (PF) techniques \cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}
-and allow to reduce the impact of the poor resolution of the calorimeter systems (compared with trackers) in the overall reconstruction.
-The PF algorithms impose some special requirements in the design of the detectors.
-For example, it requires highly granular, compact
-and hermetic calorimeters.
+To meet the precision required by the ILC %or CLIC
+physics goals, event reconstruction is based on the 
+Particle Flow (PF) technique \cite{Brient:2002gh,Morgunov:2004ed,Sefkow:2015hna}.
+PF implies the reconstruction of every single particle of the final state. 
+This in turn requires the construction of calorimeters with unprecedented granularity.
 
-The CALICE collaboration is driving most of the efforts on R\&D of highly granular calorimeters \cite{Sefkow:2015hna} 
+The CALICE collaboration is driving most of the efforts on R\&D of highly granular calorimeters
 for future linear colliders by investigating and building prototypes for several
@@
 is the silicon-tungsten electromagnetic calorimeter, SiW-ECAL.
-The SiW-ECAL is the baseline choice for the ILD electromagnetic calorimeter.
-It consists of a detector (in the barrel region) of 24 $X_{0}$ of thickness which corresponds to $\sim 1~\lambda_{I}$ (interaction length).
-It has silicon (Si) as active material and tungsten (W) as absorber material.
+Sensors made of pixellated Silicon diodes (Si) are sandwiched between tungsten (W) absorbers.
 The combination of Si and W choices  makes possible the design and construction
 of a very compact calorimeter with highly granular and compact active layers.
-It will be built an alveolar structure of carbon fiber into which modules made of tungsten
-plates and the active sensors will be inserted. The very-front-end (VFE) electronics will be
-embedded in the detector units. The silicon sensors will be segmented
-in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD.
+%30 layers in total
+%in the barrel region in modules of 20 cm thick.
+%It will be built an alveolar structure of carbon fiber into which modules made of tungsten
+%plates and the active sensors will be inserted. 
+In the detectors at the ILC, the very-front-end (VFE) electronics of the calorimeters will be
+embedded in the detector units. 
+%The silicon sensors will be segmented
+%in squared cells (or channels) of 5x5 mm: a total of $\sim 100$ million readout channels will constitute the ECAL for ILD
+%and a density of channels of 6000 channels/dm$^{3}$ in the barrel.
 The desired signal dynamic range in each channel goes from 0.5 MIP to 3000 MIPs, where the MIP acronym stands 
-for the energy deposited by a minimum-inonizing-particle.
+for the energy deposited by a minimum-iononizing-particle.
 To reduce overall power consumption, the SiW-ECAL will exploit the special bunch structure
-foreseen for the ILC: the $e^{+}e^{-}$ bunches trains will arrive in spills
-of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. The data acquisition will be gated during these short windows and during the idle time the bias currents of the electronics will be shut down.
-This technique is usually denominated power pulsing. In addition to this, to cope with the large amount of channels,
-the calorimeters should work in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.
+foreseen for the ILC with the $e^{+}e^{-}$ bunches trains grouped in spills
+of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. 
+The front-end electronics will only be enabled during the spills and the bias currents will be shut down between the spills. 
+This technique is usually denominated power pulsing. 
+The calorimeters are operated in self-trigger mode (each channel featuring an internal trigger decision chain) and zero suppression mode.
 
@@
 The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
-It was successfully tested at DESY, FNAL and CERN running in front of another prototype from the CALICE
-collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of the technollogy
-and the PF calorimetry.
-For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
+It was extensively tested between 2005 and 2011 at DESY, FNAL and CERN ~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}. 
+%running in front of another prototype from the CALICE
+%collaboration, the analogue hadronic calorimeter AHCAL, delivering the proof of concept of the technollogy
+%and the PF calorimetry.
+For the physics prototype, the VFE was placed outside the active area with no particular constraints in the power consumption.
 It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
 The active layers were made of a matrix of 3x3 Si wafers of 500 $\mu$m thickness. Each of these wafers was segmented in matrices of
-6x6 squared channels of 1x1 $cm^{2}$, allowing for a potential density of 1500 channels/dm$^{3}$ assuming
-the ILD baseline design constraints on the material repartition and compactness.
+6x6 squared channels of 10x10 mm$^{2}$.
 The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
@@
 That very first prototype offered a signal over noise on the measured charge of 7.5 for MIP like 
-particles. More results proving the good performance of the technology and the PF can be found in
-references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.
+particles.
 
 The current prototype is called the SiW-ECAL technological prototype. It addresses the main technological challenges: compactness,
-power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
-It will also provide data to deeply study the PF and provide input to tune simulation programs as for example
-GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
-in particle physics to simulate the passage of particles through matter. In this section we described in detail
+power consumption reduction through power pulsing and VFE inside the detector.
+%It will also provide data to deeply study the PF and provide input to tune simulation programs as for example
+%GEANT4\cite{Agostinelli:2002hh,Allison:2006ve,Allison:2016lfl} which is widely used
+%in particle physics to simulate the passage of particles through matter. 
+The study presented here extends considerably the work presented in Ref. \cite{Amjad:2014tha} 
+on an earlier version of the technological prototype that comprised 
+e.g. four times less channels per layer. 
+Further, in this earlier study the detector was still operated in continuous power mode.
+In this section we described in detail
 the main features and characteristics of the technological prototype.
@@
 %floating zone
-silicon wafers with a thickness of 320$\mu$m.
+silicon wafers with a thickness of $320\pm15\mu$m.
 The size of the wafers is $9\times9$ cm$^{2}$ and each of them is subdivided in an array of 256 PIN diodes of $5\times5$ mm$^{2}$.
-A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC
-for particles incident perpendicularly to its surface.
+A MIP traversing the PIN parallel to its normal will create $\sim$ 80 $h^{+}e^{-}$ pairs per $\mu$m which corresponds to 4.1 fC.
+%for particles incident perpendicularly to its surface.
 The original design of the silicon wafers included an edge termination made of floating guard-rings.
 It was observed in beam tests \cite{Cornat:2015eoa,Cornat:2009zz} that the capacitive coupling between such floating guard-rings 
-and the channels at the edge created not negligible rates off fake
+and the channels at the edge created not negligible rates of parasitic signals.
 events in tests with high energy beams (pions and electrons with energies larger than 20-40 GeV)
-An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-rings design 
-as well as the internal crosstalk. It was concluded that using wafers without guard rings and with a width of the peripheral areas lower than 
+An R\&D program together with Hamamatsu Photonics (HPK Japan) was conducted to study the guard-ring design 
+as well as the internal crosstalk. It was concluded that using wafers without guard-ring and with a width of the peripheral areas lower than 
 500$\mu$m thanks to the use of stealth dicing technique, the amount of these squared events 
 can be reduced to be at negligible level.
-For the setup described this article we used different solutions for the edge terminations.
-For all of them, the expected levels of fake events are negligible due to
-the low energy of the interactions studied in this paper:
-MIP like particles or electromagnetic showers created by particles of few GeV
-from the DESY beam. Therefore, they are not further discussed here.
+For the setup described in this article we used different solutions for the edge terminations.
+For all of them, the expected rate of fake events is however negligible due to
+the low energy of the particle beam studied in the present article.
+%MIP like particles or electromagnetic showers created by particles of few GeV
+%from the DESY beam. Therefore, they are not further discussed here.
 
@@
   \centering
-    \includegraphics[width=4in]{../figs/skiroc2_block.eps}
-\caption{The schematics of the analog part of SKIROC2. \todo{High-stack picture (right bottom corner)}}
+    \includegraphics[width=4in]{skiroc2_block.png}
+\caption{The schematics of the analog part of SKIROC2.}
 \label{SKIROC2}
@@
 a fast shaper for the trigger decision and a set of dual gain slow shapers for charge measurement.
-The gain can be controlled by modifying the feedback capacitance during the configuration of the detector.
-With the lowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs. 
-Finally, a Wilkinson type analogue to digital converter fabricates the digitized charge deposition that can be readout. 
-Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as
-triggered or not triggered and the information is stored in a 15 cell deep physical switched capacitor array (SCA).
+The gains can be controlled by modifying the feedback capacitance.
+%With the lowest gain, 6pF, the ASIC will handle a linear dynamic range from 0.1 to up to 1500 MIPs. 
+When there is a trigger, the charge of the triggered channel is held after a fixed delay 
+and stored in one of the memory cells of the 15 cell deep physical switched capacitor array (SCA). 
+At the end of the slow clock period in which a trigger occurred
+the held of the charge of all the channels not triggered is launched.
+Finally, the signals are digitized by a Wilkinson type analogue to digital converter.
+The digitized information includes tags to identify the channels with and without trigger.
 
-The SKIROC ASICs can be power-pulsed by taking advantage of the ILC spill structure: 
-the bias currents of the ASIC can be shut down during the idle time between bunch trains.
-With this method, the ASIC is able to reduce its power consumption down to 25 $\mu$W per channel,
-meeting the ILC requirements. 
-The power pulsing feature is used for all the results discussed in this paper
-and for first time in long periods of data taking in beam test.
+The SKIROC ASICs can be power-pulsed. 
+Under conditions as designed for the ILC the power consumption is expected to be as low as 25muW.
+The power pulsing feature is used for all the results discussed in this paper.
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=4in]{../figs/ASU_geometry1.eps}  \\
-    \includegraphics[width=4in]{../figs/ASU_geometry2.eps}  \\
+    \includegraphics[width=4in]{ASU_geometry1-eps-converted-to.pdf}  \\
+    \includegraphics[width=4in]{ASU_geometry2-eps-converted-to.pdf}  \\
   \end{tabular}
-  \caption{Repartition of the ASIC (up) and channels (down) in one ASU. In this perspective, the PCB is in the top
-    and the sensors are in glued in the back.
-    The channels are separated (in x and y) by 5.5 mm.
+  \caption{Repartition of the ASIC (up) and channels (down) in one ASU as viewed from the PCB side.
+    The channels are separated (in x and y) by 5.5 mm$^{2}$.
     The empty cross in the middle of the ASU corresponds to the 1 mm separation between the sensors.
@@
 The ASUs are currently equipped
-further with 16 SKIROC2 ASICs for the read out and features 1024 square pads (64 per ASIC) of 5x5 mm.
+further with 16 SKIROC2 ASICs for the read out and feature 1024 square pads (64 per ASIC) of 5.5x5.5 mm.
 The channels and ASICs are distributed along the ASU as shown in Figure \ref{ASU}. Each ASU is equipped with 4 silicon wafers as the described in Section \ref{sec:wafers}.
@@
 
-The current version of the PCB is called the FEV11. It has a thickness of 1.6mm which
-grows up to 2.7mm when the ASICs in its current packaging (1.1 mm thick LFBGA package) are
+The current version of the PCB is called the FEV11. It has a thickness of 1.6 mm which
+grows up to 2.7 mm when the ASICs in its current packaging (1.1 mm thick LFBGA package) are
 bonded in top of it.
-With these characteristics, a potential density of
-3800 channels/dm$^{3}$ is achievable keeping the space and
-interaction length requirements of the the baseline design of the ECAL forthe ILD.
-This number should be compared with
-the density achieved in beam tests with the physics prototype: 1500 channels/dm$^{3}$.
-With the first versions
-of the technological prototype we reached similar potential density level as in
-the current version but equipping only a
-quarter of the ASUs surface \cite{Amjad:2014tha}.
+%With these characteristics, a potential density of
+%4300 channels/dm$^{3}$ is achievable, to be compared with the channel density of the physics prototype of 
+%1500 channels/dm$^{3}$.
 
@@
 \begin{enumerate}
-\item The first component is the so called detector interface (DIF) which is placed at the beginning of each layer holding up to 15 ASUs.
-\item All DIFs are connected by single HDMI cables to the concentrator cards as the second component: the Gigabit Concentrator Cards (GDCCs).
-These cards are used to control up to 7 DIFs.
-They collect all data from the DIFs and distribute among them the system clock and fast commands.
+\item The first component is the so called detector interface (DIF) which is placed at the beginning of each layer.
+\item Each DIF is connected via a standard HDMI to the  second component: a concentrator card called the Gigabit Concentrator Cards (GDCCs).
+These cards control up to 7 DIFs.
+They collect all data from the DIFs and distribute in turn the system clock and fast commands.
   \item The most downstream component, is the clock and control card (CCC) which
@@
 
-\subsection{Fully equipped readout modules: the SLABs}
+\subsection{The prototype setup}
 \label{sec:setup}
@@
   \centering
-    \includegraphics[width=6in]{../figs/short_slab_bga.jpg} 
-  \caption{Open single SLAB with FEV11 ASU, 16 SKIROC 2 and the interface card visibles. }
+    \includegraphics[width=6in]{short_slab_bga_13.jpg} 
+  \caption{Open single readout layer with FEV11 ASU, 16 SKIROC 2 and the interface card visibles. }
 \label{ASU2}
@@
 
-A fully equipped readout module is shown in Fig. \ref{ASU2}. These modules are called
-SLABs and consist of a chain of one or several fully equipped ASUs
+A fully equipped readout module is shown in Fig. \ref{ASU2}. These modules consist in this case of one ASU
 connected to a data acquisition system (DAQ) through an adapter board, called SMBv4.
-The SMBv4 also serves as to hold other
-services as power connectors or the super capacitances used for the power pulsing. 
-These capacitances of 400mF with 16 m$\Omega$ of equivalent serial resistance
-are extra dimensioned to provide enough local storage 
-of power to assure stable low voltage levels during the power pulsing. %In this configuration
+The ASU is the squared PCB on the right side, equipped with the 16 SKIROC2 bump bonded.
+It is connected with kapton connectors to the SMBv4 PCB which occupies the rest of the picture.
+The SMBv4 also holds other
+services e.g. the super capacitance used for the power pulsing. 
+This decoupling capacitor (seen in the left bottom part of the photograph)
+ of 400mF with 16 m$\Omega$ of equivalent serial resistance
+provides enough local storage 
+of power to assure stable low voltage supply during the power pulsing. %In this configuration
 %the high currents are still crossing the interconnections/
@@
 
-For the production of the small sample of SLABs studied in this document,
+For the production of the small sample of readout modules studied in this document,
 a scalable working procedure has been established among several groups \cite{Boudry:2318814}
@@
 Figure \ref{assembly}. For more details we refer to Ref.\cite{Boudry:2318814}.
-This process is to be extrapolated to a full assembly procedure for
-e.g. the ILD detector.
+%This process is to be extrapolated to a full assembly procedure for
+%e.g. the ILD detector.
 
@@
 \begin{tabular}{l}
-\includegraphics[width=4.0in]{../figs/assembly.png} 
+\includegraphics[width=6.0in]{SiW-ECAL-Process_Flow_v2018.pdf}
 \end{tabular}
-\caption{Process flow for the assembly of the SiW-ECAL SLABs.}
+\caption{Process flow for the assembly of the SiW-ECAL readout layers.}
 \label{assembly}
@@
 
-\subsection{The prototype setup}
-\label{sec:setup2}
+%\subsection{The prototype setup}
+%\label{sec:setup2}
 
 A picture showing the SiW-ECAL technological prototype setup can be seen in Figure \ref{proto}.
-The current prototype consists on 7 layers of SLABs housed in a PVC and aluminum structure that can host up to 10 layers in slots separated by 15mm each.
-The first six layers were placed in the first six slots and the last one was in the last slot,
-with respect to the beam pipe. In the following sections, we will refer to layers number 1 to 7, where
-the 1 is the closest to the beam pipe and 7 is the farthest.
+The current prototype consists of 7 layers of 
+readout layers housed in a PVC and aluminum structure that can host up to 10 layers in slots separated by 15 mm each.
+The first six layers were placed in the first six slots and the last one was in the last slot.
+In the following sections, we will refer to layers number 1 to 7, where
+the 1 is the most upstream of the beam.
 This setup is used for commissioning (Section \ref{sec:commissioning}) and for the beam test
-(Section \ref{sec:beamtest}). In both cases, the detector was
-running in power pulsing mode.
+(Section \ref{sec:beamtest}).
 
@@
 \begin{tabular}{l}
-\includegraphics[width=4.0in]{../figs/proto.png} 
+\includegraphics[width=4.0in]{proto.png} 
 \end{tabular}
@@
 During the commissioning, we observed the repetition of coherent noise events affecting to several
-SLABs at the end of acquisitions with long gating time. The situation
-could be remedied by improving the isolation of the individual SLABs and by reducing the
+readout layers at the end of acquisitions with long gating time. The situation
+could be remedied by improving the isolation of the individual readout layers and by reducing the
 data taking to short gating times.
@@
 obtained by means of dedicated data taking runs. In these runs
-we scan relatively high trigger thresholds (between 1-3 MIPs) and progressively mask channels that exhibit counts. 
-In each step, the decision of tagging a channel as noisy was taking following the next rules:
+we scan relatively high trigger thresholds from larger to lower values ({\it i.e.} between 1-3 MIPs) and progressively mask channels that exhibit counts. 
+In each step, the decision of tagging a channel as noisy was taking following the rules described next:
 
@@
 \item if the channel was triggered at rates larger than 0.5-1\% of the total number of triggers per ASIC it was added to the list;
-\item if a channel was tagged as noisy in, at least, three of the SLABs, it was tagged as noisy for all and added to the list of channels being suspect of suffer from routing issues.
+\item if a channel was tagged as noisy in, at least, three of the readout layers, it was tagged as noisy for all and added to the list of channels being suspect of suffer from routing issues.
 \end{itemize}
 
-Following this procedure, we found to different types of noisy channels. One set consists of
+Following this procedure, we found two different types of noisy channels. One set consists of
 channels randomly distributed along the surface of every ASU and the other consists
@@
 In addition to the different noisy channel types described above, we also have
-masked full sectors of the SLABs if an ASIC was tagged as faulty (at least 70\% of channels 
+masked full sectors of the readout layers if an ASIC was tagged as faulty (at least 70\% of channels 
 listed as noisy) or if a Si-wafer was damaged (high leakage currents).
-The results of this study is summarized in Figure \ref{noisycells}.
+The results of this study are summarized in Figure \ref{noisycells}.
 
@@
   \centering
-  \begin{tabular}{l}
-  \includegraphics[width=4in]{../figs/commissioning/masked_layer.eps} \\
-  \includegraphics[width=4in]{../figs/commissioning/masked_chip.eps}
-  \end{tabular}
-\caption{Fraction of channels that are tagged as noisy in all slabs. 
-Top: different type of noisy channels per slab. 
-Bottom: break down of the total number of noisy channels per ASIC. 
-The ASICs 4-7 (wafer issue) and 10 from layer 1 and the ASIC 4 from layer 7 are not included
-in the second plot since they are fully masked.}
+  \includegraphics[width=4in]{masked_layer-eps-converted-to.pdf} \\
+\caption{Fraction of channels that are tagged as noisy in all readout layers.}
 \label{noisycells}
@@
 After the noisy channels have been masked, dedicated trigger threshold
-scan runs are taken, and the results are shown in the threshold scan curves where the
+scans are performed. The results are presented with the so-called the threshold scan curves where the
 x-axis represents the threshold value and the y-axis
@@
 where $p_{0}$ is 1/2 of the normalization, $p_{1}$ is the value in which the noise levels are 
-the 50\% of its maximum and $p_{2}$ give us the width of the threshold scan curve. 
+the 50\% of its maximum and $p_{2}$ give us the width of the error function. 
 In Figure \ref{scurve_channels} 
@@
   \begin{tabular}{ll}
-  \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn18_asic7_layer2.eps} & \includegraphics[width=2.8in]{../figs/commissioning/scurve_chn2_asic0_layer2.eps}
+  \includegraphics[width=2.8in]{scurve_chn18_asic7_layer2-eps-converted-to.pdf} & \includegraphics[width=2.8in]{scurve_chn2_asic0_layer2-eps-converted-to.pdf}
   \end{tabular}
@@
 
-\subsection{S/N ratio in the trigger branch}
+\subsection{S/N ratio for the trigger decission}
 \label{sec:comm_trigger_sn}
 
-Performing threshold scan scurves using
-real signals allow to calculate the signal over noise (S/N) ratio.
+Performing threshold scans using
+real signals allows to calculate the signal over noise (S/N) ratio
+for the trigger decision.
 For that we compare the curves for 1 MIP and 2 MIP injected signals.
 The S/N is, in the following, defined as the ratio between the distance of both curves at its
-50\% and the width of the curves.
+50\% and the width of the curves. The width is defined as the half of distance, in threshold units, between the
+curve at $50\pm34\%$.
 In Figure \ref{scurves_injection} we see the 1 MIP and 2 MIP curves obtained for several channel
 in a SKIROC testboard in which a single SKIROC2 in BGA package is placed and the 1 MIP and 2 MIPs 
- signals are directly injected in the preamplifier 
+size signals are directly injected in the preamplifier 
 (via a 3 pF capacitor located in the injection line as shown in Figure \ref{SKIROC2}).
@@
   \begin{tabular}{l}
-	\includegraphics[width=4in]{../figs/commissioning/scurve_pp_fastshaper_ch_DAC.eps} \\
+	\includegraphics[width=4in]{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
 	\end{tabular}
@@
   \begin{tabular}{l}
-	\includegraphics[width=4in]{../figs/commissioning/cosmic_scurves_asic3_layer2.eps} 
+	\includegraphics[width=4in]{cosmic_scurves_asic3_layer2-eps-converted-to.pdf} 
 	\end{tabular}
@@
 \begin{equation}
-  S/N=12.9\pm3.4
+  S/N(trigger)=12.9\pm3.4
 \end{equation}
-for the trigger branch. The central value is calculated from Figure \ref{SKIROC2} by
-the comparison of the 1 and 2 MIP curves and using the width of the 1 MIP curve in the denominator. The estimated
+for the trigger decision. The central value is calculated from Figure \ref{SKIROC2} by
+the comparison of the 1 and 2 MIP curves and using the width of the 1 MIP curve in the denominator.
+ The estimated
 uncertainty has two components: the difference of width between the 1 and 2 MIP curves of injected signals and the differences (width and middle point) between the 1 MIP curves for injected and
-cosmic ray signals.
-
-Dedicated studies in beam test are needed in order to
+cosmic ray signals. With this value of the 
+S/N we are able to operate the internal trigger for small signals of the size of $\sim0.5$ MIP.
+This is seen in \ref{trigger_thresholds} where the chosen thresholds of every ASIC being tested
+in beam are shown. However dedicated studies in beam test are needed in order to
 reduce the uncertainty of this measurement.
-However, by combining the information contained in the Figs \ref{scurves_injection} and \ref{scurves_cosmics}, we can also estimate the energy that corresponds
-to a given trigger threshold.
-This is shown in Figure \ref{trigger_thresholds}, where the chosen threholds of every ASIC being tested
-in beam are shown.
 
@@
   \centering
-  \includegraphics[width=4in]{../figs/commissioning/threshold_chip.eps}
+  \includegraphics[width=4in]{threshold_chip-eps-converted-to.pdf}
   \caption{Summary of the trigger threshold settings in internal DAC units and in MIP units.}
@@
 Using this new procedure we manage to reduce the number of masked channels by a factor of two
-without any loss of performance, at least in the laboratory and using 3 of the 7 SLABs.
+without any loss of performance, at least in the laboratory and using 3 of the 7 readout layers.
 This new procedure will also be applied in the next beam test.
@@
 \item Test in magnetic field up to 1 T using the PCMag. For this test a special PVC structure was
-  designed and produced to support one single SLAB.	
+  designed and produced to support one single readout layer.	
   The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
-  mechanical consistency of the SLAB itself are able
+  mechanical consistency of the readout layer itself are able
   to handle strong magnetic fields; 
@@
   \begin{tabular}{l}
-    \includegraphics[width=4in]{../figs/mip_pedestal_example.eps}
+    \includegraphics[width=4in]{mip_pedestal_example-eps-converted-to.pdf}
   \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/ped_mean_layer2.eps} & \includegraphics[width=2.8in]{../figs/pedestal/width_mean_layer2.eps}
+    \includegraphics[width=2.8in]{ped_mean_layer2-eps-converted-to.pdf} & \includegraphics[width=2.8in]{width_mean_layer2-eps-converted-to.pdf}
   \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/h_ped_mean.eps} & \includegraphics[width=2.8in]{../figs/pedestal/h_ped_width.eps}
+    \includegraphics[width=2.8in]{h_ped_mean-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width-eps-converted-to.pdf}
   \end{tabular}
@@
   \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/MIP/MIPsummary_title.eps} & \includegraphics[width=2.8in]{../figs/MIP/SNsummary_title.eps}  
+      \includegraphics[width=2.8in]{MIPsummary_title-eps-converted-to.pdf} & \includegraphics[width=2.8in]{SNsummary_title-eps-converted-to.pdf}  
   \end{tabular}
-\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated channels.}
+\caption{Result of the MIP position calculation and signal over noise for the charge measurement on triggered channels for all calibrated channels.}
 \label{mipandSN}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=4in]{../figs/MIP/MIP3peaks.eps} 
+      \includegraphics[width=4in]{MIP3peaks-eps-converted-to.pdf} 
     \end{tabular}
@@
    % \begin{tabular}{ll}
-  \includegraphics[width=4in]{../figs/MIP/efficiency_nhits4_chips.eps}
-  %& \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom.eps} \\
+  \includegraphics[width=4in]{efficiency_nhits4_chips-eps-converted-to.pdf}
+  %& \includegraphics[width=2.8in]{../figs/MIP/efficiency_nhits4_chips_zoom-eps-converted-to.pdf} \\
   %  \end{tabular}
@@
 
-\subsubsection{Power of signal separation for MIP-size signals}
+\subsubsection{S/N for the charge measurement of triggered channels}
 \label{sec:sn}
 
-The power of signal separation for MIP size signals is defined 
+The S/N for the charge measurement of triggered channels is defined 
 as the ratio between the most-probable-value of
@@
 Results are summarized in Figure \ref{mipandSN}, rightmost plot.
-It is important to remark that this definition corresponds to what
-has been called so far as the S/N of the SiW-ECAL (see for example Ref. \cite{Amjad:2014tha}).
-However, we think that it is more correct to define the S/N of the detector
-in the trigger decission line and use the power of signal separation concept
-for the the quantity described at the beginning of the paragraph.
+The large size of this value allows us to filter out small spurious triggers 
+with high efficiency.
 
@@
 The pedestal positions and noise levels of the channels of the ASIC 12 when the
-SLAB is inside of the PCMag are compared with the results from the calibration run described in the previous section.
+readout layer is inside of the PCMag are compared with the results from the calibration run described in the previous section.
 This is shown in Figure \ref{pedestal_magnetic}.
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_pedestal_chip12.eps} & \includegraphics[width=2.8in]{../figs/pedestal/1T/summary_noise_chip12.eps}
+    \includegraphics[width=2.8in]{summary_pedestal_chip12-eps-converted-to.pdf} & \includegraphics[width=2.8in]{summary_noise_chip12-eps-converted-to.pdf}
   \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_energy_shower.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_vs_nhits_shower.eps} \\
+      \includegraphics[width=2.8in]{pedestal_vs_energy_shower-eps-converted-to.pdf} & \includegraphics[width=2.8in]{pedestal_vs_nhits_shower-eps-converted-to.pdf} \\
     \end{tabular}
@@
     \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_layer3.eps} & \includegraphics[width=2.8in]{../figs/pedestal/pedestal_deviation_4GeV.eps} \\
+      \includegraphics[width=2.8in]{pedestal_deviation_layer3-eps-converted-to.pdf} & \includegraphics[width=2.8in]{pedestal_deviation_4GeV-eps-converted-to.pdf} \\
     \end{tabular}
@@
 similar to the targets of the ILD detector for the ILC. This is also the first time
-that a SiW-ECAL prototype continuously takes data in a beam test running in power pulsing mode, one of the crucial
-features for the detectors for the ILC. Finally, we tested the performance of the detector
+that results with the SiW-ECAL prototype continuously working in power pulsing mode are published.
+Finally, we tested the performance of the detector
 modules working for long periods inside magnetic fields.
 
-A very comprehensive and detailed commissioning procedure has been established and optimized
-allowing us to identify and isolate the different noise sources that could spoil the data taking.
+%A very comprehensive and detailed commissioning procedure has been established and optimized
+%allowing us to identify and isolate the different noise sources that could spoil the data taking.
 The beam test has provided a lot of useful data to study 
@@
 a channel by channel calibration, showing a good homogeneity with a spread of the 5\% for all channels.
-The signal over noise, S/N, of the detector has been evaluated to be $12.9\pm3.4$.
-The power of signal separation for signals of 1 MIP is $20.4\pm1.5$.
+The S/N on the trigger has been evaluated to be $12.9\pm3.4$.
+The S/N on the charge measurement of triggered cells is $20.4\pm1.5$. The hit detection efficiency
+in tracks has been evaluated to be compatible with 100\%.
 
@@
 
-Many efforts are also concentrated in the construction and test of long SLABs
+Many efforts are also concentrated in the construction and test of long readout layers
 made of several ASUs enchained since we know that the ILD ECAL will host long layers of up to $\sim$2.5m.
@@
 and require close collaboration between mechanical and electronic engineers.
-A first long SLAB prototype
+A first long readout layer prototype
 of $\sim8$ ASUs has been already tested in beam test also in DESY in 2018.
@@
 A small sample of FEV11\_COBs (same connexion pattern with the interface card than FEV11)
-with a total thickness of 1.2 mm (to be compared with the 2.7 of the LFBGA solution in the FEV11)
+with a total thickness of 1.2 mm (to be compared with the 2.7 mm of the LFBGA solution in the FEV11)
 has been produced and tested in the laboratory
 showing its readiness for tests with particle beams. A sample can be seen in Figure \ref{cob}.
-These new boards maximize the density of channels (6000 channels/dm$^{3}$) for the ECAL of the ILD
-and will allow to satisfy the baseline requirements of the ECAL for the ILD.
+%These new boards maximize the density of channels (6000 channels/dm$^{3}$) 
+%satisfying the baseline requirements of the ECAL for the ILD.
 
@@
   \centering
-    \includegraphics[width=2.8in]{../figs/fev11_cob.png} 
+    \includegraphics[width=2.8in]{fev11_cob.png} 
   \caption{Two FEV11\_COB boards with 16 SKIROC2a wire bonded. The ASICs are protected with watch glasses.}
@@
 \bibliographystyle{JHEP}
-\bibliography{../references}
+\bibliography{../../references}
 

### 2019-04-04 performance-paper-draft/commissioning_arxiv1810.05133/arxiv-v1/draft_arxiv-v1.tex
Up to date to the arxiv submissions

--- 2019-04-04 performance-paper-draft/commissioning_arxiv1810.05133/arxiv-v0/draft_arxiv-v0.tex
@@
 
+%\usepackage{jinstpub} % for details on the use of the package, please
+                     % see the JINST-author-manual
 \usepackage{jinstpub} % for details on the use of the package, please
-                     % see the JINST-author-manual
 
@@
 
-\author{\centering S.\,Bilokin\footnote{ Now at IPHC, Strasbourg.}, J.\,Bonis, P.\,Cornebise, A.\,Gallas, A.\,Irles,  R.\,P\"oschl, F.\,Richard, A.\,Thiebault, D.
+\author{\centering S.\,Bilokin\footnote{ Now at IPHC, Strasbourg.}, J.\,Bonis, P.\,Cornebise, A.\,Gallas, A.\,Irles**,  R.\,P\"oschl, F.\,Richard, A.\,Thiebault, D.
 \,Zerwas \\ {\it Laboratoire de l'Acc\'elerateur Lin\'eaire, CNRS/IN2P3 et Universit\'e de Paris-Sud XI, Centre Scientifique d'Orsay B\^atiment 200, BP 34, F-91898 Orsay 
@@
   \end{tabular}
-  \caption{Pedestal mean position (left plot) and width (right plot) for all channels in one layer.}
+  \caption{Upper plots: pedestal mean position (left plot) and width (right plot) for all channels in one layer.
+Lower plots: same plots but after subtracting the corresponding averaged values calculated for each ASIC and SCA.}
 \label{pedestal_layer}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{h_ped_mean-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width-eps-converted-to.pdf}
+    \includegraphics[width=2.8in]{h_ped_mean_notitle-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width_notitle-eps-converted-to.pdf} 
+%%    \includegraphics[width=2.8in]{h_ped_mean_average-eps-converted-to.pdf} & \includegraphics[width=2.8in]{h_ped_width_average-eps-converted-to.pdf} \\
   \end{tabular}
@@
   \begin{tabular}{ll}
-      \includegraphics[width=2.8in]{MIPsummary_title-eps-converted-to.pdf} & \includegraphics[width=2.8in]{SNsummary_title-eps-converted-to.pdf}  
+      \includegraphics[width=2.8in]{MIP_summary-eps-converted-to.pdf} & \includegraphics[width=2.8in]{SN_summary-eps-converted-to.pdf}  
   \end{tabular}
@@
   \begin{tabular}{ll}
-    \includegraphics[width=2.8in]{summary_pedestal_chip12-eps-converted-to.pdf} & \includegraphics[width=2.8in]{summary_noise_chip12-eps-converted-to.pdf}
+    \includegraphics[width=2.8in]{1T_summary_pedestal-eps-converted-to.pdf} & \includegraphics[width=2.8in]{1T_summary_noise-eps-converted-to.pdf}
   \end{tabular}

### 2019-04-04 proceedings/CHEF/beamtest/proceeding_v1.tex
create folder for all confereces (2017)

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jinstpub} % for details on the use of the package, please
                     % see the JINST-author-manual

\title{\boldmath Latest R\&D news and beam test performance of the highly granular SiW-ECAL technological prototype for the ILC.}

%% %simple case: 2 authors, same institution
%% \author{A. Uthor}
%% \author{and A. Nother Author}
%% \affiliation{Institution,\\Address, Country}

% more complex case: 4 authors, 3 institutions, 2 footnotes
\author[a]{A. Irles\note{Corresponding author.} on behalf of the CALICE collaboration}
%\author{on behalf the CALICE collaboration}

% The "\note" macro will give a warning: "Ignoring empty anchor..."
% you can safely ignore it.

\affiliation[a]{Laboratoire de l'Acc\'el\'erateur Lin\'eaire, Centre Scientifique d'Orsay, Universit\'e de Paris-Sud XI, CNRS/IN2P3, F-91898 Orsay Cedex, France}

% e-mail addresses: only for the forresponding author
\emailAdd{irles@lal.in2p3.fr}
%\collaboration[]{on behalf of the CALICE collaboration}

\abstract{
  High precision physics at future colliders as the International Linear Collider (ILC) require unprecedented high precision in the determination
  of the energy of final state particles.
  The needed precision will be achieved thanks to the Particle Flow algorithms (PF) which require highly granular and hermetic calorimeters systems.
  The physical proof of concept of the PF was performed in the previous campaign of beam tests of physic prototypes within the CALICE collaboration.
  One of these prototypes was the physics prototype of the Silicon-Tungsten Electromagnetic Calorimeter (SiW-ECAL)
  for the ILC. 
  In this document we present the latest news on R\&D of the next generation prototype,
  the technological prototype with fully embedded very front-end (VFE) electronics,
  of the SiW-ECAL.
  Special emphasis is given to the presentation and discussion of the first results from the beam test done at DESY in June 2017.
  The physics program for such beam test consisted in the calibration and commissioning of the current set of available SiW ECAL modules;
  the test of performance of individual slabs under 1T magnetic fields; and the study of electromagnetic showers events.
}

\keywords{Calorimeter methods, calorimeters, Si and pad detectors}

%\arxivnumber{1234.56789} % only if you have one

% \collaboration{\includegraphics[height=17mm]{example-image}\\[6pt]
%   XXX collaboration}
% or

% if you write for a special issue this may be useful
\proceeding{Calorimetry for the High Energy Frontier 2017\\
  October 2-6, 2017\\
  Lyon, France}

\begin{document}
\maketitle
\flushbottom

\section{Introduction}

The International Linear Collider, ILC~\cite{Behnke:2013xla}, is an accelerator based particle physics project
which will provide collisions of polarized beams made up of $e^{+}e^{-}$ with center-of-mass energies ($c.m.e$) of 250 GeV - 1 TeV.
These collisions will be studied by two multipurpose detectors:
the International Large Detector (ILD) and the Silicon Detector (SiD)~\cite{Behnke:2013lya}.
The accomplishment of the ambitious physics program~\cite{Baer:2013cma,Fujii:2017vwa} of the ILC requires
unprecedented precision in the energy determination of final states.
To meet these required precision levels, the detectors will be based on the Particle Flow (PF) techniques~\cite{Brient:2002gh,Morgunov:2004ed}.
These techniques rely on single particle separation in the full detector volume to choose the best information available
to measure the energy of the final state objects (i.e. measuring the charged particles momentum at tracking devices better than in the calorimeters).
Therefore, PF algorithms require highly granular and compact calorimeter systems featuring minimum dead material (high hermeticity).
The R\&D of highly granular calorimeters for future linear colliders is conducted within the CALICE collaboration.%~\cite{calice}.
For further information about PF and CALICE R\&D we refer the reader to reference~\cite{Sefkow:2015hna} and references therein.

In this document we will focus in the description of the silicon-tungsten electromagnetic calorimeter, SiW-ECAL, technological prototype
and its performance in beam test. The design and R\&D of this prototype is conducted by CALICE and it is oriented at the baseline design of the ILD ECAL.
The ILD ECAL is a sampling calorimeter of 24 $X_{0}$ of thickness (in the barrel region) and it
uses silicon (Si) as active material and tungsten (W) as absorber material.
The combination of Si and W for the construction of the detector allows
the construction of a very compact calorimeter made up of compact active layers with small cell size (high granularity) in the transverse and longitudinal planes.
It will consist of an alveolar structure of carbon fiber into which the slabs made up of tungsten
plates and active sensors will be inserted. The very-front-end (VFE) electronics will be
embedded in the slabs.
The silicon sensors will be segmented
in squared cells of 5x5 mm, featuring a total of $\sim 100$ million channels for the ECAL of the ILD.
To reduce overall power consumption, the ILD ECAL will exploit the special bunch structure
foreseen for the ILC: the $e^{+}e^{-}$ bunchs trains will arrive within
acquisition windows of $\sim$ 1-2 ms width separated by $\sim$ 200 ms. During the idle time, $\sim99\%$ of the time, the bias currents of the electronics will be shut down.
This technique is usually denominated power pulsing. In addition, as the PF techniques demands minimum dead material in the detector,
the design of the ILD foresees the calorimeters (hadronic and electromagnetic) to be placed inside the magnetic coil that provides magnetic fields of 3.5 T.

\section{The SiW-ECAL engineering prototype.}

The first SiW-ECAL prototype was the so called SiW-ECAL physics prototype.
It was successfully tested at DESY, FNAL and CERN running together with another CALICE prototype,
the analogue hadronic calorimeter AHCAL, delivering the proof of concept of PF calorimetry.
For the physics prototype, the VFE was placed outside the active area with no particular constraints in power consumption.
%It consisted of 30 layers of Si as active material alternated with tungsten plates as absorber material.
%The active layers were made of a matrix of 3x3 Si wafers. Each of these wafers was segmented in matrices of
%6x6 squared pixels of 1x1 $cm^{2}$.
%The prototype was divided in 3 modules of 10 layers with different W depth per layer in each of these modules
%(0.4, 1.6 and 2.4 $X_{0}$) making a total of 24 $X_{0}$ which equivales to $\sim 1~\lambda_{I}$ (interaction length).
Published results proving the good performance of the technology and the PF can be found in references~\cite{Adloff:2011ha,Anduze:2008hq,Adloff:2008aa,Adloff:2010xj,CALICE:2011aa,Bilki:2014uep}.

The new generation prototype is called the SiW-ECAL technological prototype  and it addresses the main technological challenges: compactness,
power consumption reduction through power pulsing and VFE inside the detector close to real ILD conditions.
It will also provide data allowing deep studies of the PF performance and input to tune the Monte Carlo programs.

%\subsection{Slabs and Active Sensor Units.}
The base unit of such technological prototype is the Active Sensor Units or ASU which is the entity of sensors, thin PCB (printed circuit boards) and ASICs (application-specific integrated circuits).
An individual ASU has a lateral dimension of 18x18 cm$^{2}$ and has glued onto it 4 silicon wafers (currently with a thickness of 320 $\mu$m).
The ASUs are equipped
further with 16 ASICs for the read out and features 1024 square pads, 64 per ASIC, of 5x5 mm$^{2}$ (the physics prototype featured squared pads of 10x10 mm$^{2}$).
The readout layers of the SiW-ECAL consist of a chain of ASUs and an interface card
to a data acquisition system (DAQ) at the beginning of the layer.
This interface card also carries services as power connectors,
test output pins, connectors for signal injection, etc. 
Currently, the technological prototype layers are built with a version of the PCB called FEV11 with
16 SKIROC~\cite{Callier:2011zz} (Silicon pin Kalorimeter Integrated ReadOut Chip) ASICs version 2
in BGA packages mounted on top of it. The SKIROC ASIC consists of 64 channels comprising each a low noise charge preamplifier of variable gain followed by two lines:
a fast line for the trigger decision and a slow line for dual gain charge measurement.
Finally, a Wilkinson type analogue to digital converter fabricates the digitized charge deposition that can be readout.
Once one channel is triggered, the ASIC reads out all 64 channels adding a bit of information to tag them as triggered or not triggered.
The information is stored in 15 cell deep physical switched capacitor array (SCA).
This autotrigger capability is mandatory for the ILC case since the accelerator will not provide a central global trigger.
A key feature of the SKIROC ASICs is that they can be power pulsed to meet ILC power consumption requirements.
A new version, 2a, has been produced and will be used to equip new layers currently in production.
The design of the subsequent chain of the data acquisition (DAQ) is described in~\cite{Gastaldi:2014vaa}. 
The whole system is controlled by the Calicoes and the Pyrame DAQ software version 3~~\cite{pyrame1,pyrame2}.

\begin{figure}[!t]
  \centering
  \includegraphics[width=5in]{figures/techno_fev8.eps}
  \caption{Leftmost upper figure: open single SLAB with FEV11 ASU, 16 SKIROC, interface card and DIF visible; the silicon sensors are glued to the PCB in the other side. Leftmost lower figure: picture of the technological prototype with 7 single short layers inside a mechanical aluminum structure designed for beam tests. Rightmost photographs show the FEV11\_COB: the upper figure correspond to a picture taken from the top; the lower one corresponds to a lateral picture.}
  \label{proto}
\end{figure}

Figure \ref{proto}, leftmost upper plot, shows a picture of a full equipped short slab with FEV11 ASU. 
These PCBs still don't meet current requirements
for the ILD in terms of thickness (1.2 mm). The FEV11 thickness is 1.6 alone and 2.7 mm including the ASICs.
There are ongoing R\&D activities in an alternative PCB design in which the ASICs
will be directly placed on board of the PCB in dedicated cavities. The ASICS will be in semiconductor packaging and wire bonded to the PCB.
These PCBs are denominated COB for "chip on board".
A small sample of FEV11\_COB boards with thickness of 1.2 mm have been produced (see figure \ref{proto} rightmost photographs)
and is planned to be added to the prototype and tested in beam tests conditions.

\section{Performance on positron beam test.}

The prototype tested in beam in June 2017 consisted of 7 layers: see figure \ref{proto} leftmost lower photograph.
A dedicated and comprehensive commissioning process was followed before going to the beam test.
The commissioning included the definition of trigger threshold values or the list noisy channels to be masked.
In the first layer, $\sim 40\%$ of channels were masked due to a damaged Si wafer. In all the other, only the 6-7\% of channels were masked except in the last one were this number grew up to the 16\% due to a faulty ASIC. The number of masked channels may be drastically reduced by setting individual threshold settings instead of global trigger threshold values for each channel on an ASIC. This possibility will become available with the next version of SKIROC ASIC.

The detector was exposed to a positron beam in the DESY test beam area (line 24).
The beam test line at DESY provides continuous positron beams in the energy range of 1 to 6 GeV with
rates of the order of the KHz (with maximum of $\sim 3$ KHz). In addition, DESY gives acces to a bore 1 T solenoid in the beam area. 
The detector was running in power pulsing mode without any extra active cooling system.
By means of an external pulse generator we defined the length of the acquisition window to be
3.7 ms at a frequency of 5 Hz.

The physics program of the beam test can be summarized in the following points:

\begin{itemize}
\item Commissioning and calibration without absorber using 3 GeV positrons acting as minimum ionizing particle (MIPs);
\item magnetic field tests up to 1 T;
\item response to electrons with fully equipped detector, i.e. sensitive parts {\it and} W absorber.
\end{itemize}

\subsection{Calibration runs.}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.6in]{figures/MIPsummary_title.eps} & \includegraphics[width=2.6in]{figures/SNsummary_title.eps}
  \end{tabular}
\caption{Result of the MIP position calculation and signal over noise calculation for all calibrated cells.}
\label{mipandSN}
\end{figure}

The main calibration was realized 
by directing the 3 GeV positron beam on 81 positions equally distributed over the surface of the detector.
These data were used for pedestal estimation and energy calibration.
Calibration and pedestal analysis was done for all single layers not requiring track reconstruction.
We calculated the pedestal position for every channel and SCA by fitting the distribution of non triggered hits with a Gaussian function.
Afterwards, we subtracted these values to the distribution of triggered hits and fit the resulting distributions to a Landau function convoluted by a Gaussian.
The most-probable-value of the convoluted function is taken as the MIP value.
We have obtained a raw energy calibration spread of the 5\% among all cells with the 98\% of all available cells being fitted. Results are summarized in figure \ref{mipandSN}, leftmost plot.

The signal-over-noise ratio, defined as the ratio between the most-probable-value of
the Landau-gauss function fit to the data (pedestal subtracted) and the pedestal width
(calculated as the standard deviation of the Gaussian distribution fitted to the data), was estimated.
The average value for all channels and slabs is 20.4.
Results are summarized in figure \ref{mipandSN}, rightmost plot.

\begin{figure}[!t]
  \centering
    \begin{tabular}{ll}
      \includegraphics[width=2.6in]{figures/MIP3peaks.eps} & \includegraphics[width=2.6in]{figures/MIPefficiency_hitsintrack5_hitouttrack0_bcidcut2850_chip.eps} \\
    \end{tabular}
    \caption{Left: the single cell energy distribution (for all calibrated cells) for 3 GeV positron tracks acting as MIPs. Right: hit efficiency for all layers and ASICs in high purity samples of tracks of MIP-like acting particles.}
\label{miplog}
\end{figure}

After pedestal subtraction, calibration and track reconstruction we could finalize the MIP calibration by selecting tracks that cross the detector parallel to its normal.
The results are shown in figure \ref{miplog} where, in the leftmost plot, single cell the energy distribution for MIPs is shown for all calibrated cells. 
The distribution reveals the presence of a second and third peak due to events involving multiple particles crossing the detector.
In the rightmost plot, we
summarize the results of hit detection efficiency in tracks made of MIP acting particles. To evaluate the efficiency we define a high purity sample of
events of positron traversing the detector perpendicularly by selecting
tracks with at least 5 layers (of 7 possible) with a hit in exactly the same cell. Afterwards we check if the other layers have or not a hit in the same cell. Finally, we repeat this for all layers and cells and show the result for all ASICs and layers. Except few exceptions, the efficiency is compatible with $100\%$.
Lower efficiencies may be related to some channels having effective high thresholds for the triggers.
This can be improved with the next generation of SKIROC (the 2a) which allow for threshold optimization of single channels.
To avoid the confusion of the concept of inefficiency and blindness of the detector due to saturation of the DAQ
(for example if a noisy channels fills up the memory before the physical signal) we constraint the analysis to events that are stored before the last but one cell in the SCA.

Finally, a calibration run with the beam hitting the slabs under an angle of $\sim 45^{0}$ was done.
The purpose of this run was to prove that the MIP position scales with a factor $\sqrt{2}$
due to the larger path to be crossed by the positron in the Si wafer.
Preliminary results show a perfect agreement with the expected results.

\subsection{Magnetic field tests.}

For this test, a special PVC structure was
designed and produced to support the slab.

The purpose of the test was twofold: first to prove that the DAQ, all electronic devices and the mechanical slab itself were able
to handle strong magnetic fields; second to prove the stability of performance during these tests.
We took several runs, with 0, 0.5 and 1 T magnetic fields with and without 3 GeV positron beam.
We observed that the pedestals position is independent of the magnetic field (within the 1 per mille). The MIP position was increased, in average,
by 3\% for 1 T and 1.5\% for 0.5 T with respect with the 0 T case.
This level of increase is expected since the positron traversing the magnetic field hit the slab with a deflecting angle,
increasing then the path of the particle through the wafer. More detailed studies and simulation comparisons are to come.

\subsection{Response to electromagnetic showers.}

\begin{figure}[!t]
  \centering
  \begin{tabular}{ll}
    \includegraphics[width=2.6in]{figures/energy_z_profile_grid20_conf2.eps} & \includegraphics[width=2.6in]{figures/4GeV_energy_z_profile.eps} 
  \end{tabular}
  \caption{Raw electromagnetic shower profiles for different tungsten configurations and several energies of the beam. In the x-axis, we show the layer number. In the y-axis, the averaged fraction of {\it energy} (sum of ADC in all triggered cells in a event, considering only events where all layers had at least a hit) measured in every layer. }
\label{showers}
\end{figure}

The purpose of the test was to study the interaction of positrons with the absorber material resulting in
electromagnetic showers.
We inserted W plates of different thicknesses between the sensitive layers and we performed
a scan of energies of the positron beam: 1-5.8 GeV.
We tested the response of the detector with three different configurations of the W repartition.
The accumulated amount of tungsten, in radiation length units, $X_{0}$, in front of each of the modules is:
\begin{itemize}
\item W-configuration 1: $0.6,1.2,1.8,2.4,3.6,4.8$ and $6.6~X_{0}$
\item W-configuration 2: $1.2,1.8,2.4,3.6,4.8,6.6$ and $8.4~X_{0}$
\item W-configuration 3: $1.8,2.4,3.6,4.8,6.6,8.4$ and $10.2~X_{0}$
\end{itemize}
%The first one adding up a total of 6.16 $X_{0}$, the second 7.84 $X_{0}$ and the third of 9.52 $X_{0}$.
Preliminary results of the raw electromagnetic shower profiles are shown in figure \ref{showers}
for several beam energies in the W-configuration 2 (left) and for 4 GeV beam energy and the three different W-configurations (right). This first approach to the data looks promising but further studies and comparisons with simulations are needed.

\acknowledgments

This project has received funding from the European Union{\textquotesingle}s Horizon 2020 Research and Innovation program under Grant Agreement no. 654168.
This work was supported by the P2IO LabEx (ANR-10-LABX-0038), excellence project HIGHTEC,
in the framework {\textquotesingle}Investissements d{\textquotesingle}Avenir{\textquotesingle}
(ANR-11-IDEX-0003-01) managed by the French National Research Agency (ANR).
The research leading to these results has received funding from the People Programme (Marie
Curie Actions) of the European Union{\textquotesingle}s Seventh Framework Programme (FP7/2007-2013)
under REA grant agreement, PCOFUND-GA-2013-609102, through the PRESTIGE
programme coordinated by Campus France.
The measurements leading to these results have been performed at the Test Beam Facility at DESY Hamburg (Germany), a member of the Helmholtz Association (HGF).

% We suggest to always provide author, title and journal data:
% in short all the informations that clearly identify a document.

\begin{thebibliography}{99}

%\bibitem{ilctdr}
%  \emph{http://www.linearcollider.org/ILC/Publications/Technical-Design-Report}
 \bibitem{Behnke:2013xla} 
  T.~Behnke {\it et al.},
  ``The International Linear Collider Technical Design Report - Volume 1: Executive Summary,''
  arXiv:1306.6327 [physics.acc-ph].
  %%CITATION = ARXIV:1306.6327;%%
  %243 citations counted in INSPIRE as of 08 Dec 2017

\bibitem{Behnke:2013lya} 
  T.~Behnke {\it et al.},
  ``The International Linear Collider Technical Design Report - Volume 4: Detectors,''
  arXiv:1306.6329 [physics.ins-det].
  %%CITATION = ARXIV:1306.6329;%%
  %284 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Baer:2013cma} 
  H.~Baer {\it et al.},
  ``The International Linear Collider Technical Design Report - Volume 2: Physics,''
  arXiv:1306.6352 [hep-ph].
  %%CITATION = ARXIV:1306.6352;%%
  %540 citations counted in INSPIRE as of 08 Dec 2017

\bibitem{Fujii:2017vwa} 
  K.~Fujii {\it et al.},
  ``Physics Case for the 250 GeV Stage of the International Linear Collider,''
  arXiv:1710.07621 [hep-ex].
  %%CITATION = ARXIV:1710.07621;%%
  %5 citations counted in INSPIRE as of 08 Dec 2017

\bibitem{Brient:2002gh} 
  J.~C.~Brient and H.~Videau,
  ``The Calorimetry at the future e+ e- linear collider,''
  eConf C {\bf 010630}, E3047 (2001)
  [hep-ex/0202004].
  %%CITATION = HEP-EX/0202004;%%
  %90 citations counted in INSPIRE as of 08 Nov 2017

\bibitem{Morgunov:2004ed} 
  V.~Morgunov and A.~Raspereza,
  ``Novel 3-D clustering algorithm and two particle separation with tile HCAL,''
  physics/0412108.
  %%CITATION = PHYSICS/0412108;%%
  %6 citations counted in INSPIRE as of 08 Nov 2017

%\bibitem{calice} 
%  \emph{https://twiki.cern.ch/twiki/bin/view/CALICE/CaliceCollaboration}

\bibitem{Sefkow:2015hna} 
  F.~Sefkow, A.~White, K.~Kawagoe, R.~Poschl and J.~Repond,
  ``Experimental Tests of Particle Flow Calorimetry,''
  Rev.\ Mod.\ Phys.\  {\bf 88}, 015003 (2016)
  doi:10.1103/RevModPhys.88.015003
  [arXiv:1507.05893 [physics.ins-det]].
  %%CITATION = doi:10.1103/RevModPhys.88.015003;%%
  %5 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2011ha} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Tests of a particle flow algorithm with CALICE test beam data,''
  JINST {\bf 6}, P07005 (2011)
  doi:10.1088/1748-0221/6/07/P07005
  [arXiv:1105.3417 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/6/07/P07005;%%
  %32 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Anduze:2008hq} 
  J.~Repond {\it et al.} [CALICE Collaboration],
  ``Design and Electronics Commissioning of the Physics Prototype of a Si-W Electromagnetic Calorimeter for the International Linear Collider,''
  JINST {\bf 3}, P08001 (2008)
  doi:10.1088/1748-0221/3/08/P08001
  [arXiv:0805.4833 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/3/08/P08001;%%
  %78 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2008aa} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Response of the CALICE Si-W electromagnetic calorimeter physics prototype to electrons,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 608}, 372 (2009)
  doi:10.1016/j.nima.2009.07.026
  [arXiv:0811.2354 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2009.07.026;%%
  %56 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Adloff:2010xj} 
  C.~Adloff {\it et al.} CALICE Collaboration],
  ``Study of the interactions of pions in the CALICE silicon-tungsten calorimeter prototype,''
  JINST {\bf 5}, P05007 (2010)
  doi:10.1088/1748-0221/5/05/P05007
  [arXiv:1004.4996 [physics.ins-det]].
  %%CITATION = doi:10.1088/1748-0221/5/05/P05007;%%
  %19 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{CALICE:2011aa} 
  C.~Adloff {\it et al.} [CALICE Collaboration],
  ``Effects of high-energy particle showers on the embedded front-end electronics of an electromagnetic calorimeter for a future lepton collider,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 654}, 97 (2011)
  doi:10.1016/j.nima.2011.06.056
  [arXiv:1102.3454 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2011.06.056;%%
  %9 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Bilki:2014uep} 
  B.~Bilki {\it et al.} [CALICE Collaboration],
  ``Testing hadronic interaction models using a highly granular silicon tungsten calorimeter,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 794}, 240 (2015)
  doi:10.1016/j.nima.2015.05.009
  [arXiv:1411.7215 [physics.ins-det]].
  %%CITATION = doi:10.1016/j.nima.2015.05.009;%%
  %5 citations counted in INSPIRE as of 07 Nov 2017

 \bibitem{Callier:2011zz} 
  S.~Callier, F.~Dulucq, C.~de La Taille, G.~Martin-Chassard and N.~Seguin-Moreau,
  ``SKIROC2, front end chip designed to readout the Electromagnetic CALorimeter at the ILC,''
  JINST {\bf 6}, C12040 (2011).
  doi:10.1088/1748-0221/6/12/C12040
  %%CITATION = doi:10.1088/1748-0221/6/12/C12040;%%
  %21 citations counted in INSPIRE as of 07 Nov 2017

\bibitem{Gastaldi:2014vaa} 
  F.~Gastaldi, R.~Cornat, F.~Magniette and V.~Boudry,
 ``A scalable gigabit data acquisition system for calorimeters for linear collider,''
  PoS TIPP {\bf 2014}, 193 (2014).
  %%CITATION = POSCI,TIPP2014,193;%%
  %1 citations counted in INSPIRE as of 08 Nov 2017

\bibitem{pyrame1}
  F. Magniette, M. Rubio-Roy, and F. Thiant,
  ``Pyrame, a rapid-prototyping framework for online systems,''
  Journal of Physics, Conference Series, Vol 664, 2015.

\bibitem{pyrame2}
  M. Rubio-Roy, F. Thiant, and F. Magniette,
  ``Flexible online monitoring for high-energy physics with Pyrame,''
  Journal of Physics, Conference Series, 2016.

%\bibitem{a}
%Author, \emph{Title}, \emph{J. Abbrev.} {\bf vol} (year) pg.

%\bibitem{b}
%Author, \emph{Title},
%arxiv:1234.5678.

%\bibitem{c}
%Author, \emph{Title},
%Publisher (year).

\end{thebibliography}
\end{document}

### 2019-04-04 proceedings/IEEE2017/proceeding_v3.tex
create folder for all confereces (2017)

--- 2018-04-25 proceedings/IEEE/proceeding_arxiv.tex
@@
 \centering
-\includegraphics[width=3.0in]{shortslab-eps-converted-to.pdf}
+\includegraphics[width=3.0in]{shortslab.eps}
 % where an .eps filename suffix will be assumed under latex, 
@@
   \begin{tabular}{l}
-    \includegraphics[width=3.0in]{fevcob1-eps-converted-to.pdf}\\
-    \includegraphics[width=3.0in]{fevcob2-eps-converted-to.pdf}
+    \includegraphics[width=3.0in]{fevcob1.eps}\\
+    \includegraphics[width=3.0in]{fevcob2.eps}
   \end{tabular}
@@
 \centering
-\includegraphics[width=3.0in]{proto-eps-converted-to.pdf}
+\includegraphics[width=3.0in]{proto.eps}
 \caption{Technological prototype: 7 single short slabs inside the mechanical aluminum structure.}
@@
   \begin{tabular}{l}
-    \includegraphics[width=2.5in]{mipsummary-eps-converted-to.pdf}  \\
-    \includegraphics[width=2.5in]{snsummary-eps-converted-to.pdf}
+    \includegraphics[width=2.5in]{mipsummary.eps}  \\
+    \includegraphics[width=2.5in]{snsummary.eps}
   \end{tabular}
@@
 \centering
-\includegraphics[width=3.5in]{mip3peaks-eps-converted-to.pdf}
+\includegraphics[width=3.5in]{mip3peaks.eps}
 \caption{Single cell energy distribution (for all calibrated cells) for 3 GeV positron tracks acting as MIPs. }
@@
   \begin{tabular}{l}
-    \includegraphics[width=3.0in]{shower1-eps-converted-to.pdf}\\
-    \includegraphics[width=3.0in]{shower2-eps-converted-to.pdf}\\
-    \includegraphics[width=3.0in]{shower3-eps-converted-to.pdf}
+    \includegraphics[width=3.0in]{shower1.eps}\\
+    \includegraphics[width=3.0in]{shower2.eps}\\
+    \includegraphics[width=3.0in]{shower3.eps}
   \end{tabular}
@@
 \centering
-\includegraphics[width=2.0in]{longslab-eps-converted-to.pdf}
+\includegraphics[width=2.0in]{longslab.eps}
 % where an .eps filename suffix will be assumed under latex, 

### 2019-04-30 performance-paper-draft/NIMsub_arxiv1902.00110/v1/draft.tex
v1, with shower study

--- 2019-04-04 performance-paper-draft/NIMsub_arxiv1902.00110/v0/draft.tex
@@
 \documentclass[final,3p,times,twocolumn]{elsarticle}
-%\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
+\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
              % images in pdf, png or jpg format)
@@
 \usepackage{amsmath}
+\usepackage{subcaption}
+\usepackage{hyperref}
+\hyphenation{time-stamped}
 %\title{\boldmath Commissioning and performance in beam tests of the highly granular SiW-ECAL technological prototype for the ILC}
@@
 The technological  prototype of the CALICE highly granular silicon-tungsten electromagnetic 
-calorimeter (SiW-ECAL) tested in beam at DESY in 2017. 
+calorimeter (SiW-ECAL) has been tested in beam at DESY in 2017. 
 In this test the setup comprised seven layers of 1024 channels and a size of $18\times18$ cm$^2$ each.
@@
 and hermetic calorimetric systems. Furthermore, the PF capabilities are enhanced when the calorimeters
-are placed inside a large magnetic field that favors the separation of charged particles. 
+are placed inside a large magnetic field that favours the separation of charged particles. 
 This in turn calls for a compact design of the calorimeters.
@@
   \begin{tabular}{l}
+  \begin{subfigure}{\textwidth}
+    \centering
     \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
+    \caption{}
+    \label{proto:a}
+  \end{subfigure}%
+  \end{tabular}
+  \begin{tabular}{l}
+    \begin{subfigure}{\textwidth}
+    \centering
+    %  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
     \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
+    \caption{}
+    \label{proto:b}
+    \end{subfigure}%
   \end{tabular}
-\caption{Top: prototype with 7 layers inside the mechanical housing. Bottom: schematic view of the readout modules
-  including the surface repartition readout by each ASIC, numbered from 0 to 15. Notice that the adapter board and DAQ-detector interface drawings are not at scale.}
+%\begin{tabular}{l}
+%  \includegraphics[width=0.65\textwidth]{proto_numbered_2.png} \\
+%  \includegraphics[width=0.75\textwidth]{mapping-eps-converted-to.pdf} \\
+%\end{tabular}
+\caption{(a) Prototype with 7 layers inside the mechanical housing. (b) Schematic view of the readout modules
+  including the surface repartition readout by each ASIC, numbered from 0 to 15. Notice that the adapter board and the DAQ-detector interface drawings are not at scale.}
 \label{proto}
@@
 A picture showing the SiW-ECAL technological prototype setup tested at DESY (Hamburg) in summer
-2017 can be seen in Figure \ref{proto}.
-The setup consists of 7 layers housed in a PVC and aluminum structure that can host up to 10 layers
+2017 can be seen in Figure \ref{proto:a}.
+The setup consists of 7 layers housed in a PVC and aluminium structure that can host up to 10 layers
 in slots with a $15-$mm pitch. The first six layers were placed in the first six slots
@@
 on top of a carbon cradle that protects the sensors
-and the sides of the module. The readout module is further wrapped by two aluminum plates
+and the sides of the module. The readout module is further wrapped by two aluminium plates
 that provide electromagnetic shielding and mechanical stability.
@@
 to a data acquisition system (DAQ)\cite{Gastaldi:2014vaa,Rubio-Roy:2017ere,Magniette:2018wdz} at the beginning of the module.
-In the picture, the ASU is covered 
-by an aluminum plate marked by the red number 1.
-The ASU consist of a $18\times18$ cm$^2$ sized printed circuit board, PCB,
+In Figure \ref{proto:a}, the ASUs are covered 
+by an aluminium plate as the one marked by the red number 1.
+Each ASU consist of a $18\times18$ cm$^2$ sized printed circuit board, PCB,
 equipped with 16 VFE ASICs and 4 silicon sensors glued onto the other side.
 The PCB features 1024 square pads of $5.5\times5.5$ mm$^2$ that are readout by the ASICs.
-Part of the adapter board is also covered by the aluminum plate and the uncovered part 
-is seen over the red number 2 in the picture. 
+Part of the adapter board is also covered by the aluminium plate and the uncovered part 
+is seen over the red number 2 in Figure \ref{proto:a}. 
 The adapter board also holds other
@@
 of power to assure stable low voltage supply during the power pulsing. This capacitor
-is seen just above the red number 2.
+is seen just above the red number 2 in Figure \ref{proto:a}.
 The first component
-of the DAQ system, the detector interface board described in \cite{Gastaldi:2014vaa}, is identified in the picture by a red
-number 3.
-For simplicity, the rest of the DAQ system is not shown.
+of the DAQ system, the detector interface board described in \cite{Gastaldi:2014vaa},
+is identified in Figure \ref{proto:a} by a red number 3.
+For simplicity, the rest of the DAQ system is not shown.  A schematic drawing of a readout module
+is shown in Figure \ref{proto:b}.
 
@@
 The triggers are timestamped within each gated acquisition with a slow clock
-of 5 MHz. The timestamp numbers are called brunch crossing identifiers (BCID).
+of 5 MHz. The timestamp numbers are called bunch crossing identifiers (BCID).
 The charges are stored in the buffers of a switched capacitor array, SCA, and later converted by a 12-bit Wilkinson ADC.
@@
 The four sensors consist of $90\times90$ mm$^{2}$ silicon sensors of
-320$\pm15\,\upmu$m thick with high resistivity (bigger than 5000 $\Omega\cdot$cm).
+320$\pm15\,\upmu$m thick with high resistivity (larger than 5000 $\Omega\cdot$cm).
 Each sensor is subdivided in an array of 256 PIN diodes of $5.5\times5.5$ mm$^2$
@@
   The beam was normally directed to 81 positions equally distributed over the modules surface.
-\item Test in a magnetic field up to 1 T using, also without tungsten and with 3 GeV positrons. For this test, a PVC structure was
-designed and produced to support one single readout module.	
-%The purpose of such test was twofold: first to prove that the DAQ, all electronic devices and the 
-%readout module itself are able
-%to handle strong magnetic fields; 
-%second to check the quality of the data and the performance of the detector during the data taking when running
-%in a magnetic field.
+\item Test in a magnetic field up 1 T using a 3 GeV positron beam.
+  For this test, a PVC structure was designed and produced to support one single readout module
+  without any tungsten plates.
 \item Response to electrons of different energies with a fully equipped detector, {\it i.e}\@. sensitive parts {\it and} tungsten absorber. 
@@
 and the results of the pedestal, noise and MIP calibration in Section \ref{sec:calib}.
-We also show the results on the pedestal and noise stability when the readout modules are placed inside
-a magnetic field, in Section \ref{sec:magnetic}. %The study of the performance of the detector
-%for electromagnetic shower events is not covered in this document and will be the topic of a future paper.
+We also show the performance of the single readout tested in a magnetic field in Section \ref{sec:magnetic}. Finally,
+a first look to the performance of the detector
+in electromagnetic shower events is discussed in Section \ref{sec:showers}.
 
@@
 \begin{figure}[h!]
-  \includegraphics[width=0.5\textwidth]{masked_layer-eps-converted-to.pdf} 
+  \includegraphics[width=0.5\textwidth]{masked_layer.eps} 
 \caption{Fraction of channels with counts above one MIP in noise runs and that have been disabled for the data taking.}
@@
 
-The threshold of the internal trigger can be optimized by means of dedicated scans of trigger threshold values
+For each ASIC, the threshold of the internal trigger
+was optimized by means of dedicated scans of trigger threshold values
 with only noise signals or with injected signals of different amplitudes.
-%In the absence of external signals,
-%the shape and position of the threshold scan curves shows the
-%full envelope of the noise in the fast shaper which
-%not only depends on the electronic noise but also on the slow clock frequency, making its interpretation
-%not clear. 
-The trigger thresholds used for data taking of the individual channels
-are determined by lowering successively the trigger thresholds of the
-channels and recording the number of counts. The resulting curves can be approximated by an inverted error function.
-%Anyway, as the first goal is to set the trigger thresholds high enough to filter out most of the
-%noise events independently of its origin, we made the optimization of the trigger threshold values by performing dedicated
-%threshold scan runs with only noise. For that end, for a fixed amount of time, we counted the times that
-%every channel recorded at least one trigger as a function of
-%the internal trigger threshold. The resulting curve of acquisitions with triggers vs trigger threshold was
-%interpreted as the integral of the noise spectrum, assumed as gaussian.
+The scans start from high values of the thresholds
+and this are lowered successively and the number of signals recorded
+by each channel are counted. The resulting curves can be approximated by an inverted error function.
 A value of the optimal threshold was calculated for every channel by shifting the threshold
@@
 of the frequency of the white noise of the electronics and the clock speed of the readout.
-Therefore, the width is not a proper measurement of the detector noise.
+Therefore, this quantity is not the optimal estimator of the detector noise.
 To achieve this the scan has to be repeated with external signals.
@@
 
-%With this procedure, we fulfill the first requirement: set the trigger thresholds high enough to filter the noise.
-%We still need to know what is the size of signals that we can trigger on.
-%For this we need to perform a calibration of the trigger thresholds
-%and for that we need to perform the scans with calibrated external signals as input.
-%We planned to do this with beam particle by performing
-%scans with the beam hitting the detector at different angles. Unfortunately, due to tightness
-%of the program this could not be done
-%at the beam test described in this document. Instead
-%we used injected signals directly on the SKIROCs. Again we face the issue that
-%this capability is not included in all our modules so
-%we did it in a SKIROC testboard \cite{Suehara:2018mqk} in which a single SKIROC2 in BGA package is placed and signals of
-%the equivalent size of the expected for 1 MIP and 2 MIPs
-%are directly injected in the preamplifier (via a 3 pF capacitor located in the injection line).
 The result of these scans is shown in Figure \ref{scurves_injection} for several channels of one SKIROCs.
@@
   \begin{tabular}{l}
-	\includegraphics[width=0.35\textwidth]{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
+	\includegraphics[width=0.5\textwidth]{scurve_pp_fastshaper_ch_DAC_labels.eps}\\ %{scurve_pp_fastshaper_ch_DAC-eps-converted-to.pdf} \\
 	\end{tabular}
-\caption{Threshold curves with charge injection (1 MIP in blue and 2 MIPs in red) for different channels in a SKIROC2 testboard.
-From this plot, we extract a $(S/N)_{trigger}$ of about 12.8 in the trigger line.}
+  \caption{Two sets of threshold curves. Each set consists of theshold curves for individual channels in which a charge is artifially injected using a pulse generator.
+    For the set in the left (in blue), an equivalent of 1 MIP was injected. For the set in the right (red), a equivalent of 2 MIPs was injected.
+    These curves were obtained in a dedicated testboard \cite{Suehara:2018mqk} to test single SKIROC2 ASICs.}
 \label{scurves_injection}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{threshold_chip-eps-converted-to.pdf}
+  \includegraphics[width=0.5\textwidth]{threshold_chip.eps}
   \caption{Summary of the trigger threshold settings in the internal DAC units and in MIP units.}
@@
 due to the preamplifiers sensitivity to instabilities of the power supply; {\it b)}
-an artifact of the event validation logical sequence of the ASIC. These fake
+an artefact of the event validation logical sequence of the ASIC. These fake
 events are removed offline using timing information.
@@
   \centering 
-  \includegraphics[width=0.5\textwidth]{efficiency_nhits4_chips-eps-converted-to.pdf} \\
+  \includegraphics[width=0.5\textwidth]{efficiency_nhits4_chips.eps} \\
   \caption{MIP detection efficiency in high purity samples of tracks of MIP-like acting particles for all layers.
@@
 
-\subsection{Pedestal and noise stability in a magnetic field}
+\subsection{Performance of a single readout module in a magnetic field}
 \label{sec:magnetic}
 
-Data were recorded without magnetic field as reference for values of the magnetic field of 0.5 T and 1T, respectively. 
-%The study of the performance of the modules inside
-%inside magnetic fields has been divided in three consecutive steps:
-%a run with a magnetic field of 1 T; a second run with 0.5 T; and a final run with the magnet off.
+The study of the performance of the module inside
+inside magnetic fields has been divided in three consecutive steps:
+a reference run without magnetic field; a run with a magnetic field of 1 T; a second run with 0.5 T; and a final run without, again, magnetic field.
 The beam, 3 GeV positrons, was incident on the area of the PCB readout by the ASIC number 12.
-
-The pedestal position and width of all channels
-in the readout module inside of the magnetic field are compared with
-their values obtained in Section \ref{sec:calib}.
+During all this time, the readout module was continuously monitored and did not
+show any technical issue or change of performance. Due to the lower beam rates in this area (and the technical character of the test)
+we did not collect enough data to present a reliable comparison with the calibration described in the previous sections.
+However, we got enough data to study in detail the stability of the pedestal position and width of all channels
+in the ASIC 12. Their values are well compatible with the values obtained in Section \ref{sec:calib}.
 This is shown in Figure \ref{pedestal_magnetic}.
@@
 Due to the lower rates in this beam area, the
-analysis is only done up to few memory cells and at least 500 entries are required in order to calculate the pedestals
-for comparison with the default values.
+analysis is only done up to few memory cells.%and at least 500 entries are required in order to calculate the pedestals
+%for comparison with the default values.
 
@@
   \begin{tabular}{l}
-    \includegraphics[width=0.5\textwidth]{1T_summary_pedestal-eps-converted-to.pdf} \\
-    \includegraphics[width=0.5\textwidth]{1T_summary_noise-eps-converted-to.pdf}
+    \includegraphics[width=0.5\textwidth]{1T_summary_pedestal.eps} \\
+    \includegraphics[width=0.5\textwidth]{1T_summary_noise.eps}
   \end{tabular}
-  \caption{Average deviation of the pedestal mean position (up) and width (down). The error bars correspond to one standard deviation of the averaged values.}
+  \caption{
+    Average deviation of the pedestal mean position (up) and width (down) during the different runs at different magnetic field (1T, 0.5 T and 0T)
+    compared with data taken outside of the magnet structure. The error bars correspond to one standard deviation of the averaged values.
+    The results for several SCA is presented in each plot, with a slight shift in the $x$-axis to artificially separate the points for better visualization.
+  }
 \label{pedestal_magnetic}
+\end{figure}
+
+\subsection{Performance of the SiW-ECAL for low energy electromagnetic showers.}
+\label{sec:showers}
+For the last part of the beam test, the stack was equipped with several plates of tungsten of different thickness, interleaved
+between the readout modules (including one also between the beam and the first module).
+We performed several energy scans of the beam (1, 2, 3, 4, 5 and 5.8 GeV)
+and directed it in different positions. In addition, also several distributions of the tungsten absorbers
+were put in place. For the analysis of these data we proceed in a similar way than 
+the described in Section \ref{sec:mip} for the event building by timestamp.
+In addition, the single cell calibration described in previous section is applied.
+In Section \ref{sec:mip}, the events with more than 5 triggers per module were rejected to remove shower like events from the sample, in the present analysis, no constrain on the number of triggers per layer was applied.
+The results presented here correspond to the configuration of tungsten amounting 8.4 $X_{0}$ with the beam directed
+to the area covered by ASICs number 12-15. For this run, we got enough data to
+calculate with high statistics the shower profile for all the energies. This is presented in Figure \ref{showers}.
+To calculate the shower profile, we used the the single cell calibration results presented in the previous sections.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=0.5\textwidth]{shower.eps}\\
+  \caption{Electromagnetic shower profiles for different beam energies. In the x-axis, we show the accumulated thickness of tungsten absorber in front
+    of evert active layer. In the y-axis, the averaged fraction of the total energy measured by every active layer in each electromagnetic shower event. }
+\label{showers}
 \end{figure}
@@
 The MIP detection efficiency in tracks has been evaluated to be compatible with the 100\% in most of the channels.
+This first approach to electromagnetic shower results looks promising although further studies and comparisons with simulations are foreseen
+including the data of coming beam tests, which will include further R\&D developments and a potentially larger
+stack with up to $\sim20-30$ fully equipped
+layers and an homogeneous tungsten absorber distribution amounting up to $\sim24$ $X_{0}$ as foreseen, for example, by the ILD project
+for the International Linear Collider.
 
